### 2019-11-19 career_preparation/resume/resume.tex
mv career, add personal statement

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Anand Jain}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{
github, linkedin : anandijain\\
site: anandj.net\\
}
\address{anandj@uchicago.edu \\(408)597-4214\\}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Chicago}
{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun, 2021}\\
\textbf{Santa Clara High School} \hfill \textbf{2017}
%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages} Python, Julia, C, Bash\\
\textbf{Packages}  PyTorch, Gym, TensorFlow $\geq v2$, Sklearn, Pandas \\
\textbf{Spoken Languages} English - Fluent, Hindi, Spanish, Chinese - Classroom

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab LSST Intern\hfill Jun 24 - Aug 31}\\
\textbullet{Researched the applications of neural differential equations to astronomy\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Technology/Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Odds Tracking on GCP\hfill Oct 2018 - Now}\\
\textbullet{Built a python package that tracks sports statistics and odds\\}
\textbullet{Learned about cloud deployment by spinning up free-tier VMs on GCP\\}
\textbullet{Have collected over 1 GBs of live odds data from football, basketball and hockey}\\
\textbullet{Long-Short Term Memory (LSTM) classifer for directional movement of moneyline}
\begin{itemize}
\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, PyTorch
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: RL Gym Environment\hfill Feb 2019 - Now}\\
\textbullet{Created a set of custom reinforcement learning environments using the OpenAI Gym package for the output of Sips\\}
\textbullet{Attempted to use a Deep-Q network to learn a state value function.\\}
\textbullet{Goal: I'd like to update my envs to be compatible with TF-agents and run the different algorithms supported and see if the agent learns any better}

\begin{itemize}
\item \textbf{Technology/Tools:} Python, Gym, PyTorch
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/gym-sips
\end{itemize}

\section{COURSES}
\par
\normalfont{\textbullet{Algorithms}}
\normalfont{\textbullet{Discrete Math}}
\normalfont{\textbullet{Abstract Linear Algebra}}
\normalfont{\textbullet{Mathematical Logic}}
\normalfont{\textbullet{Inventing Interactive Devices}}
\normalfont{\textbullet{Electronics}}
\normalfont{\textbullet{Computer Systems}}
\section{ACTIVITIES}

\textbf{UCQuantum\hfill Aug 2019 - Now}\\
\textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
\textbullet{We have 50 facebook group members and roughly 15 active members}\\
\textbullet{Initial meetings have been learning/teaching the basics: superposition, entanglement, quantum logic gates, unitary matrices, and superdense coding}\\
\textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\
%-------------------------------------------------------------------------------

\end{resume}
\(\)\end{document}

### 2019-11-26 blender/intro/one.py
updates, added elm stuff and bov type schema

@@ -3,18 +3,20 @@ import bpy
 number = 7
 counter = 0
 
-for i in range(0, number+28):
+for i in range(0, number + 28):
     counter += 2
     counter2 = 0
     for j in range(0, number):
         counter2 += 2
         counter3 = 0
         for k in range(0, number):
-            bpy.ops.mesh.primitive_cube_add(size=2, location=(counter3+2, counter2-2, counter-2))
+            bpy.ops.mesh.primitive_cube_add(
+                size=2, location=(counter3 + 2, counter2 - 2, counter - 2)
+            )
             counter3 += 2
             bpy.ops.rigidbody.object_add()
             bpy.context.object.rigid_body.mass = 20
-            bpy.context.object.rigid_body.collision_shape = 'BOX'
+            bpy.context.object.rigid_body.collision_shape = "BOX"
             bpy.context.object.rigid_body.friction = 1
             bpy.context.object.rigid_body.use_margin = True
             bpy.context.object.rigid_body.collision_margin = 0

### 2019-11-26 blender/intro/primitive.py

@@ -1,6 +1,7 @@
 import bpy
 from random import randint
 
+
 def gen_monkeys():
     number = 60
 
@@ -8,7 +9,7 @@ def gen_monkeys():
         x = randint(-30, 30)
         y = randint(-30, 30)
         z = randint(-30, 30)
-        bpy.ops.mesh.primitive_monkey_add(location=(x,y,z))
+        bpy.ops.mesh.primitive_monkey_add(location=(x, y, z))
 
 
 if __name__ == "__main__":

### 2019-11-26 julia/http/req.py

@@ -1,21 +1,33 @@
 import requests
 import time
 
+
 def get_page():
     url = "https://api.matchbook.com/edge/rest/events"
 
-    querystring = {"offset": "0", "per-page": "20", "sport-ids": "1,4", "states": "open,suspended,closed,graded", "exchange-type": "back-lay",
-                "odds-type": "DECIMAL", "include-prices": "true", "price-depth": "3", "price-mode": "expanded", "include-event-participants": "false"}
+    querystring = {
+        "offset": "0",
+        "per-page": "20",
+        "sport-ids": "1,4",
+        "states": "open,suspended,closed,graded",
+        "exchange-type": "back-lay",
+        "odds-type": "DECIMAL",
+        "include-prices": "true",
+        "price-depth": "3",
+        "price-mode": "expanded",
+        "include-event-participants": "false",
+    }
 
-    headers = {'user-agent': 'api-doc-test-client'}
+    headers = {"user-agent": "api-doc-test-client"}
 
     response = requests.request("GET", url, headers=headers, params=querystring)
 
     # print(response.text)
     return response
 
+
 if __name__ == "__main__":
     t0 = time.time()
     ret = get_page()
     t1 = time.time()
-    print(f'delta: {str(t1 -t0)}')
+    print(f"delta: {str(t1 -t0)}")

### 2019-11-26 vision/old_src/demos.py

@@ -1,4 +1,1 @@
 # this file is for demonstrating the relevant functions in python cv2
-
-
- 

### 2019-11-26 vision/old_src/edges.py

@@ -2,19 +2,19 @@ import cv2
 import numpy as np
 import time
 
-PATH = 'images/cvtest.jpg'
+PATH = "images/cvtest.jpg"
 
 
 if __name__ == "__main__":
-    img = cv2.imread('images/cvtest.jpg')
+    img = cv2.imread("images/cvtest.jpg")
     gray = cv2.cvtColor(img, cv2.COLOR_RGB2GRAY)
     blur = cv2.GaussianBlur(gray, (11, 11), 0)
     canny = cv2.Canny(gray, 150, 300)
     res = cv2.resize(canny, None, fx=0.125, fy=0.125, interpolation=cv2.INTER_CUBIC)
-    
-    cv2.imwrite('images/output_contour.png',  canny)
-    cv2.imwrite('images/output_contour_resized.png',  res)
-    cv2.imshow('canny', res)
+
+    cv2.imwrite("images/output_contour.png", canny)
+    cv2.imwrite("images/output_contour_resized.png", res)
+    cv2.imshow("canny", res)
     cv2.waitKey(0)
 
-    print(img.shape)  
+    print(img.shape)

### 2019-11-26 vision/old_src/helpers.py

@@ -1,11 +1,6 @@
-
-
-
 # MACROS
 
 PATH
 
-TEST_IMG_PATH = PATH + '/cvtest.jpg' 
-TEST_VID_PATH = PATH + '/nba.mp4'
-
-
+TEST_IMG_PATH = PATH + "/cvtest.jpg"
+TEST_VID_PATH = PATH + "/nba.mp4"

### 2019-11-26 vision/old_src/vid.py

@@ -1,15 +1,15 @@
 import numpy as np
 import cv2
 
-cap = cv2.VideoCapture('sunset.mp4')
+cap = cv2.VideoCapture("sunset.mp4")
 
-while(cap.isOpened()):
+while cap.isOpened():
     ret, frame = cap.read()
 
     gray = cv2.cvtColor(frame, cv2.COLOR_BGR2GRAY)
 
-    cv2.imshow('frame', gray)
-    if cv2.waitKey(1) & 0xFF == ord('q'):
+    cv2.imshow("frame", gray)
+    if cv2.waitKey(1) & 0xFF == ord("q"):
         break
 
 cap.release()

### 2019-11-26 blender/intro/add_transform.py
updates, added elm stuff and bov type schema

@@ -1,16 +1,18 @@
 import bpy
 
-#def add_transform(seq):
+# def add_transform(seq):
 #    cur_frame = bpy.context.scene.frame_current
 #    c = 7
 #    bpy.ops.sequencer.effect_strip_add(type="TRANSFORM", channel=(c+1), frame_start=cur_frame)
 
-def add_movie(fn='/home/sippycups/Videos/short_clips/projector.mp4'):
+
+def add_movie(fn="/home/sippycups/Videos/short_clips/projector.mp4"):
     cur_frame = bpy.context.scene.frame_current
     channel = 7
-    bpy.ops.sequencer.movie_strip_add(filepath=fn, frame_start=cur_frame, channel=channel)
-    
-    
+    bpy.ops.sequencer.movie_strip_add(
+        filepath=fn, frame_start=cur_frame, channel=channel
+    )
+
+
 if __name__ == "__main__":
     add_movie()
-    

### 2019-11-26 career_preparation/practice/misc/mc.py

@@ -1,0 +1,41 @@
+def maxLCS(s):
+    """
+    the maximum number u could have is where there are n unique chars,
+    len(s) % 2 == 0, and len(s) == 2n
+    """
+    str_dict = {char: [] for char in set(s)}
+    for i, char in enumerate(s):
+        str_dict[char].append(i)
+    max_common = get_LCS(s, str_dict)
+
+    return max_common
+
+
+def get_LCS(s, d):
+    """
+    returns the lcs for a given split index
+    not fast enough
+
+    binary search? 
+    probabilistically, random strings will follow gaussian 
+    so it really is worthwhile to start at the middle instead of looping through
+    """
+    max_common = 0
+    str_len = len(s)
+
+    for i in range(str_len):
+        commons = 0
+        for k, v in d.items():
+            on_left = 0
+            on_right = 0
+            for elt in v:
+                if elt <= i:
+                    on_left += 1
+                elif elt > i:
+                    on_right += 1
+
+            commons += min(on_left, on_right)
+        if commons > max_common:
+            max_common = commons
+
+    return max_common

### 2019-11-26 career_preparation/practice/misc/strage_sort.py

@@ -1,0 +1,18 @@
+def strangeSort(mapping, nums):
+    """
+    
+    """
+    print(nums)
+    d_map = {str(n): str(i) for i, n in enumerate(mapping)}
+    converted = convert(nums, d_map)
+    indices = sorted(range(len(converted)), key=converted.__getitem__)
+    ret = [nums[i] for i in indices]
+    print(ret)
+    return ret
+
+
+def convert(nums, d_map):
+    # construct dict for easy access of correct map val
+    converted = []
+    converted = [int("".join(d_map[char] for char in str_num)) for str_num in nums]
+    return converted

### 2019-11-26 ml/lstm.py

@@ -19,58 +19,65 @@ window = 1
 log_interval = 100
 break_idx = 100
 
-save_folder = './models/'
-save_fn = 'lstm.pt'
+save_folder = "./models/"
+save_fn = "lstm.pt"
 
 save_path = save_folder + save_fn
 dir = "../data/stocks/Data/Stocks/"
 
 # device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-device = torch.device('cpu')
+device = torch.device("cpu")
 
 print(device)
 
+
 def plot_data(data, separate=True):
     # numpy input
-	col_names = ['open', 'high', 'low', 'close']
-	groups = range(4)
-	i = 1
-	plt.figure()
-	if separate:
-	    for group in groups:
-	        plt.subplot(len(groups), 1, i)
-	        plt.plot(data[:, group])
-	        plt.title(col_names[group], y=0.5, loc='right')
-	        i += 1
-	else:
-	    plt.plot(data)
-	plt.show()
+    col_names = ["open", "high", "low", "close"]
+    groups = range(4)
+    i = 1
+    plt.figure()
+    if separate:
+        for group in groups:
+            plt.subplot(len(groups), 1, i)
+            plt.plot(data[:, group])
+            plt.title(col_names[group], y=0.5, loc="right")
+            i += 1
+    else:
+        plt.plot(data)
+    plt.show()
 
 
 def dataset_shapes(dataset):
-	sample_x, sample_y = dataset[0]
-	print(f'dataset_shapes: sample_x shape: {sample_x.shape}, sample_y shape: {sample_y.shape}')
-	return sample_x, sample_y
+    sample_x, sample_y = dataset[0]
+    print(
+        f"dataset_shapes: sample_x shape: {sample_x.shape}, sample_y shape: {sample_y.shape}"
+    )
+    return sample_x, sample_y
+
 
 def dataloader_shapes(data_loader):
     for (x, y) in data_loader:
-        print(f'dataloader_shapes: x shape: {x.shape}, y shape: {y.shape}')
+        print(f"dataloader_shapes: x shape: {x.shape}, y shape: {y.shape}")
         break
     return x, y
 
+
 def attempt_load(model, path):
-	try:
-	    model.load_state_dict(torch.load(path))
-	    print(f'model state dict loaded from: {path}')
-	except Exception:
-	    pass
-	return model
+    try:
+        model.load_state_dict(torch.load(path))
+        print(f"model state dict loaded from: {path}")
[…]

### 2019-11-26 ml/vae.py

@@ -1,4 +1,4 @@
-'''
+"""
 variational autoencoder for multiline games
 
 want to split by pre game and in game too
@@ -6,7 +6,7 @@ want to split by pre game and in game too
 todo scheme:
 
 - get padded quarters
-'''
+"""
 import pandas as pd
 import torch
 import torch.nn as nn
@@ -18,10 +18,10 @@ import sips
 
 
 class Net(nn.Module):
-    '''
+    """
     This network is defined recursively.
     |layers| ~ log_2(input_dim)
-    '''
+    """
 
     def __init__(self, input_dim):
         super(Net, self).__init__()
@@ -60,12 +60,12 @@ class Net(nn.Module):
         return x
 
     def __repr__(self):
-        print(f'encoder: {self.enc}')
-        print(f'decoder: {self.dec}')
-        return 'network'
+        print(f"encoder: {self.enc}")
+        print(f"decoder: {self.dec}")
+        return "network"
 
 
-if __name__ == '__main__':
+if __name__ == "__main__":
     data_loader = sips.h.loaders.VAELoader()
     net = Net(data_loader.length).double()
 

### 2019-11-26 random/flux_vs_pytorch/mnist.py

@@ -17,7 +17,8 @@ class Net(nn.Module):
         x = F.relu(self.fc1(x))
         x = self.fc2(x)
         return F.log_softmax(x, dim=1)
-    
+
+
 def train(args, model, device, train_loader, optimizer, epoch):
     model.train()
     for batch_idx, (data, target) in enumerate(train_loader):
@@ -28,9 +29,16 @@ def train(args, model, device, train_loader, optimizer, epoch):
         loss.backward()
         optimizer.step()
         if batch_idx % args.log_interval == 0:
-            print('Train Epoch: {} [{}/{} ({:.0f}%)]\tLoss: {:.6f}'.format(
-                epoch, batch_idx * len(data), len(train_loader.dataset),
-                100. * batch_idx / len(train_loader), loss.item()))
+            print(
+                "Train Epoch: {} [{}/{} ({:.0f}%)]\tLoss: {:.6f}".format(
+                    epoch,
+                    batch_idx * len(data),
+                    len(train_loader.dataset),
+                    100.0 * batch_idx / len(train_loader),
+                    loss.item(),
+                )
+            )
+
 
 def test(args, model, device, test_loader):
     model.eval()
@@ -40,38 +48,84 @@ def test(args, model, device, test_loader):
         for data, target in test_loader:
             data, target = data.to(device), target.to(device)
             output = model(data)
-            test_loss += F.nll_loss(output, target, reduction='sum').item() # sum up batch loss
-            pred = output.argmax(dim=1, keepdim=True) # get the index of the max log-probability
+            test_loss += F.nll_loss(
+                output, target, reduction="sum"
+            ).item()  # sum up batch loss
+            pred = output.argmax(
+                dim=1, keepdim=True
+            )  # get the index of the max log-probability
             correct += pred.eq(target.view_as(pred)).sum().item()
 
     test_loss /= len(test_loader.dataset)
 
-    print('\nTest set: Average loss: {:.4f}, Accuracy: {}/{} ({:.0f}%)\n'.format(
-        test_loss, correct, len(test_loader.dataset),
-        100. * correct / len(test_loader.dataset)))
+    print(
+        "\nTest set: Average loss: {:.4f}, Accuracy: {}/{} ({:.0f}%)\n".format(
+            test_loss,
+            correct,
+            len(test_loader.dataset),
+            100.0 * correct / len(test_loader.dataset),
+        )
+    )
+
 
 def main():
     # Training settings
-    parser = argparse.ArgumentParser(description='PyTorch MNIST Example')
[…]

### 2019-11-26 random/intro_to_flask/app/hello.py

@@ -1,10 +1,13 @@
 from flask import Flask
+
 app = Flask(__name__)
 
-@app.route('/')
-def index():
-    return 'Index Page'
 
-@app.route('/hello')
+@app.route("/")
+def index():
+    return "Index Page"
+
+
+@app.route("/hello")
 def hello_world():
-    return 'Hello, World!'
+    return "Hello, World!"

### 2019-11-26 vision/old_src/extra.py

@@ -1,26 +1,25 @@
 import numpy as np
 import cv2
 
-cap = cv2.VideoCapture('images/microfile.mp4')
+cap = cv2.VideoCapture("images/microfile.mp4")
 
 # params for ShiTomasi corner detection
-feature_params = dict( maxCorners = 100,
-                       qualityLevel = 0.3,
-                       minDistance = 7,
-                       blockSize = 7 )
+feature_params = dict(maxCorners=100, qualityLevel=0.3, minDistance=7, blockSize=7)
 
 # Parameters for lucas kanade optical flow
-lk_params = dict( winSize  = (15,15),
-                  maxLevel = 2,
-                  criteria = (cv2.TERM_CRITERIA_EPS | cv2.TERM_CRITERIA_COUNT, 10, 0.03))
+lk_params = dict(
+    winSize=(15, 15),
+    maxLevel=2,
+    criteria=(cv2.TERM_CRITERIA_EPS | cv2.TERM_CRITERIA_COUNT, 10, 0.03),
+)
 
 # Create some random colors
-color = np.random.randint(0,255,(100,3))
+color = np.random.randint(0, 255, (100, 3))
 
 # Take first frame and find corners in it
 ret, old_frame = cap.read()
 old_gray = cv2.cvtColor(old_frame, cv2.COLOR_BGR2GRAY)
-p0 = cv2.goodFeaturesToTrack(old_gray, mask = None, **feature_params)
+p0 = cv2.goodFeaturesToTrack(old_gray, mask=None, **feature_params)
 
 # Create a mask image for drawing purposes
 mask = np.zeros_like(old_frame)
@@ -32,38 +31,37 @@ while True:
     frame_gray = cv2.cvtColor(frame, cv2.COLOR_BGR2GRAY)
 
     # if x % 3 == 0:
-    p0 = cv2.goodFeaturesToTrack(old_gray, mask = None, **feature_params)
+    p0 = cv2.goodFeaturesToTrack(old_gray, mask=None, **feature_params)
 
     # calculate optical flow
     p1, st, err = cv2.calcOpticalFlowPyrLK(old_gray, frame_gray, p0, None, **lk_params)
     # if st is None:
 
     # Select good points
-    good_new = p1[st==1]
-    good_old = p0[st==1]
+    good_new = p1[st == 1]
+    good_old = p0[st == 1]
 
     # draw the tracks
-    for i,(new,old) in enumerate(zip(good_new,good_old)):
[…]

### 2019-11-26 vision/old_src/show.py

@@ -3,10 +3,11 @@ import numpy as np
 import time
 
 # IMG_PATH = 'images/cvtest.jpg'
-VID_PATH = 'images/album_cover.mp4'
+VID_PATH = "images/album_cover.mp4"
 
 W = 1920
 H = 1080
+
 
 def process_frame(img):
     # gray = cv2.cvtColor(img, cv2.COLOR_RGB2GRAY)
@@ -20,7 +21,7 @@ def process_frame(img):
     # for i in corners:
     #     x,y = i.ravel()
     #     res = cv2.circle(img, (x,y), 10, 255, -1)
-    cv2.imshow('img', res)
+    cv2.imshow("img", res)
     # print(res.shape)
 
 
@@ -32,7 +33,7 @@ if __name__ == "__main__":
 
     while cap.isOpened():
         ret, frame = cap.read()
-        frame_number = cap.get(cv2.CAP_PROP_POS_FRAMES)   
+        frame_number = cap.get(cv2.CAP_PROP_POS_FRAMES)
         print(frame_number)
         if ret == True:
             process_frame(frame)
@@ -40,5 +41,3 @@ if __name__ == "__main__":
         else:
             cap.release()
             cv2.destroyAllWindows()
-
-     

### 2019-11-28 julia/diffrl/basic_diffrl.jl
cleanup

@@ -1,14 +1,0 @@
-using Gym
-env = make("CartPole-v0", :human_pane)
-
-actions = [sample(env._env.action_space) for i=1:1000]
-i = 1
-done = false
-reset!(env)
-# for trial in 
-while i <= length(actions) && !done
-    global i, done
-    a, b, done, d = step!(env, actions[i])
-    render!(env)
-    i += 1
-end

### 2019-11-28 julia/diffrl/cartpole_diffrl.jl

@@ -1,126 +1,0 @@
-using Flux, Gym, Printf, Zygote
-using Zygote: @adjoint
-using Flux.Optimise: update!
-using Statistics: mean
-#using CuArrays
-
-import Base.sign
-
-#Load game environment
-
-env = make("CartPole-v0", :human_pane)
-reset!(env)
-
-#ctx = Ctx(env)
-
-#display(ctx.s)
-# using Blink# when not on Juno
-# body!(Blink.Window(), ctx.s)
-
-# ----------------------------- Parameters -------------------------------------
-
-STATE_SIZE = length(env._env.state)
-ACTION_SIZE = length(env._env.action_space)
-MAX_TRAIN_REWARD = env._env.x_threshold * env._env.θ_threshold_radians
-SEQ_LEN = 8
-
-# Optimiser params
-η = 3f-2
-# ------------------------------ Model Architecture ----------------------------
-sign(x) = Base.sign.(x)
-@adjoint sign(x) = sign(x), x̄ -> (x̄,)
-
-model = Chain(Dense(STATE_SIZE, 24, relu),
-              Dense(24, 48, relu),
-              Dense(48, 1, tanh), x->sign(x)) |> gpu
-
-opt = ADAM(η)
-
-action(state) = state |> model |> (model_output) -> (3 .+ model_output) / 2
-
-loss(rewards) = Flux.mse(rewards, MAX_TRAIN_REWARD)
-
-# ----------------------------- Helper Functions -------------------------------
-
-function train_reward(env::EnvWrapper)
-    s = env._env.state
-    x, ẋ, θ, θ̇  = s
-    # Custom reward for training
-    # Product of Triangular function over x-axis and θ-axis
-    # Min reward = 0, Max reward = env.x_threshold * env.θ_threshold_radians
-    x_upper = env._env.x_threshold - x
-    x_lower = env._env.x_threshold + x
-
-    r_x     = max(0f0, min(x_upper, x_lower))
-
-    θ_upper = env._env.θ_threshold_radians - θ
-    θ_lower = env._env.θ_threshold_radians + θ
-
-    r_θ     = max(0f0, min(θ_upper, θ_lower))
-
-    return r_x * r_θ
-end
-
-function μEpisode(env::EnvWrapper)
-    l = 0
-    for frames ∈ 1:SEQ_LEN
-        #render(env, ctx)
-        #sleep(0.01)
-        a = action(env._env.state)
-        s′, r, done, _ = step!(env, a)
[…]

### 2019-11-28 julia/diffrl/treb_diffrl.jl

@@ -1,55 +1,0 @@
-using Flux, Trebuchet
-using Zygote: forwarddiff
-using Statistics: mean
-using Random
-
-lerp(x, lo, hi) = x*(hi-lo)+lo
-
-function shoot(wind, angle, weight)
-  Trebuchet.shoot((wind, Trebuchet.deg2rad(angle), weight))[2]
-end
-
-shoot(ps) = forwarddiff(p -> shoot(p...), ps)
-
-Random.seed!(0)
-
-model = Chain(Dense(2, 16, σ),
-              Dense(16, 64, σ),
-              Dense(64, 16, σ),
-              Dense(16, 2)) |> f64
-
-θ = params(model)
-
-function aim(wind, target)
-  angle, weight = model([wind, target])
-  angle = σ(angle)*90
-  weight = weight + 200
-  angle, weight
-end
-
-distance(wind, target) =
-  shoot(Tracker.collect([wind, aim(wind, target)...]))
-
-function loss(wind, target)
-  try
-    (distance(wind, target) - target)^2
-  catch e
-    # Roots.jl sometimes give convergence errors, ignore them
-    println("Error in Loss fxn")
-    param(0)
-  end
-end
-
-DIST  = (20, 100)	# Maximum target distance
-SPEED =   5 # Maximum wind speed
-
-target() = (randn() * SPEED, lerp(rand(), DIST...))
-
-meanloss() = mean(sqrt(loss(target()...)) for i = 1:100)
-
-opt = ADAM()
-
-dataset = (target() for i = 1:100_000)
-cb = Flux.throttle(() -> @show(meanloss()), 10)
-
-Flux.train!(loss, θ, dataset, opt, cb = cb)

### 2019-11-28 julia/stats/bayes.jl

@@ -1,5 +1,0 @@
-# https://juliastats.github.io/Distributions.jl/stable/starting/
-using Turing, Flux, Distributions, Plots, Random
-
-
-

### 2019-11-28 julia/test/mod_two.jl

@@ -1,10 +1,0 @@
-using Plots
-
-module MyMod
-	function test_plot()
-		plot(randn(10))
-
-	end
-end
-
-

### 2019-11-28 julia/lotka.jl
cleanup

@@ -1,50 +1,0 @@
-using Flux, DiffEqFlux, DifferentialEquations, Plots
-
-## Setup ODE to optimize
-function lotka_volterra(du,u,p,t)
-  x, y = u
-  α, β, δ, γ = p
-  du[1] = dx = α*x - β*x*y
-  du[2] = dy = -δ*y + γ*x*y
-end
-u0 = [1.0,1.0]
-tspan = (0.0,10.0)
-p = [1.5,1.0,3.0,1.0] #True Params
-prob = ODEProblem(lotka_volterra,u0,tspan,p)
-println("ODE prob defined")
-
-# Verify ODE solution
-sol = solve(prob,Tsit5())
-plot(sol)
-
-# Generate data from the ODE
-data_sol = solve(prob,Tsit5(),saveat=0.1)
-A1 = data_sol[1,:] # length 101 vector
-A2 = data_sol[2,:] # length 101 vector
-t = 0:0.1:10.0
-scatter!(t,A1,color=[1],label = "rabbits")
-scatter!(t,A2,color=[2],label = "wolves")
-
-# Build a neural network that sets the cost as the difference from the
-# generated data and true data
-
-p = param([4., 1.0, 2.0, 0.4]) # Initial Parameter Vector
-function predict_rd() # Our 1-layer neural network
-  diffeq_rd(p,prob,Tsit5(),saveat=0.1)
-end
-loss_rd() = sum(abs2,predict_rd()-data_sol) # loss function
-
-# Optimize the parameters so the ODE's solution stays near 1
-
-data = Iterators.repeated((), 1000)
-opt = ADAM(0.1)
-cb = function () #callback function to observe training
-  #= display(loss_rd()) =#
-  # using `remake` to re-create our `prob` with current parameters `p`
-  scatter(t,A1,color=[1],label = "rabbit data")
-  scatter!(t,A2,color=[2],label = "wolves data")
-  display(plot!(solve(remake(prob,p=Flux.data(p)),Tsit5(),saveat=0.1),ylim=(0,6),labels = ["rabbit model","wolf model"],color=[1 2]))
-end
-# Display the ODE with the initial parameter values.
-cb()
-Flux.train!(loss_rd, [p], data, opt, cb = cb)

### 2019-11-28 julia/test/my_mod.jl

@@ -1,10 +1,0 @@
-module ThisMod
-
-	using Plots
-	
-	function test_plot()
-		plot(randn(10))
-	end
-	
-end
-

### 2019-11-28 julia/saved_cifar.jl
more cleanup

@@ -1,12 +1,0 @@
-using Flux, Metalhead, Statistics
-using Flux: onehotbatch, onecold, crossentropy, throttle
-using Metalhead: trainimgs
-using Images: channelview
-using Statistics: mean
-using Base.Iterators: partition
-using Bson: @save, @load
-
-function kernel_tups_vgg19()
-	kernels = [(3, 3) for _ in 1:16]
-end
-

### 2019-11-28 julia/saved_mnist.jl

@@ -1,64 +1,0 @@
-using Flux
-using Statistics
-using Flux: onehotbatch, onecold, crossentropy, throttle, @epochs
-using BSON: @save, @load
-using BenchmarkTools
-
-function get_mnist()
-	imgs = Flux.Data.MNIST.images()
-	X = hcat(float.(reshape.(imgs, :))...)
-	
-	labels = Flux.Data.MNIST.labels()
-	Y = onehotbatch(labels, 0:9)
-	return X, Y
-end
-	
-function get_model()
-	model = Chain(Dense(784, 100, relu), Dense(100, 10), softmax)
-	return model
-end
-
-function params_into_model(fn)
-	model = get_model()
-	@load fn weights
-	Flux.loadparams!(model, weights)
-	return model
-end
-
-function load_model(fn)
-	@load fn model
-	return model
-end
-
-accuracy(x, y) = mean(onecold(model(x)) .== onecold(y))
-
-function train_model(model)
-	loss(x, y) = crossentropy(model(x), y)
-	evalcb = () -> @show(loss(X, Y))
-	opt = ADAM()
-	# dataset = Iterators.repeated((X, Y), 200)
-	Flux.train!(loss, params(model), dataset, opt, cb=throttle(evalcb, 10))
-end
-
-function save_weights(fn, model)
-	weights = Tracker.data.(params(model))
-	@save fn weights
-end
-
-function save_model(fn, model)
-	@save fn model
-end
-
-function main()
-	#model_path = "./models/mymodel.bson"
-	#weights_path = "./models/myweights.bson"
-	X, Y = get_mnist()
-	model = load_model(model_path)
-	# model = params_into_model("./models/myweights.bson")
-	train_model(model)
-	println(accuracy(X, Y))
-	#save_weights(weights_path, model)
-	# save_model(model_path, model)
-end
-
-main()

### 2019-11-29 bash/open_tor.sh
before elm-format

@@ -1,5 +1,0 @@
-#!/bin/bash
-
-sh -c '"/home/sippycups/Downloads/Applications/tor-browser_en-US/Browser/start-tor-browser" --detach || ([ !  -x "/home/sippycups/Downloads/Applications/tor-browser_en-US/Browser/start-tor-browser" ] && "$(dirname "$*")"/Browser/start-tor-browser --detach)' dummy %k
-
-

### 2019-12-02 random/career_preparation/resume/resume.tex
cleanup
clean

--- 2019-11-19 career_preparation/resume/resume.tex
@@
 \section{SKILLS}
-\textbf{Languages} Python, Julia, C, Bash\\
-\textbf{Packages}  PyTorch, Gym, TensorFlow $\geq v2$, Sklearn, Pandas \\
-\textbf{Spoken Languages} English - Fluent, Hindi, Spanish, Chinese - Classroom
+\textbf{Languages:} Python, Julia, Bash, C\\
+\textbf{Packages:}  PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas \\
+\textbf{Spoken:} English, Hindi, Spanish
 
@@
 \section{PROJECTS}
-\textbf{Sips: Odds Tracking on GCP\hfill Oct 2018 - Now}\\
-\textbullet{Built a python package that tracks sports statistics and odds\\}
-\textbullet{Learned about cloud deployment by spinning up free-tier VMs on GCP\\}
+\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
+\textbullet{Package to track odds and player data from a variety of sports and sources\\}
 \textbullet{Have collected over 1 GBs of live odds data from football, basketball and hockey}\\
-\textbullet{Long-Short Term Memory (LSTM) classifer for directional movement of moneyline}
+\textbullet{Example prediction models using TensorFlow, including classification and LSTM prediction models}
 \begin{itemize}
-\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, PyTorch
+\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, TensorFlow
 \end{itemize}
@@
 \end{itemize}
-\textbf{Gym-Sips: RL Gym Environment\hfill Feb 2019 - Now}\\
-\textbullet{Created a set of custom reinforcement learning environments using the OpenAI Gym package for the output of Sips\\}
-\textbullet{Attempted to use a Deep-Q network to learn a state value function.\\}
-\textbullet{Goal: I'd like to update my envs to be compatible with TF-agents and run the different algorithms supported and see if the agent learns any better}
+\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
+\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}
 
 \begin{itemize}
-\item \textbf{Technology/Tools:} Python, Gym, PyTorch
+\item \textbf{Technology/Tools:} Python, Gym, TensorFlow, TF-Agents
 \end{itemize}
@@
 
-\textbf{UCQuantum\hfill Aug 2019 - Now}\\
+\textbf{UCQuantum (.org)\hfill Aug 2019 - Now}\\
 \textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
-\textbullet{We have 50 facebook group members and roughly 15 active members}\\
-\textbullet{Initial meetings have been learning/teaching the basics: superposition, entanglement, quantum logic gates, unitary matrices, and superdense coding}\\
+\textbullet{We have 50 facebook group members and 10 active members}\\
 \textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\

### 2019-12-02 bash/misc/open_tor.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+sh -c '"/home/sippycups/Downloads/Applications/tor-browser_en-US/Browser/start-tor-browser" --detach || ([ !  -x "/home/sippycups/Downloads/Applications/tor-browser_en-US/Browser/start-tor-browser" ] && "$(dirname "$*")"/Browser/start-tor-browser --detach)' dummy %k
+
+

### 2019-12-02 bash/misc/remove_py38.sh
clean

@@ -1,0 +1,33 @@
+#!/bin/bash
+
+# found on stack overflow, storing for safekeeping
+
+prefix='/usr/local/'
+pyver='3.8'
+
+
+rm -rf \
+    ${prefix}bin/python${pyver} \
+    ${prefix}bin/pip${pyver} \
+    ${prefix}bin/pydoc \
+    ${prefix}bin/include/python${pyver} \
+    ${prefix}lib/libpython${pyver}.a \
+    ${prefix}lib/python${pyver} \
+    ${prefix}bin/python${pyver} \
+    ${prefix}bin/pip${pyver} \
+    ${prefix}bin/include/python${pyver} \
+    ${prefix}lib/libpython${pyver}.a \
+    ${prefix}lib/python${pyver} \
+    ${prefix}lib/pkgconfig/python-${pyver}.pc \
+    ${prefix}lib/libpython${pyver}m.a \
+    ${prefix}bin/python${pyver}m \
+    ${prefix}bin/2to3-${pyver} \
+    ${prefix}bin/python${pyver}m-config \
+    ${prefix}bin/idle${pyver} \
+    ${prefix}bin/pydoc${pyver} \
+    ${prefix}bin/pyvenv-${pyver} \
+    ${prefix}share/man/man1/python${pyver}.1 \
+    ${prefix}include/python${pyver}m
+    ${prefix}bin/pydoc ## WARN: skip if other pythons in local exist.
+
+

### 2019-12-02 haskell/first.hs

@@ -1,0 +1,4 @@
+doubleMe x = x + x
+
+
+doubleThem x y = doubleMe x + doubleMe y

### 2019-12-02 random/pythonstuff/ml/adanet/classify.py

@@ -1,65 +1,0 @@
-import adanet
-import tensorflow as tf
-
-
-FEATURES_KEY = "x"
-
-
-def input_fn(partition, training, batch_size):
-  """Generate an input function for the Estimator."""
-
-  def _input_fn():
-
-    if partition == "train":
-      dataset = tf.data.Dataset.from_tensor_slices(({
-          FEATURES_KEY: tf.log1p(x_train)
-      }, tf.log1p(y_train)))
-    else:
-      dataset = tf.data.Dataset.from_tensor_slices(({
-          FEATURES_KEY: tf.log1p(x_test)
-      }, tf.log1p(y_test)))
-
-    # We call repeat after shuffling, rather than before, to prevent separate
-    # epochs from blending together.
-    if training:
-      dataset = dataset.shuffle(10 * batch_size, seed=RANDOM_SEED).repeat()
-
-    dataset = dataset.batch(batch_size)
-    iterator = dataset.make_one_shot_iterator()
-    features, labels = iterator.get_next()
-    return features, labels
-
-  return _input_fn
-
-feature_columns = None
-
-estimator = adanet.AutoEnsembleEstimator(
-    head=head,
-    candidate_pool={
-        'linear':
-            tf.estimator.LinearEstimator(
-                head=head,
-                feature_columns=feature_columns,
-                optimizer=...)
-            )
-        'dnn':
-            tf.estimator.DNNEstimator(
-                head=head,
-                feature_columns=feature_columns,
-                optimizer=...,
-                hidden_units=[1000, 500, 100])},
-                max_iteration_steps = 50)
-
-    estimator.train(input_fn = train_input_fn, steps = 100)
-    metrics=estimator.evaluate(input_fn = eval_input_fn)
-    predictions=estimator.predict(input_fn = predict_input_fn)
-    }
-)
-
-
-def main():
-    (x_train, y_train), (x_test, y_test)=(tf.keras.datasets.boston_housing.load_data())
-    # Preview the first example from the training data
-    print('Model inputs: %s \n' % x_train[0])
-    print('Model output (house price): $%s ' %(y_train[0] * 1000))
-    head=MultiClassHead(n_classes=2)

### 2019-12-14 audio/app.py
go

@@ -17,21 +17,11 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 
+import utils 
+
 from flask import Flask, Response, request, render_template
 
-
 app = Flask(__name__)
-
-DIRECTORY = "/home/sippycups/Music/2019/"
-FILE_NAMES = os.listdir(DIRECTORY)
-
-
-def sgram(wave):
-    return torchaudio.transforms.Spectrogram()(wave)
-
-
-def wavey(filename):
-    return torchaudio.load(DIRECTORY + filename)[0]
 
 
 @app.route("/")
@@ -39,14 +29,15 @@ def hello_world():
     """
 
     """
-    return str(FILE_NAMES)
+    return str(utils.FILE_NAMES)
 
 
 @app.route('/sgrams/<int:i>')
 def display_sgram(i):
-    song_name = FILE_NAMES[i]
+    song_name = utils.FILE_NAMES[i]
     print(f'song_name: {song_name}')
-    specgram = sgram(wavey(song_name))
+    waveform = utils.wavey(song_name)
+    specgram = utils.sgram(waveform)
 
     fig = Figure(figsize=(20, 10), dpi=500)
     axis = fig.add_subplot(1, 1, 1, title=str(song_name))
@@ -58,8 +49,8 @@ def display_sgram(i):
 
 @app.route('/waves/<int:i>')
 def display_wave(i):
-    song_name = FILE_NAMES[i]
-    wave = wavey(song_name)
+    song_name = utils.FILE_NAMES[i]
+    wave = utils.wavey(song_name)
     fig = Figure(figsize=(10, 10), dpi=100)
     axis = fig.add_subplot(1, 1, 1, title=str(song_name))
     axis.plot(wave.t().numpy())

### 2019-12-14 audio/utils.py

@@ -1,0 +1,16 @@
+import os
+import torch
+import torchaudio
+import matplotlib.pyplot as plt
+
+
+DIRECTORY = "/home/sippycups/Music/2019/"
+FILE_NAMES = os.listdir(DIRECTORY)
+
+
+def sgram(wave):
+    return torchaudio.transforms.Spectrogram()(wave)
+
+
+def wavey(filename):
+    return torchaudio.load(DIRECTORY + filename)[0]

### 2019-12-14 audio/window.py

@@ -1,0 +1,15 @@
+from matplotlib.figure import Figure
+
+import torch
+import torchaudio
+import matplotlib.pyplot as plt
+
+import pandas as pd
+import numpy as np
+
+from sips.h import helpers 
+
+
+if __name__ == "__main__":
+    
+    pass

### 2019-12-24 random/career_preparation/resume/resume.tex
go
resume update

@@
 \textbf{Santa Clara High School} \hfill \textbf{2017}
+
+\section{COURSES}
+\par
+\normalfont{\textbullet{Algorithms}}
+\normalfont{\textbullet{Discrete Math}}
+\normalfont{\textbullet{Abstract Linear Algebra}}
+\normalfont{\textbullet{Mathematical Logic}}
+\normalfont{\textbullet{Inventing Interactive Devices}}
+\normalfont{\textbullet{Electronics}}
+\normalfont{\textbullet{Computer Systems}}
+
 %-------------------------------------------------------------------------------
@@
 \section{SKILLS}
-\textbf{Languages:} Python, Julia, Bash, C\\
-\textbf{Packages:}  PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas \\
-\textbf{Spoken:} English, Hindi, Spanish
+\textbf{Languages:} Python, Julia, Go, Bash, C\\
+\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
+\textbf{Spoken:} Fluent English. Classroom Hindi and Spanish
 
@@
 \section{EXPERIENCE}
-\textbf{Fermilab LSST Intern\hfill Jun 24 - Aug 31}\\
-\textbullet{Researched the applications of neural differential equations to astronomy\\}
-\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves}\\
+\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun 24 - Aug 31 2019}\\
+\textbullet{Researched the applications of neural differential equations to astronomy for the Large Synoptic Survey Telescope\\}
+\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
+\textbullet{Presented a poster of my work on Neural-ODEs at the 2019 LSST Conference in Arizona}\\
 \textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
 \begin{itemize}
-    \item \textbf{Technology/Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy
+    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
 \end{itemize}
@@
 \textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
-\textbullet{Package to track odds and player data from a variety of sports and sources\\}
-\textbullet{Have collected over 1 GBs of live odds data from football, basketball and hockey}\\
-\textbullet{Example prediction models using TensorFlow, including classification and LSTM prediction models}
+\textbullet{Created Python package to track odds and statistics for a variety of sports\\}
+\textbullet{Have collected over 1 GBs of data using Linux virtual machines on Google Cloud }\\
+\textbullet{Trained TensorFlow win/loss classification and LSTM odds prediction neural network models on Sips data}\\
+\textbullet{Wrote Flask app to visualize odds using Matplotlib}
 \begin{itemize}
-\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, TensorFlow
+\item \textbf{Tools:} Python, Requests, Beautiful Soup, TensorFlow, Flask, Matplotlib
 \end{itemize}
@@
 \textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
-\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}
+\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}\\
+\textbullet{Agent takes actions to buy the home team or the away team moneyline, and receives reward at the end of the game}\\
+\textbullet{Agent learns hedging strategies to mitigate risk}
 
 \begin{itemize}
-\item \textbf{Technology/Tools:} Python, Gym, TensorFlow, TF-Agents
+\item \textbf{Tools:} Python, Gym, TensorFlow, TF-Agents
 \end{itemize}
@@
 
-\section{COURSES}
-\par
-\normalfont{\textbullet{Algorithms}}
-\normalfont{\textbullet{Discrete Math}}
-\normalfont{\textbullet{Abstract Linear Algebra}}
-\normalfont{\textbullet{Mathematical Logic}}
-\normalfont{\textbullet{Inventing Interactive Devices}}
-\normalfont{\textbullet{Electronics}}
-\normalfont{\textbullet{Computer Systems}}
 \section{ACTIVITIES}
 
-\textbf{UCQuantum (.org)\hfill Aug 2019 - Now}\\
+\textbf{UCQuantum (.org) - Founder/President}
+\hfill \textbf{Aug 2019 - Now}\\
 \textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\

### 2019-12-31 random/pythonstuff/fin/edgar.py
updates

@@ -3,16 +3,6 @@ import bs4
 import pandas as pd
 
 
-""" todo today
-
-email elise
-quantum notes readthru 
-
-
-"""
-
-
-
 """
 list companies
 get company ids 
@@ -20,17 +10,51 @@ get company ids
 
 
 
-def search_link(name:str) -> str:
+def search_link(name:str, form_type='13F-HR') -> str:
     company = name.replace(' ', '+')
-    return 'https://www.sec.gov/cgi-bin/browse-edgar?company=' + company + '&count=100'
+    return 'https://www.sec.gov/cgi-bin/browse-edgar?company=' + company + '&type=' + form_type + '&count=100&output=xml'
 
-
-# def get_pages(companies:list)-> list:
-#     for c in companies:
-#         link = search_link()
 
 def get_page(link:str)->bs4.BeautifulSoup:
     return bs4.BeautifulSoup(r.get(link).text, 'html.parser')
+
+
+def next_pages(page: bs4.BeautifulSoup) -> list:
+    pages = [page]
+    next_page = page.find('span', {'id': 'next'})
+    while next_page is not None:
+        page = get_page(next_page.a['href'])
+        pages.append(page)
+        next_page = page.find('span', {'id': 'next'})
+
+    return pages
+        
+
+def grab_docs_links(page:bs4.BeautifulSoup) -> list:
+    all_links = []
+    all_pages = next_pages(page)
+    for page in all_pages:
+        t = page.find('table', {'class' : 'results'})
+        links = [l['href'] for l in t.find_all('a')]
+        all_links += links
+
+    #  = [l['href'] for l in page.find_all('a', {'id' : 'documentsbutton'}) for page in all_pages]
+    return all_links
+        
+
+
+def get_holdings(page:bs4.BeautifulSoup, output='df') -> pd.DataFrame:
+    table = page.find('table', {'summary': 'Form 13F-NT Header Information'})
+
+    if output == 'df':
+        ret = clean_holdings(pd.read_html(table.prettify())[0])
+        
+    return ret
+
+def clean_holdings(df:pd.DataFrame) -> pd.DataFrame:
+    df.columns = df.iloc[2]
+    df.drop([0, 1, 2], inplace=True)
+    return df
 
 def get_CIKs():
     cik = 'https://www.sec.gov/cgi-bin/cik_lookup'
@@ -44,7 +68,11 @@ if __name__ == "__main__":
 
     links = list(map(search_link, companies))
[…]

### 2019-12-31 random/pythonstuff/fin/edgar.py
updates:

@@ -5,17 +5,16 @@ import pandas as pd
 
 """
 list companies
-get company ids 
+get company ids
 """
 
 
-
-def search_link(name:str, form_type='13F-HR') -> str:
+def search_link(name: str, form_type='13F-HR') -> str:
     company = name.replace(' ', '+')
-    return 'https://www.sec.gov/cgi-bin/browse-edgar?company=' + company + '&type=' + form_type + '&count=100&output=xml'
+    return 'https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&company=' + company + '&type=' + form_type + '&count=100&output=xml'
 
 
-def get_page(link:str)->bs4.BeautifulSoup:
+def get_page(link: str) -> bs4.BeautifulSoup:
     return bs4.BeautifulSoup(r.get(link).text, 'html.parser')
 
 
@@ -28,51 +27,57 @@ def next_pages(page: bs4.BeautifulSoup) -> list:
         next_page = page.find('span', {'id': 'next'})
 
     return pages
-        
 
-def grab_docs_links(page:bs4.BeautifulSoup) -> list:
+
+def grab_docs_links(page: bs4.BeautifulSoup) -> list:
     all_links = []
     all_pages = next_pages(page)
     for page in all_pages:
-        t = page.find('table', {'class' : 'results'})
+        t = page.find('table', {'class': 'results'})
         links = [l['href'] for l in t.find_all('a')]
         all_links += links
 
-    #  = [l['href'] for l in page.find_all('a', {'id' : 'documentsbutton'}) for page in all_pages]
     return all_links
-        
 
 
-def get_holdings(page:bs4.BeautifulSoup, output='df') -> pd.DataFrame:
+def get_holdings(page: bs4.BeautifulSoup, output='df') -> pd.DataFrame:
     table = page.find('table', {'summary': 'Form 13F-NT Header Information'})
 
     if output == 'df':
         ret = clean_holdings(pd.read_html(table.prettify())[0])
-        
+
     return ret
 
-def clean_holdings(df:pd.DataFrame) -> pd.DataFrame:
+
+def clean_holdings(df: pd.DataFrame) -> pd.DataFrame:
     df.columns = df.iloc[2]
     df.drop([0, 1, 2], inplace=True)
     return df
+
 
 def get_CIKs():
     cik = 'https://www.sec.gov/cgi-bin/cik_lookup'
     return cik
 
-if __name__ == "__main__":
-    
[…]

### 2020-01-01 random/pythonstuff/fin/edgar.py
moved fin to separate repo, updated resume

@@ -1,83 +1,0 @@
-import requests as r
-import bs4
-import pandas as pd
-
-
-"""
-list companies
-get company ids
-"""
-
-
-def search_link(name: str, form_type='13F-HR') -> str:
-    company = name.replace(' ', '+')
-    return 'https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&company=' + company + '&type=' + form_type + '&count=100&output=xml'
-
-
-def get_page(link: str) -> bs4.BeautifulSoup:
-    return bs4.BeautifulSoup(r.get(link).text, 'html.parser')
-
-
-def next_pages(page: bs4.BeautifulSoup) -> list:
-    pages = [page]
-    next_page = page.find('span', {'id': 'next'})
-    while next_page is not None:
-        page = get_page(next_page.a['href'])
-        pages.append(page)
-        next_page = page.find('span', {'id': 'next'})
-
-    return pages
-
-
-def grab_docs_links(page: bs4.BeautifulSoup) -> list:
-    all_links = []
-    all_pages = next_pages(page)
-    for page in all_pages:
-        t = page.find('table', {'class': 'results'})
-        links = [l['href'] for l in t.find_all('a')]
-        all_links += links
-
-    return all_links
-
-
-def get_holdings(page: bs4.BeautifulSoup, output='df') -> pd.DataFrame:
-    table = page.find('table', {'summary': 'Form 13F-NT Header Information'})
-
-    if output == 'df':
-        ret = clean_holdings(pd.read_html(table.prettify())[0])
-
-    return ret
-
-
-def clean_holdings(df: pd.DataFrame) -> pd.DataFrame:
-    df.columns = df.iloc[2]
-    df.drop([0, 1, 2], inplace=True)
-    return df
-
-
-def get_CIKs():
-    cik = 'https://www.sec.gov/cgi-bin/cik_lookup'
-    return cik
-
-
-def main():
-    """
-    1. given list of companies, gather all of the CIKs using cik_lookup
-    """
-
-    companies = ['Renaissance Technologies', 'Two Sigma Investments', 'Bridgewater Associates',
-                    'AQR Capital Management', 'Millennium Management', 'Elliott Management', 'BlackRock', 'Citadel LLC']
-    links = list(map(search_link, companies))
-    pages = list(map(get_page, links))
-    document_links = list(map(grab_docs_links, pages))
-    doc_pages = list(map(get_page, document_links))
-
[…]

### 2020-01-01 random/pythonstuff/fin/test_edgar.py

@@ -1,22 +1,0 @@
-import edgar as ed
-
-
-def test_get_links(companies: list) -> list:
-    
-    return list(map(ed.search_link, companies))
-
-# example link : https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&company=Renaissance+Technologies&type=13F-HR&output=xml
-               # https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&company=Renaissance+Technologies&type=13F-HR&count=100&output=xml
-# https://www.sec.gov/cgi-bin/browse-edgar?
-# action=getcompany
-# &company=Renaissance+Technologies
-# &type=13F-HR
-# &output=xml
-
-
-if __name__ == "__main__":
-    companies = ['Renaissance Technologies', 'Two Sigma Investments', 'Bridgewater Associates',
-                 'AQR Capital Management', 'Millennium Management', 'Elliott Management', 'BlackRock', 'Citadel LLC']
-    links = test_get_links(companies)
-    print(links)
-

### 2020-01-01 random/career_preparation/resume/resume.tex
moved fin to separate repo, updated resume

@@
 \textbf{University of Chicago}
-{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun, 2021}\\
+{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun 2021}\\
 \textbf{Santa Clara High School} \hfill \textbf{2017}
@@
 \section{SKILLS}
-\textbf{Languages:} Python, Julia, Go, Bash, C\\
+\textbf{Languages:} Python, Julia, Go, Bash, C/C++\\
 \textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
@@
 \section{EXPERIENCE}
-\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun 24 - Aug 31 2019}\\
-\textbullet{Researched the applications of neural differential equations to astronomy for the Large Synoptic Survey Telescope\\}
+\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
+\textbullet{Researched the applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
 \textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
-\textbullet{Presented a poster of my work on Neural-ODEs at the 2019 LSST Conference in Arizona}\\
+\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
 \textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
@@
 \textbullet{Have collected over 1 GBs of data using Linux virtual machines on Google Cloud }\\
-\textbullet{Trained TensorFlow win/loss classification and LSTM odds prediction neural network models on Sips data}\\
+\textbullet{Trained TensorFlow win/loss classification and LSTM time-series prediction neural network models on Sips data}\\
 \textbullet{Wrote Flask app to visualize odds using Matplotlib}
@@
 \textbullet{Agent takes actions to buy the home team or the away team moneyline, and receives reward at the end of the game}\\
-\textbullet{Agent learns hedging strategies to mitigate risk}
+\textbullet{Agent learns risk mitigating hedging strategies}
 
@@
 \textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
-\textbullet{We have 50 facebook group members and 10 active members}\\
+\textbullet{We have 50 Facebook group members and 10 active members}\\
 \textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\

### 2020-01-19 random/career_preparation/resume/resume.tex
gan going thru training but not really any results

@@
 \textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
-\textbullet{Created Python package to track odds and statistics for a variety of sports\\}
-\textbullet{Have collected over 1 GBs of data using Linux virtual machines on Google Cloud }\\
+\textbullet{Attempting to deploy data scrapers that gather information about sports and the odds market, feed this data into different neural network architectures and evaluate model performance.\\}
+\textbullet{Using Linux VMs on Google Cloud, I run Python scripts to track REST APIs for odds and sports statistics websites with BeautifulSoup}\\
 \textbullet{Trained TensorFlow win/loss classification and LSTM time-series prediction neural network models on Sips data}\\

### 2020-01-19 audio/app.py

@@ -17,7 +17,7 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 
-import utils 
+import utils
 
 from flask import Flask, Response, request, render_template
 
@@ -32,22 +32,22 @@ def hello_world():
     return str(utils.FILE_NAMES)
 
 
-@app.route('/sgrams/<int:i>')
+@app.route("/sgrams/<int:i>")
 def display_sgram(i):
     song_name = utils.FILE_NAMES[i]
-    print(f'song_name: {song_name}')
+    print(f"song_name: {song_name}")
     waveform = utils.wavey(song_name)
     specgram = utils.sgram(waveform)
 
     fig = Figure(figsize=(20, 10), dpi=500)
     axis = fig.add_subplot(1, 1, 1, title=str(song_name))
-    axis.imshow(specgram.log2()[0, :, :].numpy(), cmap='rainbow')
+    axis.imshow(specgram.log2()[0, :, :].numpy(), cmap="rainbow")
     output = io.BytesIO()
     FigureCanvasAgg(fig).print_png(output)
     return Response(output.getvalue(), mimetype="image/png")
 
 
-@app.route('/waves/<int:i>')
+@app.route("/waves/<int:i>")
 def display_wave(i):
     song_name = utils.FILE_NAMES[i]
     wave = utils.wavey(song_name)

### 2020-01-19 audio/gen.py

@@ -1,0 +1,208 @@
+import time
+import os
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+
+from torch.utils.data import Dataset, DataLoader
+
+import torchaudio
+
+from scipy.io.wavfile import write
+import matplotlib.pyplot as plt
+
+import utils
+
+GEN_PATH = 'gen.pth'
+DISC_PATH = 'disc.pth'
+DIRECTORY = "/home/sippycups/Music/2018/"
+FILE_NAMES = os.listdir(DIRECTORY)
+
+FAKES_PATH = 'samples/'
+
+WINDOW_LEN = 50000
+GEN_LATENT = WINDOW_LEN // 100
+
+
+class Generator(nn.Module):
+    def __init__(self, window=WINDOW_LEN):
+        super(Generator, self).__init__()
+        self.l1 = nn.Linear(GEN_LATENT, GEN_LATENT)
+        # self.l2 = nn.Linear(GEN_LATENT, WINDOW_LEN // 10)
+        # self.l3 = nn.Linear(WINDOW_LEN // 10, GEN_LATENT)
+        self.l4 = nn.Linear(GEN_LATENT, WINDOW_LEN)
+
+    def forward(self, x):
+        x = F.relu(self.l1(x))
+        x = F.relu(self.l2(x))
+        x = F.relu(self.l3(x))
+        x = F.relu(self.l4(x))
+        return x
+
+
+class Discriminator(nn.Module):
+    def __init__(self, window=WINDOW_LEN):
+        super(Discriminator, self).__init__()
+        self.l1 = nn.Linear(WINDOW_LEN, WINDOW_LEN // 16)
+        # self.l2 = nn.Linear(WINDOW_LEN // 4, WINDOW_LEN // 16)
+        # self.l3 = nn.Linear(WINDOW_LEN // 16, WINDOW_LEN // 16)
+        self.l4 = nn.Linear(WINDOW_LEN // 16, 1)
+
+    def forward(self, x):
+        x = F.relu(self.l1(x))
+        x = F.relu(self.l2(x))
+        x = F.relu(self.l3(x))
+        x = F.relu(self.l4(x))
+        return F.softmax(x, dim=0)
+
+
+class Waveys(Dataset):
+    def __init__(self, window=WINDOW_LEN):
+        wave = utils.wavey(filename='81 - 2018 - 09 2 18 18.wav')
+        self.w = wave[0][0]
+        self.sample_rate = wave[1]
[…]

### 2020-01-19 audio/utils.py

@@ -1,16 +1,28 @@
 import os
 import torch
 import torchaudio
-import matplotlib.pyplot as plt
 
-
-DIRECTORY = "/home/sippycups/Music/2019/"
+DIRECTORY = "/home/sippycups/Music/2018/"
 FILE_NAMES = os.listdir(DIRECTORY)
-
+WINDOW_LEN = 10000
 
 def sgram(wave):
     return torchaudio.transforms.Spectrogram()(wave)
 
 
-def wavey(filename):
-    return torchaudio.load(DIRECTORY + filename)[0]
+def wavey(filename=FILE_NAMES[0]):
+    return torchaudio.load(DIRECTORY + filename)
+
+
+def data_windows(n: int = 100000):
+    m = len(FILE_NAMES)
+    d = {}
+    for i, fn in enumerate(FILE_NAMES):
+        t = wavey(fn)
+        window = t[0][i*n:(i+1)*n]
+        if n > len(window):
+            d[fn] = i
+            break
+    return d
+
+

### 2020-01-19 audio/window.py

@@ -7,9 +7,6 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 
-from sips.h import helpers 
-
-
 if __name__ == "__main__":
-    
+
     pass

### 2020-01-19 random/pythonstuff/intro_to_flask/app/hello.py

@@ -1,13 +1,49 @@
-from flask import Flask
+import io
+import json
+import argparse
+import os
+import random
+import math
 
-app = Flask(__name__)
+from PIL import Image
+from flask import Flask, jsonify, request
+
+import gym
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from collections import namedtuple
+from itertools import count
+from PIL import Image
+
+import torch
+import torch.nn as nn
+import torchaudio
+
+import torch.optim as optim
+import torch.nn.functional as F
+import torchvision.transforms as T
+
+import torch.nn.parallel
+import torch.backends.cudnn as cudnn
+import torch.utils.data
+
+import matplotlib.animation as animation
+from IPython.display import HTML
 
 
-@app.route("/")
-def index():
-    return "Index Page"
+device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 
 
-@app.route("/hello")
-def hello_world():
-    return "Hello, World!"
+DIR = "/home/sippycups/Music/2018/"
+FNS = os.listdir(DIR)
+
+if __name__ == "__main__":
+    waveform, sample_rate = torchaudio.load(DIR + FNS[0])
+    print("Shape of waveform: {}".format(waveform.size()))
+    print("Sample rate of waveform: {}".format(sample_rate))
+
+    plt.figure()
+    plt.plot(waveform.t().numpy())
+    plt.show()

### 2020-01-19 audio/gen.py
new dir for each audio gen run

@@ -87,10 +87,13 @@ def weights_init(m):
 def train(load_trained=False, write_gen=True):
     device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
     # device = torch.device('cpu')
-
+    time_dir = time.asctime()
     if write_gen:
         if not os.path.isdir(FAKES_PATH):
             os.mkdir(FAKES_PATH)
+            os.mkdir(time_dir)
+
+    WAV_WRITE_PATH = FAKES_PATH + time_dir + '/'
 
     ngpu = 1
     workers = 4
@@ -153,10 +156,8 @@ def train(load_trained=False, write_gen=True):
 
             fake = netG(noise)
             label.fill_(fake_label)
-            # print(f'fake :{fake}')
-
             output = netD(fake.detach()).view(-1)
-            print(f'fake_desc out: {output}')
+
             errD_fake = criterion(output, label)
             errD_fake.backward()
             D_G_z1 = output.mean().item()
@@ -170,13 +171,13 @@ def train(load_trained=False, write_gen=True):
             errG.backward()
             D_G_z2 = output.mean().item()
             optimizerG.step()
-
+            
             with torch.no_grad():
                 fake = netG(fixed_noise).detach().cpu()
                 if write_gen:
-                    write(FAKES_PATH + 'fake_' + str(epoch) + '_' +
+                    write(WAV_WRITE_PATH + 'fake_' + str(epoch) + '_' +
                           str(i) + '.wav', 44100, fake.detach().cpu().numpy().T)
-                          
+                    
                     # write(FAKES_PATH + 'real_' + str(epoch) + '_' + str(i) +
                     #       '.wav', 44100, real_cpu.detach().cpu().numpy().T)
 
@@ -184,6 +185,8 @@ def train(load_trained=False, write_gen=True):
                 print('[%d/%d][%d/%d]\tLoss_D: %.4f\tLoss_G: %.4f\tD(x): %.4f\tD(G(z)): %.4f / %.4f'
                       % (epoch, num_epochs, i, len(dataloader),
                          errD.item(), errG.item(), D_x, D_G_z1, D_G_z2))
+
+                print(f'fake: {fake}')
 
             G_losses.append(errG.item())
             D_losses.append(errD.item())

### 2020-01-19 audio/gen.py
removed models from git as they are massive

@@ -7,6 +7,7 @@ import torch.nn.functional as F
 import torch.optim as optim
 
 from torch.utils.data import Dataset, DataLoader
+from torch.utils.tensorboard import SummaryWriter
 
 import torchaudio
 
@@ -22,7 +23,7 @@ FILE_NAMES = os.listdir(DIRECTORY)
 
 FAKES_PATH = 'samples/'
 
-WINDOW_LEN = 50000
+WINDOW_LEN = 40000
 GEN_LATENT = WINDOW_LEN // 100
 
 
@@ -36,8 +37,8 @@ class Generator(nn.Module):
 
     def forward(self, x):
         x = F.relu(self.l1(x))
-        x = F.relu(self.l2(x))
-        x = F.relu(self.l3(x))
+        # x = F.relu(self.l2(x))
+        # x = F.relu(self.l3(x))
         x = F.relu(self.l4(x))
         return x
 
@@ -52,8 +53,8 @@ class Discriminator(nn.Module):
 
     def forward(self, x):
         x = F.relu(self.l1(x))
-        x = F.relu(self.l2(x))
-        x = F.relu(self.l3(x))
+        # x = F.relu(self.l2(x))
+        # x = F.relu(self.l3(x))
         x = F.relu(self.l4(x))
         return F.softmax(x, dim=0)
 
@@ -84,51 +85,86 @@ def weights_init(m):
         nn.init.constant_(m.bias.data, 0)
 
 
-def train(load_trained=False, write_gen=True):
+def prep(load_trained=True, write_gen=True):
     device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-    # device = torch.device('cpu')
+
     time_dir = time.asctime()
+
     if write_gen:
         if not os.path.isdir(FAKES_PATH):
             os.mkdir(FAKES_PATH)
-            os.mkdir(time_dir)
+
+        os.mkdir(FAKES_PATH + time_dir)
 
     WAV_WRITE_PATH = FAKES_PATH + time_dir + '/'
+
+    writer = SummaryWriter()
 
     ngpu = 1
     workers = 4
     batch_size = 128
-    num_epochs = 100
-    lr = 0.0002
+    lr = 0.001
     beta1 = 0.5
 
     dataset = Waveys()
     dataloader = DataLoader(dataset, batch_size=batch_size,
                             shuffle=True, num_workers=workers)
-    # Create the generator
+
     netG = Generator().to(device)
[…]

### 2020-01-19 random/pythonstuff/bc/src/get_new.py

@@ -1,0 +1,5 @@
+import requests as r
+
+import bs4
+
+ROOT = "https://8102.bandcamp.com"

### 2020-01-19 audio/gan.py
moved dataset classes to utils and gan models to gan.py

@@ -1,0 +1,39 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+
+WINDOW_LEN = 40000
+GEN_LATENT = WINDOW_LEN // 100
+
+
+class Generator(nn.Module):
+    def __init__(self, window=WINDOW_LEN):
+        super(Generator, self).__init__()
+        self.l1 = nn.Linear(GEN_LATENT, GEN_LATENT)
+        # self.l2 = nn.Linear(GEN_LATENT, WINDOW_LEN // 10)
+        # self.l3 = nn.Linear(WINDOW_LEN // 10, GEN_LATENT)
+        self.l4 = nn.Linear(GEN_LATENT, WINDOW_LEN)
+
+    def forward(self, x):
+        x = F.relu(self.l1(x))
+        # x = F.relu(self.l2(x))
+        # x = F.relu(self.l3(x))
+        x = F.relu(self.l4(x))
+        return x
+
+
+class Discriminator(nn.Module):
+    def __init__(self, window=WINDOW_LEN):
+        super(Discriminator, self).__init__()
+        self.l1 = nn.Linear(WINDOW_LEN, WINDOW_LEN // 16)
+        # self.l2 = nn.Linear(WINDOW_LEN // 4, WINDOW_LEN // 16)
+        # self.l3 = nn.Linear(WINDOW_LEN // 16, WINDOW_LEN // 16)
+        self.l4 = nn.Linear(WINDOW_LEN // 16, 1)
+
+    def forward(self, x):
+        x = F.relu(self.l1(x))
+        # x = F.relu(self.l2(x))
+        # x = F.relu(self.l3(x))
+        x = F.relu(self.l4(x))
+        return F.softmax(x, dim=0)

### 2020-01-19 audio/gen.py

@@ -15,6 +15,7 @@ from scipy.io.wavfile import write
 import matplotlib.pyplot as plt
 
 import utils
+import gan
 
 GEN_PATH = 'gen.pth'
 DISC_PATH = 'disc.pth'
@@ -25,56 +26,6 @@ FAKES_PATH = 'samples/'
 
 WINDOW_LEN = 40000
 GEN_LATENT = WINDOW_LEN // 100
-
-
-class Generator(nn.Module):
-    def __init__(self, window=WINDOW_LEN):
-        super(Generator, self).__init__()
-        self.l1 = nn.Linear(GEN_LATENT, GEN_LATENT)
-        # self.l2 = nn.Linear(GEN_LATENT, WINDOW_LEN // 10)
-        # self.l3 = nn.Linear(WINDOW_LEN // 10, GEN_LATENT)
-        self.l4 = nn.Linear(GEN_LATENT, WINDOW_LEN)
-
-    def forward(self, x):
-        x = F.relu(self.l1(x))
-        # x = F.relu(self.l2(x))
-        # x = F.relu(self.l3(x))
-        x = F.relu(self.l4(x))
-        return x
-
-
-class Discriminator(nn.Module):
-    def __init__(self, window=WINDOW_LEN):
-        super(Discriminator, self).__init__()
-        self.l1 = nn.Linear(WINDOW_LEN, WINDOW_LEN // 16)
-        # self.l2 = nn.Linear(WINDOW_LEN // 4, WINDOW_LEN // 16)
-        # self.l3 = nn.Linear(WINDOW_LEN // 16, WINDOW_LEN // 16)
-        self.l4 = nn.Linear(WINDOW_LEN // 16, 1)
-
-    def forward(self, x):
-        x = F.relu(self.l1(x))
-        # x = F.relu(self.l2(x))
-        # x = F.relu(self.l3(x))
-        x = F.relu(self.l4(x))
-        return F.softmax(x, dim=0)
-
-
-class Waveys(Dataset):
-    def __init__(self, window=WINDOW_LEN):
-        wave = utils.wavey(filename='81 - 2018 - 09 2 18 18.wav')
-        self.w = wave[0][0]
-        self.sample_rate = wave[1]
-        print(self.sample_rate)
-        self.length = len(self.w) // window - 1
-        self.window = window
-
-    def __len__(self):
-        return self.length
-
-    def __getitem__(self, idx):
[…]

### 2020-01-19 audio/utils.py

@@ -1,17 +1,19 @@
 import os
 import torch
 import torchaudio
+from torch.utils.data import Dataset, DataLoader
 
 DIRECTORY = "/home/sippycups/Music/2018/"
 FILE_NAMES = os.listdir(DIRECTORY)
 WINDOW_LEN = 10000
 
+
 def sgram(wave):
     return torchaudio.transforms.Spectrogram()(wave)
 
 
-def wavey(filename=FILE_NAMES[0]):
-    return torchaudio.load(DIRECTORY + filename)
+def wavey(fn=FILE_NAMES[0]):
+    return torchaudio.load(DIRECTORY + fn)
 
 
 def data_windows(n: int = 100000):
@@ -26,3 +28,33 @@ def data_windows(n: int = 100000):
     return d
 
 
+class Waveys(Dataset):
+    def __init__(self, fn='81 - 2018 - 09 2 18 18.wav', window=WINDOW_LEN):
+        wave = wavey(fn=fn)
+        self.w = wave[0][0]
+        self.sample_rate = wave[1]
+        print(self.sample_rate)
+        self.length = len(self.w) // window - 1
+        self.window = window
+
+    def __len__(self):
+        return self.length
+
+    def __getitem__(self, idx):
+        # x = self.w[idx*self.window:(idx + 1)*self.window]
+
+        # warning
+        x = self.w[10*self.window:11*self.window]
+        return x.view(1, -1)
+
+
+class Files(Dataset):
+    def __init__(self, dir=DIRECTORY):
+        self.fns = [DIRECTORY + f for f in FILE_NAMES]
+        self.length = len(self.fns)
+
+    def __len__(self):
+        return self.length
+        
+    def __getitem__(self, idx):
+        return self.fns[idx]

### 2020-01-19 audio/gan.py
vae training and making some COOL stuff

@@ -3,17 +3,15 @@ import torch.nn as nn
 import torch.nn.functional as F
 import torch.optim as optim
 
-WINDOW_LEN = 40000
-GEN_LATENT = WINDOW_LEN // 100
 
 
 class Generator(nn.Module):
-    def __init__(self, window=WINDOW_LEN):
+    def __init__(self, in_dim, out_dim):
         super(Generator, self).__init__()
-        self.l1 = nn.Linear(GEN_LATENT, GEN_LATENT)
+        self.l1 = nn.Linear(in_dim, in_dim)
         # self.l2 = nn.Linear(GEN_LATENT, WINDOW_LEN // 10)
         # self.l3 = nn.Linear(WINDOW_LEN // 10, GEN_LATENT)
-        self.l4 = nn.Linear(GEN_LATENT, WINDOW_LEN)
+        self.l4 = nn.Linear(in_dim, out_dim)
 
     def forward(self, x):
         x = F.relu(self.l1(x))
@@ -24,12 +22,12 @@ class Generator(nn.Module):
 
 
 class Discriminator(nn.Module):
-    def __init__(self, window=WINDOW_LEN):
+    def __init__(self, in_dim):
         super(Discriminator, self).__init__()
-        self.l1 = nn.Linear(WINDOW_LEN, WINDOW_LEN // 16)
+        self.l1 = nn.Linear(in_dim, in_dim // 16)
         # self.l2 = nn.Linear(WINDOW_LEN // 4, WINDOW_LEN // 16)
         # self.l3 = nn.Linear(WINDOW_LEN // 16, WINDOW_LEN // 16)
-        self.l4 = nn.Linear(WINDOW_LEN // 16, 1)
+        self.l4 = nn.Linear(in_dim // 16, 1)
 
     def forward(self, x):
         x = F.relu(self.l1(x))
@@ -37,3 +35,4 @@ class Discriminator(nn.Module):
         # x = F.relu(self.l3(x))
         x = F.relu(self.l4(x))
         return F.softmax(x, dim=0)
+

### 2020-01-19 audio/gen.py

@@ -17,14 +17,14 @@ import matplotlib.pyplot as plt
 import utils
 import gan
 
-GEN_PATH = 'gen.pth'
-DISC_PATH = 'disc.pth'
+GEN_PATH = 'gen_smol.pth'
+DISC_PATH = 'disc_smol.pth'
 DIRECTORY = "/home/sippycups/Music/2018/"
 FILE_NAMES = os.listdir(DIRECTORY)
 
 FAKES_PATH = 'samples/'
 
-WINDOW_LEN = 40000
+WINDOW_LEN = 1024
 GEN_LATENT = WINDOW_LEN // 100
 
 def weights_init(m):
@@ -53,16 +53,16 @@ def prep(load_trained=True, write_gen=True):
 
     ngpu = 1
     workers = 4
-    batch_size = 128
+    batch_size = 1
     lr = 0.001
     beta1 = 0.5
 
-    dataset = utils.Waveys()
+    dataset = utils.Waveys(window=WINDOW_LEN)
     dataloader = DataLoader(dataset, batch_size=batch_size,
                             shuffle=True, num_workers=workers)
 
-    netG = gan.Generator().to(device)
-    netD = gan.Discriminator().to(device)
+    netG = gan.Generator(GEN_LATENT, WINDOW_LEN).to(device)
+    netD = gan.Discriminator(WINDOW_LEN).to(device)
 
     if device.type == 'cuda':
         netG = nn.DataParallel(netG, list(range(ngpu)))
@@ -73,6 +73,10 @@ def prep(load_trained=True, write_gen=True):
             netG.load_state_dict(torch.load(GEN_PATH))
             netD.load_state_dict(torch.load(DISC_PATH))
         except RuntimeError:
+            print('applying new weights')
+            netG.apply(weights_init)
+            netD.apply(weights_init)
+        except FileNotFoundError:
             print('applying new weights')
             netG.apply(weights_init)
             netD.apply(weights_init)
@@ -124,12 +128,11 @@ def train_epoch(d=None, load_trained=True, write_gen=True):
     iters = 0
 
     for i, data in enumerate(dataloader, 0):
-        print(f'i: {i}')
         netD.zero_grad()
 
         real_cpu = data[0].to(device)
-
         b_size = real_cpu.size(0)
+
         label = torch.full((b_size,), real_label, device=device)
         output = netD(real_cpu).view(-1)
 
@@ -166,11 +169,13 @@ def train_epoch(d=None, load_trained=True, write_gen=True):
[…]

### 2020-01-19 audio/utils.py

@@ -5,7 +5,6 @@ from torch.utils.data import Dataset, DataLoader
 
 DIRECTORY = "/home/sippycups/Music/2018/"
 FILE_NAMES = os.listdir(DIRECTORY)
-WINDOW_LEN = 10000
 
 
 def sgram(wave):
@@ -29,7 +28,7 @@ def data_windows(n: int = 100000):
 
 
 class Waveys(Dataset):
-    def __init__(self, fn='81 - 2018 - 09 2 18 18.wav', window=WINDOW_LEN):
+    def __init__(self, window, fn='81 - 2018 - 09 2 18 18.wav'):
         wave = wavey(fn=fn)
         self.w = wave[0][0]
         self.sample_rate = wave[1]
@@ -41,10 +40,10 @@ class Waveys(Dataset):
         return self.length
 
     def __getitem__(self, idx):
-        # x = self.w[idx*self.window:(idx + 1)*self.window]
+        x = self.w[idx*self.window:(idx + 1)*self.window]
 
         # warning
-        x = self.w[10*self.window:11*self.window]
+        # x = self.w[10*self.window:11*self.window]
         return x.view(1, -1)
 
 

### 2020-01-19 audio/vae.py

@@ -1,0 +1,35 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+
+class VAE(nn.Module):
+    def __init__(self, dim, bottleneck=50):
+        super(VAE, self).__init__()
+        self.dim = dim
+        self.fc1 = nn.Linear(dim, 400)
+        self.fc21 = nn.Linear(400, bottleneck)
+        self.fc22 = nn.Linear(400, bottleneck)
+        self.fc3 = nn.Linear(bottleneck, 400)
+        self.fc4 = nn.Linear(400, dim)
+
+    def encode(self, x):
+        h1 = F.relu(self.fc1(x))
+        return self.fc21(h1), self.fc22(h1)
+
+    def reparameterize(self, mu, logvar):
+        std = torch.exp(0.5*logvar)
+        eps = torch.randn_like(std)
+        return mu + eps*std
+
+    def decode(self, z):
+        h3 = F.relu(self.fc3(z))
+        # print(f'h3: {h3.shape}')
+        return torch.sigmoid(self.fc4(h3))
+
+    def forward(self, x):
+        # print(x.shape)
+        mu, logvar = self.encode(x)
+        z = self.reparameterize(mu, logvar)
+        # print(z.shape)
+        return self.decode(z), mu, logvar

### 2020-01-19 audio/vaegen.py

@@ -1,0 +1,98 @@
+"""
+
+"""
+import os
+import time
+
+import torch
+from torch.utils.data import DataLoader
+import torchaudio
+from torch.utils.tensorboard import SummaryWriter
+from torch import nn, optim
+from torch.nn import functional as F
+
+import vae
+import utils
+
+
+writer = SummaryWriter()
+
+device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+print(device)
+SAMPLE_RATE = 44100
+WINDOW_LEN = SAMPLE_RATE  # // 2
+LOG_INTERVAL = 500
+BATCH_SIZE = 128
+BOTTLENECK = 50
+
+
+def loss_function(recon_x, x, mu, logvar):
+    # BCE = F.binary_cross_entropy(
+    #     recon_x, x.view(-1, WINDOW_LEN), reduction='sum')
+    BCE = F.binary_cross_entropy(
+        recon_x, x, reduction='sum')
+    KLD = -0.5 * torch.sum(1 + logvar - mu.pow(2) - logvar.exp())
+    return BCE + KLD
+
+
+def train(train_loader, epoch):
+    model.train()
+    train_loss = 0
+    for batch_idx, data in enumerate(train_loader):
+        data = data.to(device)
+        optimizer.zero_grad()
+        recon_batch, mu, logvar = model(data)
+        loss = loss_function(recon_batch, data, mu, logvar)
+        writer.add_scalar('train_loss', loss)
+        loss.backward()
+        train_loss += loss.item()
+        optimizer.step()
+        if batch_idx % LOG_INTERVAL == 0:
+            print('Train Epoch: {} [{}/{} ({:.0f}%)]\tLoss: {:.6f}'.format(
+                epoch, batch_idx * len(data), len(train_loader.dataset),
+                100. * batch_idx / len(train_loader),
+                loss.item() / len(data)))
+
+    print('====> Epoch: {} Average loss: {:.4f}'.format(
+          epoch, train_loss / len(train_loader.dataset)))
+
+
+def test(test_loader, epoch):
+    model.eval()
+    test_loss = 0
+    with torch.no_grad():
+        for i, (data, _) in enumerate(test_loader):
+            data = data.to(device)
+            recon_batch, mu, logvar = model(data)
+            test_loss += loss_function(recon_batch, data, mu, logvar).item()
+            if i == 0:
+                n = min(data.size(0), 8)
[…]

### 2020-01-19 audio/vaegen.py
vae training and making some COOL stuff

@@ -17,10 +17,11 @@ import utils
 
 writer = SummaryWriter()
 
-device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+# device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+device = torch.device("cpu"
 print(device)
 SAMPLE_RATE = 44100
-WINDOW_LEN = SAMPLE_RATE  # // 2
+WINDOW_LEN = SAMPLE_RATE * 5 
 LOG_INTERVAL = 500
 BATCH_SIZE = 128
 BOTTLENECK = 50

### 2020-01-19 audio/utils.py
fileloader for vae and saving, loss goes to inf tho

@@ -29,10 +29,10 @@ def data_windows(n: int = 100000):
 
 class Waveys(Dataset):
     def __init__(self, window, fn='81 - 2018 - 09 2 18 18.wav'):
-        wave = wavey(fn=fn)
+        wave = torchaudio.load(filepath=fn)
         self.w = wave[0][0]
         self.sample_rate = wave[1]
-        print(self.sample_rate)
+        # print(self.sample_rate)
         self.length = len(self.w) // window - 1
         self.window = window
 
@@ -41,9 +41,6 @@ class Waveys(Dataset):
 
     def __getitem__(self, idx):
         x = self.w[idx*self.window:(idx + 1)*self.window]
-
-        # warning
-        # x = self.w[10*self.window:11*self.window]
         return x.view(1, -1)
 
 

### 2020-01-19 audio/vae.py

@@ -4,14 +4,14 @@ import torch.nn.functional as F
 import torch.optim as optim
 
 class VAE(nn.Module):
-    def __init__(self, dim, bottleneck=50):
+    def __init__(self, dim, middle=800, bottleneck=50):
         super(VAE, self).__init__()
         self.dim = dim
-        self.fc1 = nn.Linear(dim, 400)
-        self.fc21 = nn.Linear(400, bottleneck)
-        self.fc22 = nn.Linear(400, bottleneck)
-        self.fc3 = nn.Linear(bottleneck, 400)
-        self.fc4 = nn.Linear(400, dim)
+        self.fc1 = nn.Linear(dim, middle)
+        self.fc21 = nn.Linear(middle, bottleneck)
+        self.fc22 = nn.Linear(middle, bottleneck)
+        self.fc3 = nn.Linear(bottleneck, middle)
+        self.fc4 = nn.Linear(middle, dim)
 
     def encode(self, x):
         h1 = F.relu(self.fc1(x))
@@ -24,12 +24,9 @@ class VAE(nn.Module):
 
     def decode(self, z):
         h3 = F.relu(self.fc3(z))
-        # print(f'h3: {h3.shape}')
         return torch.sigmoid(self.fc4(h3))
 
     def forward(self, x):
-        # print(x.shape)
         mu, logvar = self.encode(x)
         z = self.reparameterize(mu, logvar)
-        # print(z.shape)
         return self.decode(z), mu, logvar

### 2020-01-19 audio/vaegen.py

@@ -18,10 +18,10 @@ import utils
 writer = SummaryWriter()
 
 # device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-device = torch.device("cpu"
+device = torch.device("cpu")
 print(device)
 SAMPLE_RATE = 44100
-WINDOW_LEN = SAMPLE_RATE * 5 
+WINDOW_LEN = SAMPLE_RATE * 5
 LOG_INTERVAL = 500
 BATCH_SIZE = 128
 BOTTLENECK = 50
@@ -43,7 +43,10 @@ def train(train_loader, epoch):
         data = data.to(device)
         optimizer.zero_grad()
         recon_batch, mu, logvar = model(data)
-        loss = loss_function(recon_batch, data, mu, logvar)
+        try:
+            loss = loss_function(recon_batch, data, mu, logvar)
+        except:
+            continue
         writer.add_scalar('train_loss', loss)
         loss.backward()
         train_loss += loss.item()
@@ -53,6 +56,11 @@ def train(train_loader, epoch):
                 epoch, batch_idx * len(data), len(train_loader.dataset),
                 100. * batch_idx / len(train_loader),
                 loss.item() / len(data)))
+            with torch.no_grad():
+                sample = torch.randn(1, BOTTLENECK).to(device)
+                sample = model.decode(sample).cpu()
+                torchaudio.save('samples/' + time_dir +
+                                'vaetest' + str(batch_idx) + '_' + str(epoch) + '.wav', sample, 44100)
 
     print('====> Epoch: {} Average loss: {:.4f}'.format(
           epoch, train_loss / len(train_loader.dataset)))
@@ -77,12 +85,10 @@ def test(test_loader, epoch):
 
 if __name__ == "__main__":
 
-    
     epochs = 50
-    
-    train_loader = DataLoader(utils.Waveys(
-        window=WINDOW_LEN), batch_size=BATCH_SIZE)
-    
+
+    fileset = utils.Files()
+    # fileloader = DataLoader(fileset)
     model = vae.VAE(dim=WINDOW_LEN, bottleneck=BOTTLENECK).to(device)
     optimizer = optim.Adam(model.parameters(), lr=1e-3)
 
@@ -90,10 +96,12 @@ if __name__ == "__main__":
     os.mkdir('samples/' + time_dir)
 
     for epoch in range(1, epochs + 1):
-        train(train_loader, epoch)
-        # test(epoch)
-        with torch.no_grad():
[…]

### 2020-01-19 audio/utils.py
removed model from git

@@ -2,7 +2,7 @@ import os
 import torch
 import torchaudio
 from torch.utils.data import Dataset, DataLoader
-
+import numpy as np
 DIRECTORY = "/home/sippycups/Music/2018/"
 FILE_NAMES = os.listdir(DIRECTORY)
 
@@ -41,6 +41,8 @@ class Waveys(Dataset):
 
     def __getitem__(self, idx):
         x = self.w[idx*self.window:(idx + 1)*self.window]
+        if np.nan in x:
+            print('oh no')
         return x.view(1, -1)
 
 

### 2020-01-19 audio/vaegen.py

@@ -22,7 +22,7 @@ device = torch.device("cpu")
 print(device)
 SAMPLE_RATE = 44100
 WINDOW_LEN = SAMPLE_RATE * 5
-LOG_INTERVAL = 500
+LOG_INTERVAL = 5
 BATCH_SIZE = 128
 BOTTLENECK = 50
 
@@ -35,6 +35,7 @@ def loss_function(recon_x, x, mu, logvar):
     KLD = -0.5 * torch.sum(1 + logvar - mu.pow(2) - logvar.exp())
     return BCE + KLD
 
+loss_fn = nn.MSELoss()
 
 def train(train_loader, epoch):
     model.train()
@@ -43,10 +44,8 @@ def train(train_loader, epoch):
         data = data.to(device)
         optimizer.zero_grad()
         recon_batch, mu, logvar = model(data)
-        try:
-            loss = loss_function(recon_batch, data, mu, logvar)
-        except:
-            continue
+        loss = loss_function(recon_batch, data, mu, logvar)
+        # loss = loss_fn()
         writer.add_scalar('train_loss', loss)
         loss.backward()
         train_loss += loss.item()

### 2020-01-19 audio/utils.py
stereo vae

@@ -3,7 +3,7 @@ import torch
 import torchaudio
 from torch.utils.data import Dataset, DataLoader
 import numpy as np
-DIRECTORY = "/home/sippycups/Music/2018/"
+DIRECTORY = "/home/sippycups/Music/2019/"
 FILE_NAMES = os.listdir(DIRECTORY)
 
 
@@ -28,22 +28,25 @@ def data_windows(n: int = 100000):
 
 
 class Waveys(Dataset):
-    def __init__(self, window, fn='81 - 2018 - 09 2 18 18.wav'):
+    def __init__(self, window, fn='5 14 19 matt anand ilan.wav'):
         wave = torchaudio.load(filepath=fn)
-        self.w = wave[0][0]
+        self.w = wave[0]
         self.sample_rate = wave[1]
         # print(self.sample_rate)
-        self.length = len(self.w) // window - 1
+        self.length = len(self.w[0]) // window - 1
         self.window = window
 
     def __len__(self):
         return self.length
 
     def __getitem__(self, idx):
-        x = self.w[idx*self.window:(idx + 1)*self.window]
+        l = self.w[0][idx*self.window:(idx + 1)*self.window]
+        r = self.w[1][idx*self.window:(idx + 1)*self.window]
+        x = torch.cat([l, r])
+        # print(x)
         if np.nan in x:
             print('oh no')
-        return x.view(1, -1)
+        return l.view(1, -1)
 
 
 class Files(Dataset):

### 2020-01-19 audio/vaegen.py

@@ -21,10 +21,10 @@ writer = SummaryWriter()
 device = torch.device("cpu")
 print(device)
 SAMPLE_RATE = 44100
-WINDOW_LEN = SAMPLE_RATE * 5
+WINDOW_LEN = SAMPLE_RATE * 4
 LOG_INTERVAL = 5
 BATCH_SIZE = 128
-BOTTLENECK = 50
+BOTTLENECK = 100
 
 
 def loss_function(recon_x, x, mu, logvar):
@@ -59,7 +59,7 @@ def train(train_loader, epoch):
                 sample = torch.randn(1, BOTTLENECK).to(device)
                 sample = model.decode(sample).cpu()
                 torchaudio.save('samples/' + time_dir +
-                                'vaetest' + str(batch_idx) + '_' + str(epoch) + '.wav', sample, 44100)
+                                'vaetest' + str(batch_idx) + '_' + str(epoch) + '.wav', sample.view(2, -1), 44100)
 
     print('====> Epoch: {} Average loss: {:.4f}'.format(
           epoch, train_loss / len(train_loader.dataset)))
@@ -93,14 +93,14 @@ if __name__ == "__main__":
 
     time_dir = time.asctime() + '/'
     os.mkdir('samples/' + time_dir)
-
+    fn = '/home/sippycups/Music/2018/81 - 2018 - 119 8 5 18.wav'
     for epoch in range(1, epochs + 1):
 
-        for i, fn in enumerate(fileset):
+        # for i, fn in enumerate(fileset):
 
-            train_loader = DataLoader(utils.Waveys(
-                window=WINDOW_LEN, fn=fn), batch_size=BATCH_SIZE)
+        train_loader = DataLoader(utils.Waveys(
+            window=WINDOW_LEN, fn=fn), batch_size=BATCH_SIZE)
 
-            train(train_loader, epoch*(len(fileset))+i) # file num 
-            # test(epoch)
+        train(train_loader, epoch) # file num 
+        # test(epoch)
 

### 2020-01-19 audio/window.py

@@ -1,4 +1,4 @@
-from matplotlib.figure import Figure
+ from matplotlib.figure import Figure
 
 import torch
 import torchaudio

### 2020-01-19 audio/app.py
midpoint refactor, fileset loading getting removed from vaegen for single song training

@@ -17,11 +17,7 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 
-<<<<<<< HEAD
 import utils
-=======
-import utils 
->>>>>>> e60167c381df48112b1ddea943d77929a617e14f
 
 from flask import Flask, Response, request, render_template
 

### 2020-01-19 audio/utils.py

@@ -15,6 +15,11 @@ def wavey(fn=FILE_NAMES[0]):
     return torchaudio.load(DIRECTORY + fn)
 
 
+def init_run(fn, )
+
+
+    return tensor, relative_path, sample_rate
+
 def data_windows(n: int = 100000):
     m = len(FILE_NAMES)
     d = {}

### 2020-01-19 audio/vaegen.py

@@ -5,14 +5,16 @@ import os
 import time
 
 import torch
-from torch.utils.data import DataLoader
 import torchaudio
-from torch.utils.tensorboard import SummaryWriter
+
 from torch import nn, optim
 from torch.nn import functional as F
 
-import vae
+from torch.utils.data import DataLoader
+from torch.utils.tensorboard import SummaryWriter
+
 import utils
+import vae
 
 
 writer = SummaryWriter()
@@ -35,9 +37,8 @@ def loss_function(recon_x, x, mu, logvar):
     KLD = -0.5 * torch.sum(1 + logvar - mu.pow(2) - logvar.exp())
     return BCE + KLD
 
-loss_fn = nn.MSELoss()
 
-def train(train_loader, epoch):
+def train_epoch(modtrain_loader: DataLoader, fn: str, sample_rate: int, epoch: int, save=False):
     model.train()
     train_loss = 0
     for batch_idx, data in enumerate(train_loader):
@@ -45,27 +46,31 @@ def train(train_loader, epoch):
         optimizer.zero_grad()
         recon_batch, mu, logvar = model(data)
         loss = loss_function(recon_batch, data, mu, logvar)
-        # loss = loss_fn()
-        writer.add_scalar('train_loss', loss)
         loss.backward()
+
+        writer.add_scalar('train_loss', loss)
         train_loss += loss.item()
         optimizer.step()
+
         if batch_idx % LOG_INTERVAL == 0:
             print('Train Epoch: {} [{}/{} ({:.0f}%)]\tLoss: {:.6f}'.format(
                 epoch, batch_idx * len(data), len(train_loader.dataset),
                 100. * batch_idx / len(train_loader),
                 loss.item() / len(data)))
+
             with torch.no_grad():
                 sample = torch.randn(1, BOTTLENECK).to(device)
                 sample = model.decode(sample).cpu()
-                torchaudio.save('samples/' + time_dir +
-                                'vaetest' + str(batch_idx) + '_' + str(epoch) + '.wav', sample.view(2, -1), 44100)
+
+                if save:
+                    torchaudio.save(fn + str(epoch) + '.wav',
+                                    sample.view(2, -1), sample_rate)
 
     print('====> Epoch: {} Average loss: {:.4f}'.format(
[…]

### 2020-02-22 random/career_preparation/resume/resume.tex
updates

--- 2020-01-01 random/career_preparation/resume/resume.tex
@@
 \par
+\normalfont{\textbullet{Abstract Linear Algebra}}
 \normalfont{\textbullet{Algorithms}}
-\normalfont{\textbullet{Discrete Math}}
-\normalfont{\textbullet{Abstract Linear Algebra}}
-\normalfont{\textbullet{Mathematical Logic}}
+\normalfont{\textbullet{Computer Systems}}
+\normalfont{\textbullet{Discrete Math}}\\
+\normalfont{\textbullet{Electronics}}
 \normalfont{\textbullet{Inventing Interactive Devices}}
-\normalfont{\textbullet{Electronics}}
-\normalfont{\textbullet{Computer Systems}}
+\normalfont{\textbullet{Mathematical Logic}}\\
+\normalfont{\textbullet{Molecular Engineering}}
+\normalfont{\textbullet{Quantum Computation}}
 
@@
 \section{SKILLS}
-\textbf{Languages:} Python, Julia, Go, Bash, C/C++\\
+\textbf{Languages:} Python, Julia, Go, Bash, C/C++, SQL\\
 \textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
-\textbf{Spoken:} Fluent English. Classroom Hindi and Spanish
+\textbf{Spoken:} Fluent English. Classroom Hindi, Spanish, and Mandarin
 
@@
     \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
+    \item \textbf{Link :} github.com/deepskies/cosmoNODE and /dsutils
+
 \end{itemize}
+
 \section{PROJECTS}
-\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
-\textbullet{Created Python package to track odds and statistics for a variety of sports\\}
-\textbullet{Have collected over 1 GBs of data using Linux virtual machines on Google Cloud }\\
-\textbullet{Trained TensorFlow win/loss classification and LSTM time-series prediction neural network models on Sips data}\\
-\textbullet{Wrote Flask app to visualize odds using Matplotlib}
+
+\textbf{codebyhand: applying handwriting recognition}\\ 
+\textbullet{Goal: Use handwriting in IDE and match with code suggestions}\\
+\textbullet{Trained convolutional net on Extended MNIST (EMNIST) dataset}\\
+\textbullet{Wrote `paint` program that live infers character after each stroke}\\
+\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
+\textbullet{Todo: character bounding box detection and inference using stroke direction and order}
+
 \begin{itemize}
-\item \textbf{Tools:} Python, Requests, Beautiful Soup, TensorFlow, Flask, Matplotlib
+\item \textbf{Tools:} pytorch, torchvision, torchtext, tkinter 
 \end{itemize}
 \begin{itemize}
-\item \textbf{Link :} github.com/anandijain/sips
+\item \textbf{Link :} github.com/anandijain/codebyhand
 \end{itemize}
-\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
-\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}\\
-\textbullet{Agent takes actions to buy the home team or the away team moneyline, and receives reward at the end of the game}\\
-\textbullet{Agent learns risk mitigating hedging strategies}
 
+\textbf{sippyart: variational-autoencoders for music generation}\\ 
+\textbullet{Preface: I've been making music on my computer for a few years and have uploaded a few hundred tracks by chronology}\\
+\textbullet{Goal: Learn generative models like GANs and autoencoders}\\
+\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders}\\
+\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
+\textbullet{Todo: Make sequential embedding from one audio segment to the next using LSTM with the encoded }
 \begin{itemize}
-\item \textbf{Tools:} Python, Gym, TensorFlow, TF-Agents
+\item \textbf{Tools:} pytorch, torchaudio, torchvision
 \end{itemize}
 \begin{itemize}
-\item \textbf{Link :} github.com/anandijain/gym-sips
+\item \textbf{Link :} github.com/anandijain/sippyart
 \end{itemize}
@@
 
-\textbf{UCQuantum (.org) - Founder/President}
-\hfill \textbf{Aug 2019 - Now}\\
-\textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
-\textbullet{We have 50 Facebook group members and 10 active members}\\
-\textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\
+\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
+\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
+\textbullet{Working through Michael Nielsen and Isaac Chuang's Textbook}\\
+\textbullet{Toured Prof. David Schuster's superconducting qubit lab}\\
+\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}\\
 %-------------------------------------------------------------------------------

### 2020-02-26 random/career_preparation/resume/resume2.tex
update

--- 2020-02-22 random/career_preparation/resume/resume.tex
@@
 \textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
-\textbullet{Researched the applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
-\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
+\textbullet{Researched applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
+\textbullet{Used PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different objects' light curves (brightness over time)}\\
 \textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
@@
 
-\textbf{codebyhand: applying handwriting recognition}\\ 
-\textbullet{Goal: Use handwriting in IDE and match with code suggestions}\\
-\textbullet{Trained convolutional net on Extended MNIST (EMNIST) dataset}\\
-\textbullet{Wrote `paint` program that live infers character after each stroke}\\
-\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
-\textbullet{Todo: character bounding box detection and inference using stroke direction and order}
+\textbf{gym-sips: machine learning in sports betting on google cloud}\\ 
+\textbullet{Collected $\sim$1000 games of NFL, NHL, NBA, and MLB odds and scores on Linux VMs}\\
+\textbullet{Trained/tested LSTM model to predict odds and scores on $\sim$$5\times 10^{5}$ rows of 20 features}\\
+\textbullet{Created a discrete and continuous action space gym environment where agent either picks one team to place money on or allocates some amount to each}\\
+\textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
+\textbullet{Agent learns to hedge across time and returns a positive reward on test set}
 
 \begin{itemize}
-\item \textbf{Tools:} pytorch, torchvision, torchtext, tkinter 
+\item \textbf{Tools:} pytorch, gym, spinningup
 \end{itemize}
 \begin{itemize}
-\item \textbf{Link :} github.com/anandijain/codebyhand
+\item \textbf{Link :} github.com/anandijain/sips and /gym-sips
 \end{itemize}
-
 \textbf{sippyart: variational-autoencoders for music generation}\\ 
-\textbullet{Preface: I've been making music on my computer for a few years and have uploaded a few hundred tracks by chronology}\\
 \textbullet{Goal: Learn generative models like GANs and autoencoders}\\
@@
 \textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
-\textbullet{Todo: Make sequential embedding from one audio segment to the next using LSTM with the encoded }
+\textbullet{Todo: Make sequential embedding from one audio segment to the next using LSTM}
 \begin{itemize}
@@
 \textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
-\textbullet{Working through Michael Nielsen and Isaac Chuang's Textbook}\\
-\textbullet{Toured Prof. David Schuster's superconducting qubit lab}\\
-\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}\\
+\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
+\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
 %-------------------------------------------------------------------------------

### 2020-02-27 random/career_preparation/resume/resume2.tex
font

@@
 % Default font is the helvetica postscript font
-\usepackage{helvet}
+% \usepackage{avant}
+% \setupbodyfont[ss]
 
@@
 \textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
-\textbullet{Agent learns to hedge across time and returns a positive reward on test set}
+\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}
 
@@
 \textbf{sippyart: variational-autoencoders for music generation}\\ 
-\textbullet{Goal: Learn generative models like GANs and autoencoders}\\
-\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders}\\
+\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders running on GPU}\\
 \textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
-\textbullet{Todo: Make sequential embedding from one audio segment to the next using LSTM}
 \begin{itemize}

### 2020-02-29 random/career_preparation/resume/resume2.tex
update

@@
 
-\textbf{gym-sips: machine learning in sports betting on google cloud}\\ 
+\textbf{gym-sips: machine learning in sports betting on google cloud}\hfill\\ 
 \textbullet{Collected $\sim$1000 games of NFL, NHL, NBA, and MLB odds and scores on Linux VMs}\\
-\textbullet{Trained/tested LSTM model to predict odds and scores on $\sim$$5\times 10^{5}$ rows of 20 features}\\
-\textbullet{Created a discrete and continuous action space gym environment where agent either picks one team to place money on or allocates some amount to each}\\
+\textbullet{Created discrete and continuous action space gym environment for asset allocation}\\
 \textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
@@
 \end{itemize}
-
+\textbf{codebyhand: applying handwriting recognition}\\ 
+\textbullet{Wrote `paint` program that infers EMNIST characters after each stroke and allows transfer learning on own handwriting}\\
+\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
+\begin{itemize}
+\item \textbf{Tools:} pytorch, torchvision, tkinter 
+\end{itemize}
+\begin{itemize}
+\item \textbf{Link :} github.com/anandijain/codebyhand
+\end{itemize}
 \section{ACTIVITIES}
-
 \textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
@@
 %-------------------------------------------------------------------------------
-
 \end{resume}

### 2020-03-07 random/career_preparation/resume/resume2.tex
deepmind covid pdb viewer
updates

@@
 
-\textbf{gym-sips: machine learning in sports betting on google cloud}\hfill\\ 
-\textbullet{Collected $\sim$1000 games of NFL, NHL, NBA, and MLB odds and scores on Linux VMs}\\
+\textbf{gym-sips: reinforcement learning in sports betting on google cloud}\hfill\\ 
+\textbullet{Concurrent scraping live odds and scores $\sim$500 games/day on Linux virtual machines}\\
 \textbullet{Created discrete and continuous action space gym environment for asset allocation}\\
@@
 \begin{itemize}
-\item \textbf{Tools:} pytorch, gym, spinningup
+\item \textbf{Tools:} pytorch, gym, spinningup, go
 \end{itemize}
 \begin{itemize}
-\item \textbf{Link :} github.com/anandijain/sips and /gym-sips
+\item \textbf{Link :} github.com/anandijain/sips /sipgo /gym-sips 
 \end{itemize}

### 2020-03-07 cpp/proj/main.cpp

@@ -4,6 +4,11 @@
 
 using namespace std;
 
+struct Node {
+    Person p;
+    struct Node* next;
+}
+
 class Person{
     private:
         string id;

### 2020-03-07 haskell/first.hs

@@ -1,4 +1,3 @@
-doubleMe x = x + x
-
-
-doubleThem x y = doubleMe x + doubleMe y
+curl -X GET -H "Content-type: application/json" -H "Accept: application/json"
+"https://api.citrixonline.com/oauth/access_token?grant_type=password&user_id=test@test.com&password=xyz&client_id=123"
+curl -o curltest.html 'https://www.bovada.lv/services/sports/event/v2/events/A/description/volleyball/brazil' -H 'DNT: 1' -H 'Upgrade-Insecure-Requests: 1' -H 'User-Agent: Mozilla/5.0 (X11; Linux x86_64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/80.0.3987.122 Safari/537.36' -H 'Sec-Fetch-Dest: document' --compressed

### 2020-03-10 random/career_preparation/cover_letters/general/AQR.tex
updates

\documentclass[11pt,a4paper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\begin{document}

Dear AQR,

I am interested in the Research Analyst position for Summer 2020.
I have experience managing cloud instances, SQL databases, and on-line machine learning.
My project to track sports data is reflective of this. 
Initially in python and dreadfully slow, I could only gather a few sports every couple of minutes.
After porting my code to Golang and concurrently requesting REST endpoints, I am able to track 2000+ sports in under 30 seconds.
Additionally, now that the script writes to a Cloud SQL database, instead of CSVs, it is easier to track neural network predictions from PyTorch.
I realize there is still much to improve with my project (submit a PR!), but I see my ability to identify bottlenecks and iterate as a great strength. 
I believe this project demonstrates why I am fit for this position.

I hope to hear from you.

Thank you,

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain

\end{document}

### 2020-03-10 random/career_preparation/cover_letters/general/betfair.tex
updates

\documentclass[10pt,a4paper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\begin{document}

Dear Betfair,

I am interested in a summer internship, although I do not have a visa to work in Dublin.

I have built a Go scraper for Bovada that runs concurrently and gets the scores and moneylines for 1600+ games in 25 seconds.

I check the changes from the previous heartbeat and write these to disk, for use in Pytorch training.

I have built Long Short Term Memory networks, 1D-convolutional networks, and reinforcement learning agents for this data and feel confident in implementing classical and neural network machine learning applications.

One thing that excites me about working at Betfair is the ability to analyze and understand exchanges and behavioral economics in a domain outside of traditional finance.

A specific question that I have is on whether or not liquidity is a financial analog that holds in sports exchanges.

I hope you consider me for a position this summer.

Thank you,

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain

\end{document}

### 2020-03-10 random/career_preparation/resume/resume2.tex
updates

@@
 \section{SKILLS}
-\textbf{Languages:} Python, Julia, Go, Bash, C/C++, SQL\\
+\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL\\
 \textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
@@
 \textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
-\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
-\begin{itemize}
-    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
-    \item \textbf{Link :} github.com/deepskies/cosmoNODE and /dsutils
-
-\end{itemize}
+\textbullet{Worked with peers and mentors to create a high level API for Auto-ML and visualization of astronomy datasets, primarily in PyTorch and Matplotlib}\\
+\textbf{tools:} DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Python, Julia\\
+\textbf{src :} deepskies/cosmoNODE and deepskies/dsutils
 
@@
 \textbf{gym-sips: reinforcement learning in sports betting on google cloud}\hfill\\ 
-\textbullet{Concurrent scraping live odds and scores $\sim$500 games/day on Linux virtual machines}\\
+\textbullet{Concurrent scraping $\sim$1000 games/day of odds, scores on Linux VM to Cloud SQL}\\
 \textbullet{Created discrete and continuous action space gym environment for asset allocation}\\
 \textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
-\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}
+\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}\\
+\textbf{tools:} pytorch, gym, spinningup, go\\
+\textbf{src :} github.com/anandijain/sips /sipgo and /gym-sips
 
-\begin{itemize}
-\item \textbf{Tools:} pytorch, gym, spinningup, go
-\end{itemize}
-\begin{itemize}
-\item \textbf{Link :} github.com/anandijain/sips /sipgo /gym-sips 
-\end{itemize}
 \textbf{sippyart: variational-autoencoders for music generation}\\ 
@@
 \textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
-\begin{itemize}
-\item \textbf{Tools:} pytorch, torchaudio, torchvision
-\end{itemize}
-\begin{itemize}
-\item \textbf{Link :} github.com/anandijain/sippyart
-\end{itemize}
+\textbf{tools:} pytorch, torchaudio, torchvision, opencv\\
+\textbf{src :} github.com/anandijain/sippyart
+
 \textbf{codebyhand: applying handwriting recognition}\\ 
@@
 \textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
-\begin{itemize}
-\item \textbf{Tools:} pytorch, torchvision, tkinter 
-\end{itemize}
-\begin{itemize}
-\item \textbf{Link :} github.com/anandijain/codebyhand
-\end{itemize}
+\textbf{tools:} pytorch, torchvision, tkinter \\
+\textbf{src :} github.com/anandijain/codebyhand\\
+
 \section{ACTIVITIES}

### 2020-03-10 cpp/proj/req.cpp

@@ -1,0 +1,101 @@
+// NOT MINE 
+// credit to connormanning/ https://gist.github.com/connormanning/41efa6075515019e499c
+// g++ req.cpp -ljsoncpp -lcurl -o example.out && ./example.out
+#include <cstdint>
+#include <iostream>
+#include <memory>
+#include <string>
+
+#include <curl/curl.h>
+#include <jsoncpp/json/json.h>
+
+namespace
+{
+    std::size_t callback(
+            const char* in,
+            std::size_t size,
+            std::size_t num,
+            std::string* out)
+    {
+        const std::size_t totalBytes(size * num);
+        out->append(in, totalBytes);
+        return totalBytes;
+    }
+}
+
+int main()
+{
+    const std::string url("https://www.bovada.lv/services/sports/event/v2/events/A/description/volleyball/brazil");
+
+    CURL* curl = curl_easy_init();
+
+    // Set remote URL.
+    curl_easy_setopt(curl, CURLOPT_URL, url.c_str());
+
+    // Don't bother trying IPv6, which would increase DNS resolution time.
+    curl_easy_setopt(curl, CURLOPT_IPRESOLVE, CURL_IPRESOLVE_V4);
+
+    // Don't wait forever, time out after 10 seconds.
+    curl_easy_setopt(curl, CURLOPT_TIMEOUT, 10);
+
+    // Follow HTTP redirects if necessary.
+    curl_easy_setopt(curl, CURLOPT_FOLLOWLOCATION, 1L);
+
+    // Response information.
+    long httpCode(0);
+    std::unique_ptr<std::string> httpData(new std::string());
+
+    // Hook up data handling function.
+    curl_easy_setopt(curl, CURLOPT_WRITEFUNCTION, callback);
+
+    // Hook up data container (will be passed as the last parameter to the
+    // callback handling function).  Can be any pointer type, since it will
+    // internally be passed as a void pointer.
+    curl_easy_setopt(curl, CURLOPT_WRITEDATA, httpData.get());
+
+    // Run our HTTP GET command, capture the HTTP response code, and clean up.
+    curl_easy_perform(curl);
+    curl_easy_getinfo(curl, CURLINFO_RESPONSE_CODE, &httpCode);
+    curl_easy_cleanup(curl);
+
+    if (httpCode == 200)
+    {
+        std::cout << "\nGot successful response from " << url << std::endl;
+
+        // Response looks good - done using Curl now.  Try to parse the results
[…]

### 2020-03-10 haskell/Main.hs

@@ -1,0 +1,49 @@
+
+{-# LANGUAGE OverloadedStrings #-}
+module Main where
+    
+import Data.Char (intToDigit)
+import Network.HTTP
+import Network.Stream
+import Network.URI
+import System.Environment (getArgs)
+import System.Exit (exitFailure)
+import System.IO (hPutStrLn, stderr)
+
+main = 
+    do
+    args <- getArgs
+    case args of 
+	[addr] -> case parseURI addr of
+		       Nothing -> err "Could not parse URI"
+		       Just uri -> do
+				   cont <- get uri
+			           putStr cont
+	_ -> err "Usage: get <url>"
+
+err :: String -> IO a
+err msg = do 
+	  hPutStrLn stderr msg
+	  exitFailure
+
+get :: URI -> IO String
+get uri =
+    do
+    eresp <- simpleHTTP (request uri)
+    resp <- handleE (err . show) eresp
+    case rspCode resp of
+                      (2,0,0) -> return (rspBody resp)
+                      _ -> err (httpError resp)
+    where
+    showRspCode (a,b,c) = map intToDigit [a,b,c]
+    httpError resp = showRspCode (rspCode resp) ++ " " ++ rspReason resp
+
+request :: URI -> Request_String
+request uri = Request{ rqURI = uri,
+                       rqMethod = GET,
+                       rqHeaders = [],
+                       rqBody = "" }
+
+handleE :: Monad m => (ConnError -> m a) -> Either ConnError a -> m a
+handleE h (Left e) = h e
+handleE _ (Right v) = return v

### 2020-03-13 random/career_preparation/cover_letters/ND_paper.tex
update

\documentclass[11pt,a4paper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\begin{document}

Dear Hiring Manager,

ND presents an interesting set of opportunities to apply innovative technologies to quantifiable and sustainable recycling.

These challenges are particularly interesting to me because I feel committed to a good future for our children and I am interested in computer vision and machine learning.

I have qualifications in applied machine learning which will help decrease the contamination rate in sorted goods and provide a more reusable and recyclable product.

One area that I am excited to learn more about, which this opportunity presents, is a hands on understanding of industrial optimization and robotics.

I have experience in Excel, but I am confident in my capabilities in Python’s Matplotlib, which is a robust data visualization package.

Thank you,

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain

\end{document}

### 2020-03-13 random/career_preparation/cover_letters/ambarella.tex
update

\documentclass[11pt,a4paper]{letter} % 10pt font size default, 11pt and 12pt are also possible
\renewcommand*\familydefault{\sfdefault}

\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
% \address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number

\begin{document}

\begin{letter}{Ambarella \\ 3101 Jay Street \\ Santa Clara, CA 95054}

\opening{\textbf{Dear Ambarella,}}

I am interested in being a Software Engineer Intern for Summer 2020.

I believe I have the qualifications in convolutional neural networks, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of computer vision. Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. I am looking to further my understanding of the stack by working on embedded machine learning.

I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building.
My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice. The current solution is tractors and manually dispersing the salt. I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.

Thank you for your time and consideration.

I look forward to your reply.

\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}

\end{letter}

\end{document}

### 2020-03-13 random/career_preparation/cover_letters/dolby.tex
update

\documentclass[11pt,a4paper,english]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\usepackage{babel}
\usepackage[useregional]{datetime2}
\begin{document}

Dear Dolby,

I am interested in the Machine Learning / Signal Processing Internship for Summer 2020.

As a lifelong musician and producer, this opportunity is extremely appealing to me.

I have extensive experience with git, python, and go (similar to C++), as well as using cloud APIs for databases, virtual machines, and flask applications.

I built a tool to generate white noise and apply filters to noise in C at /DSP/ and used a variational autoencoder to generate sound based off my personal songs at /sippyart/.

I see this opportunity as an exciting way to learn about low latency audio, networking, testing, and other interesting parts of large infrastructure that don't necessarily get taught in a class.

One area that I would like to learn more from a team about is how noise reduction is implemented and how hardware designs are constructed to optimally flatten the frequency response.

Thank you,

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain\\
\today\\

\end{document}

### 2020-03-13 random/career_preparation/cover_letters/dropbox.tex
update

\documentclass[11pt,a4paper,english]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\usepackage{babel}
\usepackage[useregional]{datetime2}
\begin{document}

Dear Dropbox,

I am interested in being a Software Engineer Intern for Summer 2020.

I have extensive experience with Python, Git, Google Cloud, and SQL.

I have built a Go-lang based data-scraper for sports odds that initially took 20+ minutes in python, now takes 30 seconds and writes to a MySQL DB on Google Cloud.

I am interested in how larger scale data operations work and how to make scalable software and possibly use machine learning for load balancing.

I hope to hear from you.

Thank you,

Anand Jain\\
Computer Science\\
University of Chicago\\

anandj@uchicago.edu\\
Github, Linkedin: anandijain\\
\today\\

\end{document}

### 2020-03-13 random/career_preparation/cover_letters/nielsen.tex
update

--- 2020-03-13 random/career_preparation/cover_letters/dropbox.tex
@@
 
-Dear Dropbox,
+Dear Nielsen,
 
-I am interested in being a Software Engineer Intern for Summer 2020.
+I am interested in being a Data Science Internship for Summer 2020.
 
@@
 
-I have built a Go-lang based data-scraper for sports odds that initially took 20+ minutes in python, now takes 30 seconds and writes to a MySQL DB on Google Cloud.
+I have built a Go-lang based data-scraper for sports odds that initially took 20+ minutes in python, now takes 30 seconds.
 
-I am interested in how larger scale data operations work and how to make scalable software and possibly use machine learning for load balancing.
+I am interested in how larger scale data operations work and how to find interesting correlations and abstractions in constrained and big-data scenarios.
 
@@
 Anand Jain\\
-Computer Science\\
-University of Chicago\\
-
 anandj@uchicago.edu\\

### 2020-03-13 random/career_preparation/cover_letters/skydio.tex
update

--- 2020-03-13 random/career_preparation/cover_letters/ambarella.tex
@@
 
-\begin{letter}{Ambarella \\ 3101 Jay Street \\ Santa Clara, CA 95054}
+\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}
 
-\opening{\textbf{Dear Ambarella,}}
+\opening{\textbf{Dear Skydio,}}
 
-I am interested in being a Software Engineer Intern for Summer 2020.
+I am interested in being an Autonomy Intern for Summer 2020.
 
-I believe I have the qualifications in convolutional neural networks, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of computer vision.
+I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology.
 Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests.

### 2020-03-13 random/career_preparation/cover_letters/template.tex
update

\documentclass[11pt,a4paper,english]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\usepackage{babel}
\usepackage[useregional]{datetime2}
\usepackage{stix} % Use the Stix font by default

\usepackage{microtype} % Improve justification

\signature{Anand Jain} % Your name for the signature at the bottom

\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ } % Your address and phone number

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Nathan Drake \\ LaTeXTemplates.com \\ 321 Pleasant Lane \\ City, State 12345} % Name/title of the addressee

%-------------------------

Dear ,

I am interested in your  position for Summer 2020.

Thank you for your time and consideration.

I look forward to your reply.

Thank you,

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain\\
\today\\
\end{letter}
\end{document}

### 2020-03-13 random/career_preparation/cover_letters/template2.tex
update

--- 2020-03-13 random/career_preparation/cover_letters/skydio.tex
@@
 
-\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}
+\begin{letter}{Company \\ Company Address \\ City, State 12345}
 
-\opening{\textbf{Dear Skydio,}}
-
-I am interested in being an Autonomy Intern for Summer 2020.
-
-I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology.
-Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests.
-I am looking to further my understanding of the stack by working on embedded machine learning.
-
-I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building.
-My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice.
-The current solution is tractors and manually dispersing the salt.
-I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.
+\opening{\textbf{Dear Sir or Madam,}}
 

### 2020-03-13 random/career_preparation/cover_letters/verily.tex
update

\documentclass[11pt,a4paper,english]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\renewcommand*\familydefault{\sfdefault}

\usepackage{graphicx} % Required for including pictures
\usepackage{babel}
\usepackage[useregional]{datetime2}
\begin{document}

Anand Jain\\
anandj@uchicago.edu\\
Github, Linkedin: anandijain\\

Dear Verily,

I am interested in the Machine Learning/Software Engineering Internship for Summer 2020.

AlphaFold was one advance that sparked my interest in computational biology and made me think about how I could use my learning to have real impact.

In computer science, we learn about the layers of abstraction that are required to build up systems for high level programming.

Biology is incredibly interesting, because we have to decrypt eons of evolution's abstractions to understand the systems and use it to improve others' lives.

I have experience in writing machine learning applications that run on Google Cloud virtual machines using PyTorch, and locally using GPU.

I have experience with Go-lang and SQL for larger scale systems through my sports projects.

I am interested in contributing towards Project Baseline and learning more about biological modelling.

Thank you,

Anand Jain\\
\today\\

\end{document}

### 2020-03-13 rust/hello.rs

@@ -1,0 +1,5 @@
+fn main() {
+    /* Block comments which go to the closing delimiter. */
+    // https://transform.tools/json-to-rust-serde
+    println!("Hello World!");
+}

### 2020-03-16 random/career_preparation/cover_letters/JD.tex
simple website in js/

--- 2020-03-13 random/career_preparation/cover_letters/skydio.tex
@@
 
-\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}
+\begin{letter}{JD \\ JD Building, No. 18 \\ Kechuang 11 Street \\ BDA, Beijing, 101111}
 
-\opening{\textbf{Dear Skydio,}}
+\opening{\textbf{Dear JD,}}
 
-I am interested in being an Autonomy Intern for Summer 2020.
+I am interested in being a Research Intern for Summer 2020.
 
-I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology.
+I believe I have the qualifications in programming, machine learning, and cloud service management to develop and deploy valuable and performant models.
 Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
-I am looking to further my understanding of the stack by working on embedded machine learning.
+I am looking to work on larger and more complex models that operate with a great deal of data.
 
-I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building.
-My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice.
-The current solution is tractors and manually dispersing the salt.
-I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.
+I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
+I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
+My ideal conversation with an employee would be about how AI is changing the industry and what creative uses of AI in commerce there are.
 

### 2020-03-16 random/career_preparation/cover_letters/impossible.tex
simple website in js/

--- 2020-03-16 random/career_preparation/cover_letters/JD.tex
@@
 
-\begin{letter}{JD \\ JD Building, No. 18 \\ Kechuang 11 Street \\ BDA, Beijing, 101111}
+\begin{letter}{Impossible Foods \\ Redwood City, CA}
 
-\opening{\textbf{Dear JD,}}
+\opening{\textbf{Dear Impossible Foods,}}
 
-I am interested in being a Research Intern for Summer 2020.
+I am interested in being a Data Science Intern for Summer 2020.
 
-I believe I have the qualifications in programming, machine learning, and cloud service management to develop and deploy valuable and performant models.
+I believe I have the qualifications in programming, machine learning, and cloud service management to provide valuable insights on social media sentiment.
 Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
-I am looking to work on larger and more complex models that operate with a great deal of data.
+I am looking to work on larger and more complex models, such as BERT and GPT-2.
 
 I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
-I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
-My ideal conversation with an employee would be about how AI is changing the industry and what creative uses of AI in commerce there are.
+My ideal conversation with an employee would be about how simulation and machine learning can be used to continually improve the Impossible Burger.
 

### 2020-03-16 random/career_preparation/cover_letters/intel.tex
simple website in js/

\documentclass[11pt,a4paper]{letter} % 10pt font size default, 11pt and 12pt are also possible
\renewcommand*\familydefault{\sfdefault}

\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
% \address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number

\begin{document}

\begin{letter}{Intel Corporation \\ 2200 Mission College Blvd \\ Santa Clara, CA  95052 }

\opening{\textbf{Dear Intel,}}

In senior year of high school, I was taking AP Computer Science Principles and we had to do two presentations. I did my first presentation on convolutional neural networks and my second on quantum computing. 
I didn’t realize until I learned more about complexity theory and big-O notation in college how amazing quantum systems are. 
This profound and numinous field of study is racing to Landauer's limit and has given me an exponentially greater appreciation for the beauty of nature.

I'm hoping to contribute some meaningful addition to helping us use NISQ devices to improve lives around the world.
As founder of the UChicago Quantum Society, I am hoping to bring back insights in how to communicate scientific works to general audiences and help grow the community of the quantum-curious.

\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}

\end{letter}

\end{document}

### 2020-03-16 random/career_preparation/cover_letters/pg_and_e.tex
simple website in js/

--- 2020-03-16 random/career_preparation/cover_letters/impossible.tex
@@
 
-\begin{letter}{Impossible Foods \\ Redwood City, CA}
+\begin{letter}{Pacific Gas and Electric \\ 77 Beale Street \\ San Francisco, CA 94105}
 
-\opening{\textbf{Dear Impossible Foods,}}
+\opening{\textbf{Dear Pacific Gas and Electric,}}
 
-I am interested in being a Data Science Intern for Summer 2020.
+I am interested in being an Meteorology Data Science Intern for Summer 2020.
 
-I believe I have the qualifications in programming, machine learning, and cloud service management to provide valuable insights on social media sentiment.
+I believe I have the qualifications in programming, machine learning, and deploying cloud services to make a helpful contribution towards creating innovative predictive models.
 Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
-I am looking to work on larger and more complex models, such as BERT and GPT-2.
+I am looking to implement larger scale models that use interesting data and require innovative models, which meteorology requires.
 
-I have experience working with the hugging-face NLP transformers library, and will be taking computational linguistics next term.
-My ideal conversation with an employee would be about how simulation and machine learning can be used to continually improve the Impossible Burger.
+My ideal conversation with an employee would be about what architectures and models are used currently in meteorology and what the constraints are of these models.
 

### 2020-03-16 random/career_preparation/cover_letters/pocket_gems.tex
simple website in js/

--- 2020-03-16 random/career_preparation/cover_letters/JD.tex
@@
 
-\begin{letter}{JD \\ JD Building, No. 18 \\ Kechuang 11 Street \\ BDA, Beijing, 101111}
+\begin{letter}{Pocket Gems \\ 220 Montgomery Street \\ San Francisco, CA 94104}
 
-\opening{\textbf{Dear JD,}}
+\opening{\textbf{Dear Pocket Gems,}}
 
-I am interested in being a Research Intern for Summer 2020.
+I am interested in being a Data Science Intern for Summer 2020.
 
@@
 Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
-I am looking to work on larger and more complex models that operate with a great deal of data.
+I am looking to work on larger and more complex models.
 
@@
 I have built reinforcement learning environements using OpenAI's Gym package and am excited to implement larger models in production.
-My ideal conversation with an employee would be about how AI is changing the industry and what creative uses of AI in commerce there are.
+My ideal conversation with an employee would be about how AI is changing the gaming industry and what creative uses of AI in gaming there are.
 

### 2020-03-16 random/career_preparation/cover_letters/qurip.tex
simple website in js/

--- 2020-03-16 random/career_preparation/cover_letters/intel.tex
@@
 
-\address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
-% \address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number
+% \address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
+\address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number
 
@@
 
-\begin{letter}{Intel Corporation \\ 2200 Mission College Blvd \\ Santa Clara, CA  95052 }
+\begin{letter}{QURIP Internship}
 
-\opening{\textbf{Dear Intel,}}
+\opening{\textbf{Dear QURIP,}}
+
+Almost every quantum scientist knows Feynmans’ holy quote, "Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical".
 

### 2020-03-16 random/career_preparation/cover_letters/wing.tex
simple website in js/

--- 2020-03-13 random/career_preparation/cover_letters/skydio.tex
@@
 
-\begin{letter}{Skydio \\ 114 Hazel Ave \\ Redwood City, CA 94061}
+\begin{letter}{Wing  \\ Palo Alto, CA 94304}
 
-\opening{\textbf{Dear Skydio,}}
+\opening{\textbf{Dear Wing,}}
 
-I am interested in being an Autonomy Intern for Summer 2020.
+I am interested in being an Engineering Intern for Summer 2020.
 
-I believe I have the qualifications in machine learning, Python, and Go-lang (C++ like) to make a helpful contribution towards creating innovative applications of drone technology.
+I believe I have the qualifications in programming, machine learning, and electronics to make a helpful contribution towards creating innovative applications of Wing planes.
 Much of my time in college has been devoted towards thinking about neural network architectures and paradigms, differentiable programming and reinforcement learning being two primary interests. 
@@
 I have taken an electronics course, where we built radios, stopwatches, and other things in VDHL, as well as an interactive devices course that taught 3D printing and wearable device building. 
-My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice.
+My ideal conversation with an employee would be about autonomy in a multi-agent domain, specifically how to solve the following problem: 
+At UChicago, we have a problem in the winter, many sidewalks need to be cleared and salted on short notice. 
 The current solution is tractors and manually dispersing the salt. 
-I would like to see drones be able to quickly provide a map of unwalkable locations and report this to people cleaning up snow.
+I would like to see planes map unwalkable locations and report this to people cleaning up snow.
 

### 2020-03-16 js/app.js

@@ -1,0 +1,72 @@
+
+let today = new Date();
+let formatDate = today.toDateString().toLowerCase()
+let selectElement = document.getElementById('date');
+selectElement.innerHTML = formatDate;
+
+const staggerVisualizerEl = document.querySelector('.stagger-visualizer');
+const fragment = document.createDocumentFragment();
+const grid = [17, 17];
+const col = grid[0];
+const row = grid[1];
+const numberOfElements = col * row;
+
+for (let i = 0; i < numberOfElements; i++) {
+    fragment.appendChild(document.createElement('div'));
+}
+
+staggerVisualizerEl.appendChild(fragment);
+
+const staggersAnimation = anime.timeline({
+    targets: '.stagger-visualizer div',
+    easing: 'easeInOutSine',
+    delay: anime.stagger(50),
+    loop: true,
+    autoplay: false
+})
+    .add({
+        translateX: [
+            { value: anime.stagger('-.1rem', { grid: grid, from: 'center', axis: 'x' }) },
+            { value: anime.stagger('.1rem', { grid: grid, from: 'center', axis: 'x' }) }
+        ],
+        translateY: [
+            { value: anime.stagger('-.1rem', { grid: grid, from: 'center', axis: 'y' }) },
+            { value: anime.stagger('.1rem', { grid: grid, from: 'center', axis: 'y' }) }
+        ],
+        duration: 1000,
+        scale: .5,
+        delay: anime.stagger(100, { grid: grid, from: 'center' })
+    })
+    .add({
+        translateX: () => anime.random(-10, 10),
+        translateY: () => anime.random(-10, 10),
+        delay: anime.stagger(8, { from: 'last' })
+    })
+    .add({
+        translateX: anime.stagger('.25rem', { grid: grid, from: 'center', axis: 'x' }),
+        translateY: anime.stagger('.25rem', { grid: grid, from: 'center', axis: 'y' }),
+        rotate: 0,
+        scaleX: 2.5,
+        scaleY: .25,
+        delay: anime.stagger(4, { from: 'center' })
+    })
+    .add({
+        rotate: anime.stagger([90, 0], { grid: grid, from: 'center' }),
+        delay: anime.stagger(50, { grid: grid, from: 'center' })
+    })
+    .add({
+        translateX: 0,
+        translateY: 0,
+        scale: .5,
+        scaleX: 1,
+        rotate: 180,
+        duration: 1000,
[…]

### 2020-03-23 random/career_preparation/cover_letters/intel.tex
add bash yt-dl one-liner for wav

@@
-\documentclass[11pt,a4paper]{letter} % 10pt font size default, 11pt and 12pt are also possible
+\documentclass[11pt]{letter} % 10pt font size default, 11pt and 12pt are also possible
 \renewcommand*\familydefault{\sfdefault} 
+\usepackage[margin=1in]{geometry}
 
 \address{610 Jackson St. \\ Santa Clara, CA 95050 \\ (408)597-4214 } % Your address and phone number
-% \address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number
+\address{6103 S University Ave. \\ Chicago, IL 60637 \\ (408)597-4214 } % Your address and phone number
 
@@
 
-\begin{letter}{Intel Corporation \\ 2200 Mission College Blvd \\ Santa Clara, CA  95052 }
+\begin{letter}{}
 
@@
 
-In senior year of high school, I was taking AP Computer Science Principles and we had to do two presentations.
-I did my first presentation on convolutional neural networks and my second on quantum computing.
-I didn’t realize until I learned more about complexity theory and big-O notation in college how amazing quantum systems are. 
-This profound and numinous field of study is racing to Landauer's limit and has given me an exponentially greater appreciation for the beauty of nature.
+Last spring, I started a club (ucquantum.org) for students interested in quantum information at UChicago, advised by Prof. Andrew Cleland.
+I felt that there was a need for an academic club specifically for quantum technologies and NISQ computing.
+This fall we began hosting weekly meetings and reaching out to various departments to find interested students.
+Despite initially being slow going, our bimonthly newsletter covering news and Quantum research at UChicago has about 60 subscribers and we have a group of about 10 come each week.
+The most rewarding part about this experience has been getting to explain superposition and entanglement to people.
 
-I'm hoping to contribute some meaningful addition to helping us use NISQ devices to improve lives around the world.
-As founder of the UChicago Quantum Society, I am hoping to bring back insights in how to communicate scientific works to general audiences and help grow the community of the quantum-curious.
+Once we had learned the basics, we started planning events and reaching out to professors for when we got approved.
+We toured Prof. David Schuster's superconducting qubit lab and spoke to a few professors about their work.
+UChicago Quantum Society was approved to be an official club at the beginning of March.
+I'm particularly excited about being able to host hackathons and panels with professors, unfortunately, students are off campus next quarter.
 
-\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}
+I believe that participating in quantum research and applications will give me insights into how to better teach and engage people with the field.
+I'm hoping to use these experiences to be a more effective club president.
+
+As a computer science major, I have been interested in the software used to control quantum devices.
+I have used many of the quantum "languages" briefly (QISKit, Cirq, Quirk, etc), but after taking a course on Quantum Computation this quarter, I wanted to write my own quantum programming interface to learn how someone might make a fully featured simulator.
+
+MyQuantum is a Julia-lang package that implements the common 1-bit operators (X, Y, Z, H), arbitrary controlled gate, and an arbitrary single-qubit rotation that can be composed with a control.
+I also wrote functions to test if normalized, hermitian, unitary, added documentation, and unit tests.
+I am looking to extend what I currently have to use as a pre-hackathon learners repo, to get people familiar with code and notation, but not be too advanced.
+
+I am incredibly excited about the future of quantum computing and feel I have the necessary qualifications
+to be a valuable team member in researching NISQ devices.
+
+\begin{flushright}
+    Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu
+\end{flushright}
 

### 2020-03-23 random/career_preparation/cover_letters/qurip.tex
add bash yt-dl one-liner for wav

@@
-\documentclass[11pt,a4paper]{letter} % 10pt font size default, 11pt and 12pt are also possible
+\documentclass[11pt]{letter} % 10pt font size default, 11pt and 12pt are also possible
 \renewcommand*\familydefault{\sfdefault} 
+\usepackage[margin=1in]{geometry}
 
@@
 
-\begin{letter}{QURIP Internship}
+\begin{letter}{}
 
@@
 
-Almost every quantum scientist knows Feynmans’ holy quote, "Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical".
+Last spring, I started a club (ucquantum.org) for students interested in quantum information at UChicago, advised by Prof. Andrew Cleland.
+I felt that there was a need for an academic club specifically for quantum technologies and NISQ computing.
+This fall we began hosting weekly meetings and reaching out to various departments to find interested students.
+Despite initially being slow going, our bimonthly newsletter covering news and Quantum research at UChicago has about 60 subscribers and we have a group of about 10 come each week.
+The most rewarding part about this experience has been getting to explain superposition and entanglement to people.
 
-In senior year of high school, I was taking AP Computer Science Principles and we had to do two presentations.
-I did my first presentation on convolutional neural networks and my second on quantum computing.
-I didn’t realize until I learned more about complexity theory and big-O notation in college how amazing quantum systems are. 
-This profound and numinous field of study is racing to Landauer's limit and has given me an exponentially greater appreciation for the beauty of nature.
+Once we had learned the basics, we started planning events and reaching out to professors for when we got approved.
+We toured Prof. David Schuster's superconducting qubit lab and spoke to a few professors about their work.
+UChicago Quantum Society was approved to be an official club at the beginning of March.
+I'm particularly excited about being able to host hackathons and panels with professors, unfortunately, students are off campus next quarter.
 
-I'm hoping to contribute some meaningful addition to helping us use NISQ devices to improve lives around the world.
-As founder of the UChicago Quantum Society, I am hoping to bring back insights in how to communicate scientific works to general audiences and help grow the community of the quantum-curious.
+I believe that participating in QURIP will give me insights into how to better teach and engage people with the field.
+I'm hoping to use these experiences to be a more effective club president.
 
-\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}
+As a computer science major, I have been interested in the software used to control quantum devices.
+I have used many of the quantum "languages" briefly (QISKit, Cirq, Quirk, etc), but after taking a course on Quantum Computation this quarter, I wanted to write my own quantum programming interface to learn how someone might make a fully featured simulator.
+
+MyQuantum is a Julia-lang package that implements the common 1-bit operators (X, Y, Z, H), arbitrary controlled gate, and an arbitrary single-qubit rotation that can be composed with a control.
+I also wrote functions to test if normalized, hermitian, unitary, added documentation, and unit tests.
+I am looking to extend what I currently have to use as a pre-hackathon learners repo, to get people familiar with code and notation, but not be too advanced.
+
+I am incredibly excited about the future of quantum computing and feel I have the necessary qualifications
+to be a valuable team member in researching NISQ devices.
+
+\begin{flushright}
+    Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu
+\end{flushright}
 

### 2020-03-23 random/career_preparation/resume/resume2.tex
add bash yt-dl one-liner for wav

@@
 \section{COURSES}
-\par
-\normalfont{\textbullet{Abstract Linear Algebra}}
-\normalfont{\textbullet{Algorithms}}
-\normalfont{\textbullet{Computer Systems}}
-\normalfont{\textbullet{Discrete Math}}\\
-\normalfont{\textbullet{Electronics}}
-\normalfont{\textbullet{Inventing Interactive Devices}}
-\normalfont{\textbullet{Mathematical Logic}}\\
-\normalfont{\textbullet{Molecular Engineering}}
-\normalfont{\textbullet{Quantum Computation}}
+
+\textbullet{Abstract Linear Algebra}
+\textbullet{Algorithms}
+\textbullet{Computer Systems}
+\textbullet{Discrete Math}
+\textbullet{Electronics}
+\textbullet{Interactive Devices}
+\textbullet{Mathematical Logic}
+\textbullet{Molecular Engineering}
+\textbullet{Quantum Computation}
 
@@
 \section{SKILLS}
-\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL\\
+\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL, \LaTeX\\
 \textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
@@
 
-\textbf{codebyhand: applying handwriting recognition}\\ 
-\textbullet{Wrote `paint` program that infers EMNIST characters after each stroke and allows transfer learning on own handwriting}\\
-\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
-\textbf{tools:} pytorch, torchvision, tkinter \\
-\textbf{src :} github.com/anandijain/codebyhand\\
+\textbf{myquantum: the quantum learners repo}\\ 
+\textbullet{Wrote basic quantum math package in Julia to learn/teach basic linear algebra}\\
+\textbullet{Implements common 1-qubit gates, arbitrary 2-qubit control gates, arbitrary rotation}\\
+\textbullet{Functions for checking if normed, unitary, hermitian, and generating Bell states}\\
+\textbullet{Goal: Build circuit interface and perform QFT on my own simulated QC}\\
+\textbf{tools:} Julia, LinearAlgebra.jl \\
+\textbf{src :} github.com/anandijain/MyQuantum\\
 
@@
 \textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
-\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
+\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and QISKit}
 %-------------------------------------------------------------------------------

### 2020-03-23 random/materials.tex
add bash yt-dl one-liner for wav

\documentclass[letterpaper]{article}

\renewcommand{\familydefault}{\sfdefault}
\usepackage[margin=1in]{geometry}
\usepackage[medium]{titlesec}
\usepackage{amsmath,amssymb,mhchem}

\begin{document}
\title{Material Science Final}
\author{Anand Jain \\ anandj@uchicago.edu}
\maketitle
\paragraph{}
    \textbf{On my honor, I have neither given nor received any unauthorized aid on this exam. By signing my name below, I understand that violations of this honor code will result in suspension of academic status or expulsion from the University of Chicago’s community.  \\
    Sign or Type your name here: Anand Jain}
\section{Alpha Phase Plutonium}
    \paragraph{}
        \textit{
            \textbf{a.} 
            What's the nature of the bonding between Plutonium atoms?
        }
    \paragraph{}
        The electron configuration of isolated Plutonium is [Rn] 5f$^{6}$ 7s$^{2}$. 
        As indicated by the close groups of two atoms in the unit cell picture, there are Pu-Pu bonds.
        The bonding is covalent in the valence f subshell. The electron configuration

    \paragraph{}
    \textit{
        \textbf{b.} 
        Calculate the mass density of the alpha-phase Plutonium metal in units of g/cm3.
        }

    \paragraph{}
        The mass density of metallic $\alpha$ Plutonium is given by $\rho$ = $\dfrac{nA}{V_{c}N_{A}}$.
        We can calculate $V_{c}$ by using the formula for monoclinic unit cell volume:

        $V_{c} = abc\sin{(\beta)} = 6.1835e^{-8} * 4.8244e^{-8} * 1.0973e^{-7} * \sin{(180 - 78.2)} = 3.11526e^{-22}\frac{cm^{3}}{cell}$

        $\rho = (16\frac{atoms}{cell} * 244 \frac{g}{mol}) * (6.022e^{23}\frac{atoms}{mol} * 3.11526e^{-22}\frac{cm^{3}}{cell})^{-1}$

        $ = \frac{3904}{187.60} =$ \textbf{~ 20.8 $\frac{g}{cm^{3}}$}

        This is close to the result online of $19.86\frac{g}{cm^{3}}$.

    \paragraph{}
        \textit{
            \textbf{c.} 
            The isotope \ce{^{239}Pu} will decay into an alpha particle \ce{^{4}_{2}He} and another element.
            What is this other element? What are its atomic number and atomic mass?
        }

    \paragraph{}
        The decay product is Uranium, with an atomic number of 92, and a mass of 235 u.
        $$
        \ce{^{239}_{94}Pu} \rightarrow \ce{^{4}_{2}He} + \ce{^{235}_{92}U}
        $$

\section{H in H$_{2}$S vs H$_{3}$S}
    \paragraph{}
    \textit{
        \textbf{a.} 
        What is the nature of the H-S bond? Is it ionic or covalent?
        }

    \paragraph{}

        In H$_{2}$S, unlike H$_{2}$O, does not have a large electronegativity difference between H and B (0.38 vs 1.24, respectively).
        Additionally, sulfur's valence electrons are further away from the nucleus ([Ne] 3s$^{2}$ 3p$^{4}$ vs [He]2s$^{2}$ 2p$^{4}$).
        This makes intermolecular hydrogen bonding forces unable to form.
        The bonding exhibited is covalent.
        For H$_{3}$S

    \paragraph{}
    \textit{
        \textbf{b.} 
        Why is it relatively easy to form a solid crystal out of H$_{2}$O (ice), but immensely difficult to form a solid crystal out of H$_{2}$S?
        }
    \paragraph{}

    As stated in (a.), the further radius of protons to valence electrons prevents polar intermolecular forces from being impactful, unlike water.
    The lack of these weak intermolecular forces in H$_{3}$S, prevents an open (weak) tetrahedral structure like in water.
    These weak forces are what causes ice to be less dense than liquid water

    \paragraph{}
    \textit{
        \textbf{c.} 
        What is the crystal system of H$_{3}$S (cubic/hexagonal/tetragonal etc.)? What is the specific lattice structure within this crystal system?
        }
    \paragraph{}

        The H$_{3}$S structure is a cubic cystal system. The lattice is composed of two perovskite sublattices SH$^{-}$ and H$_{3}$S.

    \paragraph{}
        \textit{
            \textbf{d.} 
            Can you comment on why ice (solid H$_{2}$O) is insulating, but H$_{3}$S is metallic?
            }

        As stated, ice is less dense than it's liquid counterpart, due to weak intermolecular forces.
        H$_{3}$S is non-polar, and exhibits increased density, causing metallic.

\section{KCl vs KBr}
    \paragraph{}
    \textit{
        \textbf{a.} 
        What is the crystal system and the specific lattice structure of KCl and KBr?
        }
    \paragraph{}

The crystal system of KCl is, like NaCl, a face centered cubic structure.

KCl: There are two inter-penetrating BCC latices, of K$^{+}$ and Cl$^{-}$
KBr: There are two inter-penetrating FCC latices, of K$^{+}$ and Br$^{-}$

    \paragraph{}
    \textit{
        \textbf{b.} 
        We know that the X-ray wavelength is 1.54\AA. Can you use the XRD data to estimate the lattice constant of KCl, and KBr, respectively?
        }

    Yes, since it is cubic we have $\alpha = \beta = \gamma$. $n\lambda = 2d\sin{(\theta)}$ where $d :=$ interplane spacing, by Bragg's.
    $d = \frac{\lambda}{2\sin{(\theta)}} = \frac{0.154 nm}{2\sin{(35)}}$

    \paragraph{}
    \paragraph{}
    \textit{
        \textbf{c.} 
        Why do KCl only exhibit peaks with even h, k, and l numbers?
        }

    This indicates that KCl is BCC structure, as BCC requrires h, k, and l to be even.
    As opposed to FCC, where they can either be all odd or all even.

\section{Cold work on metals}
    \paragraph{}
    \textit{
        \textbf{a.} 
        If we directly stretch the rod to obtain a diameter of 7.5 mm, what would be the yield strength, tensile strength, and ductility? 
        }

        By hooks law, $\sigma = E * \epsilon$
        $\Delta{l} = \frac{\sigma * l_{0}}{E}$
        $\Delta{l} = \frac{450 MPa * 2.5 mm }{97 GPa}$
        $\Delta{l} = 11.5979381 microns$

    \paragraph{}
    \textit{
        \textbf{b.} 
        How much percentage of cold work is needed for the required tensile strength and ductility?
        }

    We need 25 pct cold work to get at least 450 MPa and a ductility higher than 10 pct.

    \paragraph{}
    \textit{
        \textbf{c.} 
        Describe how you would achieve the tensile strength, ductility, and final diameter.
        }

\section{Lead-tin phase diagram}
    \paragraph{}
    \textit{
        \textbf{a.} 
        Identify the liquidus line and solidus line for the $\alpha$ phase. 
        Identify the liquidus line and solidus line for the $\beta$ phase.
        }

    \paragraph{}

The $\alpha$ phase liquidus line is the line on the top that starts at the left at (0 wt$\%$ Sn, 327 C,) to (61.9 wt$\%$ Sn, 183 C).
This is clear, as the only phase that exists above the line is liquid and borders the a mixed phase with $\alpha$.

For $\alpha$ phase solidus line is where only phase $\alpha$ exists and borders liquid mixture: (0 wt$\%$, 327 C) to (18.3 wt$\%$, 183 C).

By the same logic:

The $\beta$ liquidus is from (61 wt$\%$, 183 C) to (100 wt$\%$ Sn, 232 C)

The $\beta$ solidus is from (100 wt$\%$, 232 C) to (97.8 wt$\%$ Sn, 183 C)

    \paragraph{}
    \textit{
        \textbf{b.} 
        Describe the microstructure changes as you very slowly cool down a Pb-Sn system at 50 wt$\%$ Sn composition from 300 deg Celsius. 
        Draw diagrams to illustrate your microstructures at 300 deg Celsius, 200 deg Celsius, and 100 deg Celsius.
        }

    \paragraph{}
    \paragraph{}
    \textit{
        \textbf{c.} 
        If you are to make a low-temperature solder, what compositions would you use for Pb and Sn? Why?
        }

        I would choose 61.9 wt$\%$ Sn and 38.1 wt$\%$ Pb, where the melting temperature is at 183 C.
        This is lower than either Pb or Sn. Additionally, it is a eutectic point, meaning it freezes and melts at the same time.
        This is an advantageous property because it is faster to solidify for circuitry, and has a a low melting temperature for re-melting.
        If it was found that the eutectic point maybe was too cool and under certain conditions would melt during usage (hot car, etc), 
        then I would choose to bias towards lead, as it is a steeper slope to a higher melting temperature, however, then we would have 
        the $\alpha$ + L phase.

\section{Semiconductor behaviors}
    \paragraph{}
    \textit{
        \textbf{a.} 
        Describe the three temperature regions for electron concentration. 
        Qualitatively explain the temperature dependence for these three temperature regions.
        }

    \paragraph{}

Firstly, the semiconductor is doped with electrons, meaning the majority carrier are P-type (holes).
For an extrinsic semiconductor, there are three regions, the freeze out, the extrinsic, and the intrinsic, in e$^{-}$ concentration / temperature.
The extrinsic region is where the e$^{-}$ concentration is constant and e$^{-}$s in the conduction band are excited by P type impurities. 
Most all impurities will be ionized as the e$^{-}$ concentration is about equal to P content.

Freeze out, however, occurs as the amount of energy required for excitation of a donated electron into the conduction band is too large to overcome the lack of thermal energy.
The intrinsic region is where the amount of thermal energy causes easy excitation of electrons into the conduction band from P-donors.
This causes the concentration of electrons to overwhelm the concentration of holes.

    \paragraph{}
    \textit{
        \textbf{b.} 
        Imagine that we need to work in the outer space with a temperature usually $<$ -200 deg Celsius. 
        What challenges will there be to build a classical computer using doped semiconductors like this one? 
        Do you have any suggestions for how to make a computer that works for that cold environment? 
        }

        \paragraph{}
The most obvious challenge will be making sure that the classical computer is in an environment that will allow for the semiconductor to be in the extrinsic region, such that the donors actually donate electrons to the conduction band.

\textbf{Thank you for an awesome quarter}
\end{document}

### 2020-03-23 bash/misc/wav_from_yt.sh

@@ -1,0 +1,4 @@
+get_audio(){
+    $# < 2 ? return 
+    youtube-dl -f251 $1 -o - | ffmpeg -i pipe: -ac 2 -f wav $2
+}

### 2020-03-29 random/pythonstuff/teachin/intro.py
added intro python material

@@ -1,0 +1,36 @@
+ 
+# data types 
+
+i = 0 # int
+f = 0. # float
+l = [] # list
+t = () # tuple, immutable
+d = {} # dict
+
+# lists aren't arrays
+
+l2 = [i, f, l, t, d]
+
+# for loop
+for elt in l2:
+    print(f'{elt}, {type(elt)}')
+    
+# functions
+
+def fxn():
+    print('hello')
+
+# arguments in functions
+
+def fxn2(s):
+    print(s)
+
+# return values
+
+def fxn3(n):
+    return n**2 # squared
+
+# importance of data types
+
+fxn3('a')
+# TypeError: unsupported operand type(s) for ** or pow(): 'str' and 'int'

### 2020-03-29 random/pythonstuff/teachin/foss.py
rust serde

@@ -1,0 +1,28 @@
+# common foss 
+
+"""
+numpy
+pandas
+
+
+"""
+import time
+import pyttsx3
+
+def sleep_and_speak(e:pyttsx3.engine.Engine, phrase:str, sleep_amt:str):
+    time.sleep(sleep_amt)
+    e.say(phrase)
+    e.runAndWait()
+
+
+def remind_every(phrase: str, n: int, sleep_amt: int):
+    i = 0
+    e = pyttsx3.init()
+    for i in range(n):
+        sleep_and_speak(e, phrase, sleep_amt)
+
+
+
+
+if __name__ == "__main__":
+    remind_every("hello", 10, 5)

### 2020-03-29 random/pythonstuff/teachin/stdlib.py

@@ -1,0 +1,17 @@
+
+"""
+https://docs.python.org/3/library/
+
+Commonly used libraries from std:
+
+math
+random
+os / os.path
+glob
+csv
+os 
+io
+urllib.requrest
+(type hinting)
+
+"""

### 2020-03-29 rust/sipoxide/src/bov.rs

@@ -1,0 +1,107 @@
+extern crate serde;
+use serde::{Serialize, Deserialize};
+
+#[derive(Serialize, Deserialize)]
+pub struct Root {
+    pub path: Vec<Path>,
+    pub events: Vec<Event>,
+}
+
+#[derive(Serialize, Deserialize)]
+pub struct Path {
+    pub id: String,
+    pub link: Option<String>,
+    pub description: String,
+    #[serde(rename = "type")]
+    pub type_field: String,
+    pub sport_code: Option<String>,
+    pub order: i128,
+    pub leaf: bool,
+    pub current: bool,
+}
+
+#[derive(Serialize, Deserialize)]
+pub struct Event {
+    pub id: String,
+    pub description: String,
+    #[serde(rename = "type")]
+    pub type_field: String,
+    pub link: String,
+    pub status: String,
+    pub sport: String,
+    pub start_time: Option<i128>,
+    pub live: bool,
+    pub away_team_first: Option<bool>,
+    pub deny_same_game: Option<String>,
+    pub teaser_allowed: Option<bool>,
+    pub competition_id: Option<String>,
+    pub notes: String,
+    pub num_markets: Option<i128>,
+    pub last_modified: Option<i128>,
+    pub competitors: Vec<Competitor>,
+    pub display_groups: Option<Vec<DisplayGroup>>,
+}
+
+#[derive(Serialize, Deserialize)]
+pub struct Competitor {
+    pub id: String,
+    pub name: String,
+    pub home: bool,
+}
+
+#[derive(Serialize, Deserialize)]
+pub struct DisplayGroup {
+    pub id: String,
+    pub description: String,
+    pub default_type: bool,
+    pub alternate_type: bool,
+    pub markets: Vec<Market>,
+    pub order: i128,
+}
+
+#[derive(Serialize, Deserialize)]
+pub struct Market {
+    pub id: String,
+    pub description_key: String,
+    pub description: String,
+    pub key: String,
+    pub market_type_id: String,
+    pub status: String,
+    pub single_only: bool,
+    pub notes: String,
+    pub period: Period,
+    pub outcomes: Vec<Outcome>,
+    pub sort_type: Option<String>,
+}
+
+#[derive(Serialize, Deserialize)]
+pub struct Period {
+    pub id: String,
+    pub description: String,
+    pub abbreviation: String,
+    pub live: bool,
+    pub main: bool,
+}
+
+#[derive(Serialize, Deserialize)]
[…]

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -1,0 +1,20 @@
+#[macro_use]
+extern crate serde_derive;
+extern crate serde;
+
+use std::fs;
+
+mod bov;
+
+fn main() {
+    let contents = fs::read_to_string("./data/root.json")
+        .expect("Something went wrong reading the file").to_string();
+
+    let ds: Vec<bov::Root> = serde_json::from_str(&contents).unwrap();
+
+    for s in ds.iter() {
+        for e in s.events.iter() {
+            println!("{}", e.id)
+        }
+    }
+}

### 2020-03-29 rust/sipoxide/src/bov.rs
added reqwest, but async/futures is messed rn

@@ -1,13 +1,13 @@
 extern crate serde;
 use serde::{Serialize, Deserialize};
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Root {
     pub path: Vec<Path>,
     pub events: Vec<Event>,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Path {
     pub id: String,
     pub link: Option<String>,
@@ -20,7 +20,7 @@ pub struct Path {
     pub current: bool,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Event {
     pub id: String,
     pub description: String,
@@ -42,14 +42,14 @@ pub struct Event {
     pub display_groups: Option<Vec<DisplayGroup>>,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Competitor {
     pub id: String,
     pub name: String,
     pub home: bool,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct DisplayGroup {
     pub id: String,
     pub description: String,
@@ -59,7 +59,7 @@ pub struct DisplayGroup {
     pub order: i128,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Market {
     pub id: String,
     pub description_key: String,
@@ -74,7 +74,7 @@ pub struct Market {
     pub sort_type: Option<String>,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Period {
     pub id: String,
     pub description: String,
@@ -83,7 +83,7 @@ pub struct Period {
     pub main: bool,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Outcome {
     pub id: String,
     pub description: String,
@@ -94,7 +94,7 @@ pub struct Outcome {
     pub competitor_id: Option<String>,
 }
 
-#[derive(Serialize, Deserialize)]
+#[derive(Serialize, Deserialize, Debug)]
 pub struct Price {
     pub id: String,
     pub american: String,

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -1,12 +1,15 @@
 #[macro_use]
 extern crate serde_derive;
 extern crate serde;
+extern crate reqwest;
+use reqwest::Error;
 
 use std::fs;
 
 mod bov;
 
-fn main() {
+fn parse() {
+
     let contents = fs::read_to_string("./data/root.json")
         .expect("Something went wrong reading the file").to_string();
 
@@ -17,4 +20,29 @@ fn main() {
             println!("{}", e.id)
         }
     }
+    // Ok(())
 }
+
+fn main() {
+    parse()
+
+}
+
+// fn grab() {
+
+//     let url = "https://www.bovada.lv/services/sports/event/v2/events/A/description/";
+    
+//     println!("getting {}", url);
+    
+//     let mut response = reqwest::get(url);
+//     // let response = match response {
+//     //     Ok(_) => response,
+//     //     Err(error) => {
+//     //         panic!("Problem opening the response: {:?}", error)
+//     //     },
+//     // };
+//     let roots: Vec<bov::Root> = response.json();
+
+//     println!("{:?}", roots);
+//     Ok(())
+// }

### 2020-03-29 rust/sipoxide/src/bov.rs
interm working with rust Results

@@ -1,11 +1,12 @@
 extern crate serde;
-use serde::{Serialize, Deserialize};
+// use serde::{Serialize, Deserialize};
 
 #[derive(Serialize, Deserialize, Debug)]
 pub struct Root {
     pub path: Vec<Path>,
     pub events: Vec<Event>,
 }
+
 
 #[derive(Serialize, Deserialize, Debug)]
 pub struct Path {

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -1,39 +1,132 @@
 #[macro_use]
 extern crate serde_derive;
 extern crate serde;
-extern crate reqwest;
-use reqwest::Error;
+// extern crate reqwest;
+// use reqwest::Error;
 
 use std::fs;
 
 mod bov;
 
-fn parse() {
-
-    let contents = fs::read_to_string("./data/root.json")
-        .expect("Something went wrong reading the file").to_string();
-
-    let ds: Vec<bov::Root> = serde_json::from_str(&contents).unwrap();
-
-    for s in ds.iter() {
-        for e in s.events.iter() {
-            println!("{}", e.id)
+impl bov::Outcome {
+    fn repr(&self) {
+        println!("oc {} {}", self.description, self.price.decimal);
+        // self.price.repr()
+    }
+}
+impl bov::Market {
+    fn repr(&self) {
+        println!("{}", self.description);
+        for o in self.outcomes.iter() {
+            o.repr();
         }
     }
-    // Ok(())
+}
+impl bov::DisplayGroup {
+    fn repr(&self) {
+        for m in self.markets.iter() {
+            m.repr();
+        }
+    }
+}
+
+impl bov::Root {
+    fn repr(&self) {
+        for e in self.events.iter() {
+            e.repr();
+        }
+    }
+
+    fn count_events(&self) -> u64 {
+        let mut n: u64 = 0;
+        for e in self.events.iter() {
+            n += 1;
+        }
+        return n;
+    }
+}
+
+impl ToString for bov::Competitor {
+    fn to_string(&self) -> String {
+        return format!("Competitor {} {} {}", self.id, self.name, self.home);
+    }
+}
+impl ToString for bov::Outcome {
+    fn to_string(&self) -> String {
+        return format!("oc {} {}", self.description, self.price.decimal);
+    }
+}
+impl ToString for bov::Market {
+    fn to_string(&self) -> String {
+        return format!("mkt {} {}", self.id, self.description);
+    }
+}
+impl ToString for bov::DisplayGroup {
+    fn to_string(&self) -> String {
+        return format!("oc {} {}", self.id, self.description);
+    }
+}
+impl ToString for bov::Event {
+    fn to_string(&self) -> String {
+        return format!("ev {} {} {}", self.id, self.description, self.status);
+    }
+}
+
+impl bov::Event {
+    fn repr(&self) {
+        println!("{} {} {}", self.id, self.description, self.sport);
+        for c in self.competitors.iter() {
+            println!("{}", c.to_string());
[…]

### 2020-03-29 rust/sipoxide/src/bov.rs
interm 2

@@ -37,10 +37,11 @@ pub struct Event {
     pub teaser_allowed: Option<bool>,
     pub competition_id: Option<String>,
     pub notes: String,
-    pub num_markets: Option<i128>,
+    pub num_markets: Option<u64>,
     pub last_modified: Option<i128>,
     pub competitors: Vec<Competitor>,
     pub display_groups: Option<Vec<DisplayGroup>>,
+    // pub display_groups: Vec<DisplayGroup>,
 }
 
 #[derive(Serialize, Deserialize, Debug)]
@@ -54,8 +55,8 @@ pub struct Competitor {
 pub struct DisplayGroup {
     pub id: String,
     pub description: String,
-    pub default_type: bool,
-    pub alternate_type: bool,
+    pub default_type: Option<bool>,
+    pub alternate_type: Option<bool>,
     pub markets: Vec<Market>,
     pub order: i128,
 }
@@ -63,12 +64,12 @@ pub struct DisplayGroup {
 #[derive(Serialize, Deserialize, Debug)]
 pub struct Market {
     pub id: String,
-    pub description_key: String,
+    pub description_key: Option<String>,
     pub description: String,
     pub key: String,
-    pub market_type_id: String,
+    pub market_type_id: Option<String>,
     pub status: String,
-    pub single_only: bool,
+    pub single_only: Option<bool>,
     pub notes: String,
     pub period: Period,
     pub outcomes: Vec<Outcome>,
@@ -105,4 +106,5 @@ pub struct Price {
     pub indonesian: String,
     pub hongkong: String,
     pub handicap: Option<String>,
+    pub handicap2: Option<String>,
 }

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -3,39 +3,40 @@ extern crate serde_derive;
 extern crate serde;
 // extern crate reqwest;
 // use reqwest::Error;
-
+use std::fmt;
+use std::fmt::Debug;
 use std::fs;
 
 mod bov;
 
-impl bov::Outcome {
-    fn repr(&self) {
-        println!("oc {} {}", self.description, self.price.decimal);
-        // self.price.repr()
-    }
-}
-impl bov::Market {
-    fn repr(&self) {
-        println!("{}", self.description);
-        for o in self.outcomes.iter() {
-            o.repr();
-        }
-    }
-}
-impl bov::DisplayGroup {
-    fn repr(&self) {
-        for m in self.markets.iter() {
-            m.repr();
-        }
-    }
-}
+// impl bov::Outcome {
+//     fn repr(&self) {
+//         println!("oc {} {}", self.description, self.price.decimal);
+//         // self.price.repr()
+//     }
+// }
+// impl bov::Market {
+//     fn repr(&self) {
+//         println!("{}", self.description);
+//         for o in self.outcomes.iter() {
+//             o.repr();
+//         }
+//     }
+// }
+// impl bov::DisplayGroup {
+//     fn repr(&self) {
+//         for m in self.markets.iter() {
+//             m.repr();
+//         }
+//     }
+// }
 
 impl bov::Root {
-    fn repr(&self) {
-        for e in self.events.iter() {
-            e.repr();
-        }
-    }
+    // fn repr(&self) {
+    //     for e in self.events.iter() {
+    //         e.repr();
+    //     }
+    // }
 
     fn count_events(&self) -> u64 {
         let mut n: u64 = 0;
@@ -46,77 +47,158 @@ impl bov::Root {
     }
 }
 
-impl ToString for bov::Competitor {
+// impl ToString for bov::Competitor {
+//     fn to_string(&self) -> String {
+//         return format!("Competitor {} {} {}", self.id, self.name, self.home);
+//     }
+// }
+// impl ToString for bov::Outcome {
+//     fn to_string(&self) -> String {
+//         return format!("oc {} {}", self.description, self.price.decimal);
+//     }
+// }
+// impl ToString for bov::Market {
+//     fn to_string(&self) -> String {
+//         return format!("mkt {} {}", self.id, self.description);
+//     }
+// }
+impl ToString for bov::Price {
     fn to_string(&self) -> String {
[…]

### 2020-03-29 rust/sipoxide/src/main.rs
interm 2

@@ -138,20 +138,14 @@ fn parse() {
         .expect("Something went wrong reading the file")
         .to_string();
 
-    // let ds: Vec<bov::Root> = serde_json::from_str(&contents).unwrap();
-    let ds: Vec<bov::DisplayGroup> = serde_json::from_str(&contents).unwrap();
-    println!("{}", ds[0].id);
-    // let mut n: u64 = 0;
-    // println!("{}", ds[0]
-    // .events[0]
-    // .display_groups[0].expect("fuck")
-    // .markets[0].expect("fuck")
-    // .outcomes[0].expect("fuck")
-    // .price.decimal).expect("fuck");
+    let ds: Vec<bov::Root> = serde_json::from_str(&contents).unwrap();
+    // let ds: Vec<bov::DisplayGroup> = serde_json::from_str(&contents).unwrap();
+    // println!("{}", ds[0].id);
+    let mut n: u64 = 0;
     for s in ds.iter() {
-        // s is a 
-        println!("{}", s.to_string());
-        // for e in s.events.iter() {
+        // s is a Root
+        // println!("{}", s.to_string());
+        for e in s.events.iter() {
             // match e.display_groups {
             //     Some(dgs) => {
             //         println!("{:?}", dgs.iter().to_string().format(", "));
@@ -160,18 +154,18 @@ fn parse() {
             //         println!("no dgs");
             //     },
             // };
-            // if let Some(dgs) = &e.display_groups {
-            //     for dg in dgs.iter() {
-            //         for m in dg.markets.iter() {
-            //             for oc in m.outcomes.iter() {
-            //                 println!("{} {} {} {}", e.id, e.description, dg.description, oc.price.decimal);
-            //             }
-            //         }
-            //         println!("{}", dg);
-            //     }
-            // } else {
-            //     println!("FUCK {} {} {}", e.id, e.description, e.sport);
-            // }
+            if let Some(dgs) = &e.display_groups {
+                for dg in dgs.iter() {
+                    for m in dg.markets.iter() {
+                        for oc in m.outcomes.iter() {
+                            println!("{} {} {} {}", e.id, e.description, dg.description, oc.price.decimal);
+                        }
+                    }
+                    println!("{}", dg);
+                }
+            } else {
+                println!("FUCK {} {} {}", e.id, e.description, e.sport);
+            }
             // for dg in e.display_groups.iter() {
             //     for m in dg.markets.iter() {
[…]

### 2020-03-29 rust/sipoxide/src/bov.rs
tmp4

@@ -2,6 +2,7 @@ extern crate serde;
 // use serde::{Serialize, Deserialize};
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Root {
     pub path: Vec<Path>,
     pub events: Vec<Event>,
@@ -9,6 +10,7 @@ pub struct Root {
 
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Path {
     pub id: String,
     pub link: Option<String>,
@@ -22,6 +24,7 @@ pub struct Path {
 }
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Event {
     pub id: String,
     pub description: String,
@@ -40,11 +43,12 @@ pub struct Event {
     pub num_markets: Option<u64>,
     pub last_modified: Option<i128>,
     pub competitors: Vec<Competitor>,
-    pub display_groups: Option<Vec<DisplayGroup>>,
-    // pub display_groups: Vec<DisplayGroup>,
+    // pub display_groups: Option<Vec<DisplayGroup>>,
+    pub display_groups: Vec<DisplayGroup>,
 }
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Competitor {
     pub id: String,
     pub name: String,
@@ -52,6 +56,7 @@ pub struct Competitor {
 }
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct DisplayGroup {
     pub id: String,
     pub description: String,
@@ -62,6 +67,7 @@ pub struct DisplayGroup {
 }
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Market {
     pub id: String,
     pub description_key: Option<String>,
@@ -77,6 +83,7 @@ pub struct Market {
 }
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Period {
     pub id: String,
     pub description: String,
@@ -86,6 +93,7 @@ pub struct Period {
 }
 
 #[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
 pub struct Outcome {
     pub id: String,
[…]

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -112,7 +112,7 @@ impl fmt::Display for bov::Event {
 
 impl fmt::Display for bov::DisplayGroup {
     fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
-        write!(f, "{:#?}", self.markets)
+        write!(f, "DG_START{} {} {} {:#?}", self.id, self.description, self.order, self.markets.iter())
     }
 }
 
@@ -134,17 +134,20 @@ impl fmt::Display for bov::Outcome {
 
 
 fn parse() {
-    let contents = fs::read_to_string("./data/dgs.json")
+    let contents = fs::read_to_string("./data/root.json")
         .expect("Something went wrong reading the file")
         .to_string();
 
     let ds: Vec<bov::Root> = serde_json::from_str(&contents).unwrap();
     // let ds: Vec<bov::DisplayGroup> = serde_json::from_str(&contents).unwrap();
+    // let ds: bov::Event = serde_json::from_str(&contents).unwrap();
+    // println!("{}", ds.description);
+    // println!("{:#?}", ds.display_groups);
     // println!("{}", ds[0].id);
     let mut n: u64 = 0;
     for s in ds.iter() {
         // s is a Root
-        // println!("{}", s.to_string());
+        println!("{}", s.to_string());
         for e in s.events.iter() {
             // match e.display_groups {
             //     Some(dgs) => {
@@ -166,14 +169,14 @@ fn parse() {
             } else {
                 println!("FUCK {} {} {}", e.id, e.description, e.sport);
             }
-            // for dg in e.display_groups.iter() {
-            //     for m in dg.markets.iter() {
-            //         for oc in m.outcomes.iter() {
-            //             println!("{} {} {} {}", e.id, e.description, dg.description, oc.price.decimal);
-            //         }
-            //     }
-            //     println!("{}", dg);
-            // }
+            for dg in e.display_groups.iter() {
+                for m in dg.markets.iter() {
+                    for oc in m.outcomes.iter() {
+                        println!("{} {} {} {}", e.id, e.description, dg.description, oc.price.decimal);
+                    }
+                }
+                println!("{}", dg);
+            }
             // match 
             // if e.display_groups.is_some() {
             //     println!("{}", e.display_groups[0].)

### 2020-03-29 rust/sipoxide/src/main.rs
tmp4

@@ -157,18 +157,18 @@ fn parse() {
             //         println!("no dgs");
             //     },
             // };
-            if let Some(dgs) = &e.display_groups {
-                for dg in dgs.iter() {
-                    for m in dg.markets.iter() {
-                        for oc in m.outcomes.iter() {
-                            println!("{} {} {} {}", e.id, e.description, dg.description, oc.price.decimal);
-                        }
-                    }
-                    println!("{}", dg);
-                }
-            } else {
-                println!("FUCK {} {} {}", e.id, e.description, e.sport);
-            }
+            // if let Some(dgs) = &e.display_groups {
+            //     for dg in dgs.iter() {
+            //         for m in dg.markets.iter() {
+            //             for oc in m.outcomes.iter() {
+            //                 println!("{} {} {} {}", e.id, e.description, dg.description, oc.price.decimal);
+            //             }
+            //         }
+            //         println!("{}", dg);
+            //     }
+            // } else {
+            //     println!("FUCK {} {} {}", e.id, e.description, e.sport);
+            // }
             for dg in e.display_groups.iter() {
                 for m in dg.markets.iter() {
                     for oc in m.outcomes.iter() {
@@ -177,19 +177,7 @@ fn parse() {
                 }
                 println!("{}", dg);
             }
-            // match 
-            // if e.display_groups.is_some() {
-            //     println!("{}", e.display_groups[0].)
-            // } else
 
-            // println!("e {}", e);
-            // e.repr();
-            // for dg in e.display_groups.iter() {
-            //     println!("dg {}", dg.id);
-            //     for m in dg.markets.iter() {
-            //         println!("{:?}", m.to_string());
-            //     }
-            // }
         }
 
         n += s.count_events()

### 2020-03-29 rust/sipoxide/src/bov.rs
to_csv working

@@ -1,6 +1,19 @@
 extern crate serde;
 // use serde::{Serialize, Deserialize};
 
+#[derive(Debug, Deserialize)]
+#[serde(rename_all = "camelCase")]
+struct Record {
+    id: String,
+    sport: String,
+    event_desc: String,
+    dg_desc: String,
+    mkt_desc: String,
+    oc_desc: String,
+    price: String,
+    hc: Option<String>,
+}
+
 #[derive(Serialize, Deserialize, Debug)]
 #[serde(rename_all = "camelCase")]
 pub struct Root {

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -1,11 +1,15 @@
 #[macro_use]
 extern crate serde_derive;
 extern crate serde;
+extern crate csv;
 // extern crate reqwest;
 // use reqwest::Error;
 use std::fmt;
 use std::fmt::Debug;
 use std::fs;
+use std::error::Error;
+use std::io;
+use std::process;
 
 mod bov;
 
@@ -98,11 +102,13 @@ impl ToString for bov::Price {
 //         };
 //     }
 // }
-// impl fmt::Display for bov::Root {
-//     fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
-//         write!(f, "{}", self.events)        
-//     }
-// }
+
+
+impl fmt::Display for bov::Root {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(f, "{:#?}", self.events)        
+    }
+}
 
 impl fmt::Display for bov::Event {
     fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
@@ -133,61 +139,70 @@ impl fmt::Display for bov::Outcome {
 //     }
 
 
-fn parse() {
+fn parseAndWrite() -> Result<(), Box<Error>> {
+
+    let write_fn = "./data/root.csv"; 
+
+    let mut wtr = csv::Writer::from_path(write_fn)?;
+
+    wtr.write_record(&["id", "sport", "event_desc", "dg_desc", "mkt_desc", "oc_desc", "price", "hc"])?;
+
     let contents = fs::read_to_string("./data/root.json")
         .expect("Something went wrong reading the file")
         .to_string();
 
+
     let ds: Vec<bov::Root> = serde_json::from_str(&contents).unwrap();
-    // let ds: Vec<bov::DisplayGroup> = serde_json::from_str(&contents).unwrap();
-    // let ds: bov::Event = serde_json::from_str(&contents).unwrap();
-    // println!("{}", ds.description);
-    // println!("{:#?}", ds.display_groups);
-    // println!("{}", ds[0].id);
+
     let mut n: u64 = 0;
     for s in ds.iter() {
         // s is a Root
-        println!("{}", s.to_string());
+        // println!("{:#?}", s);
         for e in s.events.iter() {
-            // match e.display_groups {
-            //     Some(dgs) => {
-            //         println!("{:?}", dgs.iter().to_string().format(", "));
-            //     },
-            //     _ => {
-            //         println!("no dgs");
-            //     },
-            // };
[…]

### 2020-03-29 rust/sipoxide/src/bov.rs
tokio + reqwest

@@ -1,5 +1,6 @@
 extern crate serde;
 // use serde::{Serialize, Deserialize};
+use std::fmt;
 
 #[derive(Debug, Deserialize)]
 #[serde(rename_all = "camelCase")]
@@ -21,6 +22,11 @@ pub struct Root {
     pub events: Vec<Event>,
 }
 
+impl fmt::Display for Root {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(f, "{:#?}", self.events)
+    }
+}
 
 #[derive(Serialize, Deserialize, Debug)]
 #[serde(rename_all = "camelCase")]
@@ -60,6 +66,12 @@ pub struct Event {
     pub display_groups: Vec<DisplayGroup>,
 }
 
+impl fmt::Display for Event {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(f, "{:#?}", self.display_groups)
+    }
+}
+
 #[derive(Serialize, Deserialize, Debug)]
 #[serde(rename_all = "camelCase")]
 pub struct Competitor {
@@ -79,6 +91,19 @@ pub struct DisplayGroup {
     pub order: i128,
 }
 
+impl fmt::Display for DisplayGroup {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(
+            f,
+            "DG_START{} {} {} {:#?}",
+            self.id,
+            self.description,
+            self.order,
+            self.markets.iter()
+        )
+    }
+}
+
 #[derive(Serialize, Deserialize, Debug)]
 #[serde(rename_all = "camelCase")]
 pub struct Market {
@@ -93,6 +118,12 @@ pub struct Market {
     pub period: Period,
     pub outcomes: Vec<Outcome>,
     pub sort_type: Option<String>,
+}
+
+impl fmt::Display for Market {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(f, "{:#?}", self.outcomes)
+    }
 }
 
 #[derive(Serialize, Deserialize, Debug)]
@@ -117,6 +148,12 @@ pub struct Outcome {
     pub competitor_id: Option<String>,
 }
 
+impl fmt::Display for Outcome {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
[…]

### 2020-03-29 rust/sipoxide/src/main.rs

@@ -1,223 +1,91 @@
 #[macro_use]
 extern crate serde_derive;
-extern crate serde;
 extern crate csv;
+extern crate serde;
 // extern crate reqwest;
 // use reqwest::Error;
-use std::fmt;
-use std::fmt::Debug;
-use std::fs;
+use http::{Request, Response};
+use serde::de;
 use std::error::Error;
-use std::io;
-use std::process;
+use std::fmt;
+use std::fs;
 
 mod bov;
 
-// impl bov::Outcome {
-//     fn repr(&self) {
-//         println!("oc {} {}", self.description, self.price.decimal);
-//         // self.price.repr()
-//     }
-// }
-// impl bov::Market {
-//     fn repr(&self) {
-//         println!("{}", self.description);
-//         for o in self.outcomes.iter() {
-//             o.repr();
-//         }
-//     }
-// }
-// impl bov::DisplayGroup {
-//     fn repr(&self) {
-//         for m in self.markets.iter() {
-//             m.repr();
-//         }
-//     }
-// }
-
-impl bov::Root {
-    // fn repr(&self) {
-    //     for e in self.events.iter() {
-    //         e.repr();
-    //     }
-    // }
-
-    fn count_events(&self) -> u64 {
-        let mut n: u64 = 0;
-        for e in self.events.iter() {
-            n += 1;
-        }
-        return n;
-    }
-}
-
-// impl ToString for bov::Competitor {
-//     fn to_string(&self) -> String {
-//         return format!("Competitor {} {} {}", self.id, self.name, self.home);
-//     }
-// }
-// impl ToString for bov::Outcome {
-//     fn to_string(&self) -> String {
-//         return format!("oc {} {}", self.description, self.price.decimal);
-//     }
-// }
-// impl ToString for bov::Market {
-//     fn to_string(&self) -> String {
-//         return format!("mkt {} {}", self.id, self.description);
-//     }
-// }
-impl ToString for bov::Price {
-    fn to_string(&self) -> String {
-        return format!("mkt {} {} {}", self.id, self.american, self.decimal);
-    }
-}
-
-// impl ToString for bov::DisplayGroup {
-//     fn to_string(&self) -> String {
-//         return format!("Dg {} {}", self.id, self.description);
-//     }
-// }
-
-
-// impl ToString for bov::Event {
-//     fn to_string(&self) -> String {
-//         // return format!("ev {} {} {} {:?}", self.id, self.sport, self.description, self.display_groups);
[…]

### 2020-03-29 rust/sipoxide/src/main.rs
change error to dyn error

@@ -2,17 +2,11 @@
 extern crate serde_derive;
 extern crate csv;
 extern crate serde;
-// extern crate reqwest;
-// use reqwest::Error;
-use http::{Request, Response};
-use serde::de;
 use std::error::Error;
-use std::fmt;
-use std::fs;
 
 mod bov;
 
-fn parseAndWrite(json_data: String) -> Result<(), Box<Error>> {
+fn parse_and_write(json_data: String) -> Result<(), Box<dyn Error>> {
     let write_fn = "./data/root.csv";
 
     let mut wtr = csv::Writer::from_path(write_fn)?;
@@ -85,7 +79,7 @@ async fn main() -> Result<(), reqwest::Error> {
 
     let body = res.text().await?;
 
-    parseAndWrite(body.to_string());
+    parse_and_write(body.to_string());
 
     Ok(())
 }

### 2020-03-30 random/school/paper.tex
add paper

\documentclass[12pt]{article}
\usepackage[headheight=12pt,headsep=0pt]{geometry}
\renewcommand*\familydefault{\sfdefault}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{lipsum} % only for showing some sample text
\setlength\parindent{24pt}
\linespread{2}
\fancyhf{} % clear all header and footers
\renewcommand{\headrulewidth}{0pt} % remove the header rule
\rhead{\thepage}
\pagestyle{fancy}
% \author{Anand Jain}
% \date{3 27 20}

% \title{\small Sosc Winter Quarter \\ 
\usepackage{lmodern}

\begin{document}
\noindent Anand Jain \\ 
Ali Feser \\
3/27/20 \\
Power, Identity, and Resistance-2 
\begin{center}
    MCM' and the Tendency of the Rate of Profit
\end{center}
\begin{itemize} 
    \item In Capital, Marx asks how a capitalist can purchase something with a certain value and sell it at a higher value. 
    \item Marx concludes that the defining characteristic of a capitalistic society is the ruling class' ability to valorize their capital, defined by the equation MCM'. 
    \item Captialist ownership of surplus value, the increasing proportion of constant capital to variable capital, and the declining rate of profit provide as the basis for Marx's claim that the capitalist mode of production will necessarily be replaced.

    \item I will define the model that Smith presents, contrast with Marx, and show that the structural contradictions in capitalism that Marx presents as necessitating a post-capitalist economy follow from the calculation of $\lim_{t \to \infty}$, but fails to provide bounds on the timing of this eventuality. 
    \item Instead of viewing the declining rate of profit as a indicator of capitalisms inevitable demise, I demonstrate the tendency of the rate of profit to fall is the enabling factor that allows for surplus value to be redistributed, in the form of lower cost technology, enabling wage-laborers to enter the hussle.
    \item A key feature of Smith's model claims maximal individual liberty is ideal for economic and technological growth because the function optimal\_action(someone\_else) is incomputable. 
    \item Smith defines growth based off of the total value of commodities, claiming that services rarely have value after the service is complete. \textbf{quote}
    \item Smith describes a commodity by it's exchange value/worth, $W$, derived by the sum of the constant capital, variable capital, and surplus value, given by $c + L + s = W$. \textbf{quote}
    \item Ignoring economies of scale for this paper, I assume linearity with commodity quantity $q$ to arrive at $\forall q \in \mathbb{N}, \forall{cLs} \in \mathbb{R^{+}}, q(c + L + s) = qW = qc + qL + qs $. \textbf{quote}
    \item The nation's economy will be defined as a graph on a function $f(t) = G_t(V_t, E_t)$. 
    \item Defining this graph on a function allows for any vertex in set of vertices $V$, and for any edge in the set of edges $E$ to change continuously.
    \item Now to define what each vertex and edge is (person and instantaneous time trade respectively): We will assume, following Smith's claim that there are uncountably many complexities regarding human action that necesitate individual liberty. \textbf{quote} 
    \item We can define three important types (commodities, people, and trades) that generate this model. 
    \item A Commodity is a tuple containing: quantity/amount $q$, per-unit constant capital cost $c$, the per-unit variable capital cost $L$, and resulting per-unit surplus value $s$. 
    \item Let the set of all commodities be an infinite ordered-set denoted $\boldsymbol{C}$ with cardinality $m = |\boldsymbol{C}|$. \textbf{quote}.

    \item A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities (called assets) $A_{it} = ((q, c, L, s)_{1}, (q, c, L, s)_{2},...,(q, c, L, s)_{m})$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
    \item A Trade at time $t$ is an instantaneous bidirected edge between the two Persons. 
    \item Final model assumptions: N-Person trades/cliques are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed. 
    \item Exercising a use-value can be represented as a vertex with an edge to itself, called a loop, in which a trade with one's own commodites consumes their existence.
    \item Notationally: $q_{ijt_{a}} = V_{it_{a}}.A_{jq} =$ the quantity $q$ of commodity $j$ that person $i$ owns at time $a$, similarly for the constant capital, variable capital, and surplus value.
    \item An example of labor in this model: $P_i$ Trades with $P_j$ for assets $A$ and Trades, typically money, with $P_k$.
    \item $P_k$ expends their own assets through work/labour by a series of Trades with $P_i$ in which $A$ is augmented into a new commodity with surplus value, owned by $P_i$.  
    \item Note, Money::Commodity, but acts as a commodity that serves as a primary mode of conversion for commodities associated with a consumable use-value, as the use-value of money is to employ it and generate a surplus value, given by MCM'.
    \item \textbf{quote on monetary value}
    \item This quote is a based off of the mean-value theorem (MVT); we can convert all commodities into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc.
    \item If we let $\boldsymbol{V} :=\bigcup\limits_{t \leq t_a} V_t \in G_t$ and $\boldsymbol{E} :=\bigcup\limits_{t \leq t_a} E_t \in G_t$ maximal set of all people and trades, then we can define the wealth of a nation at time $t_a$ as $\sum\limits_i^n$ $\sum\limits_j^m$ $q_{ijt_{a}} * (c_{ijt_{a}} + L_{ijt_{a}} + s_{ijt_{a}})$. 
    \item The reason that it is not a sum over all $t < t_a$ is that the surplus value accumulated through production is stored in the costant capital of the current commodities owned by people. \textbf{quote}
    \item This framework makes easy to interpret the valorization of capital.
    \item For example, if a Person $i$ at time $t$ with commodities/assets $A$ can employ their capital in a succession of Trades and conclude with more Commodities than starting, then they have valorized their capital via arbitrage.
    \item  Profitting off of the discrepancies in prices is not a zero sum game, as the arbitrageur is forcing price stability by taking profits from commodity producers, who subsequently need to employ more constant capital to reduce the per-unit variable capital cost.
    \item We now want to extend this model to account for the class dynamics of MCM' that Marx presents as necessitating a post-capitalist mode of production and show that the discretization of individuals into homogeneous classes violates Smith's key assertion that it is impossible to calculate the optimal action for any given individual. 
    \item \textbf{quote on MCM' and classes}
    \item \textbf{something about supply demand and normal distributions}
    \item Marx claims that the worker is completely reduced to selling their labor for wages that are spent entirely on the means of subsistence and reproduction. \textbf{quote}
    \item Let $\alpha$ be a set of assets defining the means of subsistence, and therefore a death condition given by: $\{A_i - x < 0| x \in \alpha \}$  
    \item We want to extend this model to explain labor/class relations, the labor theory of value, and the relative dimunition of the variable part of capital to constant capital.
    \item We can extend the type Person, with an attribute characterizing their class, where a Person is a wage-laborer $\omega$ or a capitalist $\rho$, $P_i::\omega$ and $P_i::\rho$ respectively.
    \item \textbf{Quote on use value being equivalent to exchange value}
    \item Marx identifies the apparent nonlinear behavior of the proportion of constant capital to variable capital as technology advances.
    \item  \textbf{quote}
    \item However, it is not clear that this eventuality is one that will necessarily be witnessed.
    \item  Zeno's paradox is a simple analogy for the amount of time it will take for the proportion of constant capital to entirely encompass that of variable capital, which is the real precondition for a post-capitalist mode of production.
    \item We can only say what the behavior is of $\lim_{t \to \infty}$, but not when it will happen.

\end{itemize}
\hspace{\parindent}

In conclusion

\begin{enumerate}
    \item Smith 20: "Every man thus lives by exchanging, or becomes in some measure a merchant, and the society itself grows to be what is properly a commercial society,"
    \item Marx 41: "an immense accumulation of commodities,"* its unit being a single commodity. (demonstrates $\in \mathbb{N}$, capitalist basis of value is commodities)
    \item Marx 42: When treating of use-value, we always assume to be dealing with definite quantities, such as dozens of watches, yards of linen, or tons of iron.
\end{enumerate}

\begin{itemize}
    \item \href{https://en.wikipedia.org/wiki/Graph_(abstract_data_type)}{Graphs}

\end{itemize}

% and are consequent from discretizing the populous into homogeneous classes and that collective ownership

% let $n := |\boldsymbol{V}|$ being the total number of people to have existed in this society.
% $\forall v, e \in (\boldsymbol{V}, \boldsymbol{E}), v::$Person$, e::$Trade, where Person at time T $:= (A_{t}, B_{t}, u_{t}, e_{t})$ where $u$ is a function that takes in 
\end{document}

### 2020-03-30 random/school/paper.tex
add json_file_to_csv() in main.rs

@@
 
-    \item A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities (called assets) $A_{it} = ((q, c, L, s)_{1}, (q, c, L, s)_{2},...,(q, c, L, s)_{m})$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
-    \item A Trade at time $t$ is an instantaneous bidirected edge between the two Persons. 
-    \item Final model assumptions: N-Person trades/cliques are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed. 
+    \item A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities (called assets) $A_{it} = ((q, c, L, s)_{1}, (q, c, L, s)_{2},...,(q, c, L, s)_{m})$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade $\hat{e_{ijt}}$, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
+    \item A Trade at time $t$ is an instantaneous bidirected edge between the two Persons and N-Person trades are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed.
     \item Exercising a use-value can be represented as a vertex with an edge to itself, called a loop, in which a trade with one's own commodites consumes their existence.
@@
     \item We want to extend this model to explain labor/class relations, the labor theory of value, and the relative dimunition of the variable part of capital to constant capital.
-    \item We can extend the type Person, with an attribute characterizing their class, where a Person is a wage-laborer $\omega$ or a capitalist $\rho$, $P_i::\omega$ and $P_i::\rho$ respectively.
+    \item We can extend the type Person, with an attribute characterizing their class, where a Person is a wage-laborer $\beta$ or a capitalist $\gamma$, $P_i::\beta$ and $P_i::\gamma$ respectively.
     \item \textbf{Quote on use value being equivalent to exchange value}
@@
 \end{itemize}
-\hspace{\parindent}
 
-In conclusion
+Marx, in assuming that
 

### 2020-03-30 rust/sipoxide/src/bov.rs

@@ -1,5 +1,4 @@
 extern crate serde;
-// use serde::{Serialize, Deserialize};
 use std::fmt;
 
 #[derive(Debug, Deserialize)]

### 2020-03-30 rust/sipoxide/src/main.rs

@@ -3,8 +3,52 @@ extern crate serde_derive;
 extern crate csv;
 extern crate serde;
 use std::error::Error;
+use std::fs;
 
 mod bov;
+mod scores;
+
+fn test_json_to_csv() {
+    json_file_to_csv("./data/scores.json".to_string(), "./data/scores.csv".to_string());
+}
+
+fn json_file_to_csv(read_fn: String, write_fn: String) -> Result<(), Box<dyn Error>> {
+    let json_data = fs::read_to_string(read_fn)
+        .expect("Something went wrong reading the file")
+        .to_string();
+    let mut wtr = csv::Writer::from_path(write_fn)?;
+
+    let ds: Vec<scores::Root> = serde_json::from_str(&json_data).unwrap();
+    for elt in ds.iter() {
+        if let Some(ls) = &elt.latest_score {
+            let rec = &[
+                elt.event_id.to_string(),
+                elt.sport.to_string(),
+                elt.game_status.to_string(),
+                elt.last_updated.to_string(),
+                elt.clock.to_string(),
+                ls.visitor.to_string(),
+                ls.home.to_string(),
+            ];
+            println!("{:#?}", rec);
+            wtr.write_record(rec)?;
+        } else {
+            let rec = &[
+                elt.event_id.to_string(),
+                elt.sport.to_string(),
+                elt.game_status.to_string(),
+                elt.last_updated.to_string(),
+                elt.clock.to_string(),
+                "".to_string(),
+                "".to_string(),
+            ];
+            println!("{:#?}", rec);
+            wtr.write_record(rec)?;
+        }
+    }
+    wtr.flush()?;
+    Ok(())
+}
 
 fn parse_and_write(json_data: String) -> Result<(), Box<dyn Error>> {
     let write_fn = "./data/root.csv";
@@ -21,11 +65,6 @@ fn parse_and_write(json_data: String) -> Result<(), Box<dyn Error>> {
         "price",
         "hc",
     ])?;
-    // TODO use in test
-    // let json_data = fs::read_to_string("./data/root.json")
-    //     .expect("Something went wrong reading the file")
-    //     .to_string();
-
     let ds: Vec<bov::Root> = serde_json::from_str(&json_data).unwrap();
 
     for s in ds.iter() {
@@ -83,3 +122,6 @@ async fn main() -> Result<(), reqwest::Error> {
 
     Ok(())
 }
+
+
+

### 2020-03-30 rust/sipoxide/src/scores.rs

@@ -1,0 +1,233 @@
+extern crate serde;
+use std::fmt;
+
+#[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
+pub struct Root {
+    pub event_id: i64,
+    pub event_source: String,
+    pub alt_ids: AltIds,
+    pub scoreboard_available: bool,
+    pub sport: String,
+    pub latest_score: Option<LatestScore>,
+    pub clock: Clock,
+    pub sport_details: Option<SportDetails>,
+    pub game_status: String,
+    pub last_updated: String,
+    pub display_visitor_team_first: bool,
+    #[serde(default)]
+    pub previous_periods_score: Vec<PreviousPeriodsScore>,
+    pub current_period_score: Option<CurrentPeriodScore>,
+    pub last_significant_key_event: Option<LastSignificantKeyEvent>,
+    pub last_significant_key_event_index: Option<i64>,
+}
+
+impl fmt::Display for Root {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        if let Some(cur_score) = &self.latest_score {
+            write!(f, "{}, {}, {}, {}, {} {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock, cur_score)
+        } else {
+            write!(f, "{}, {}, {}, {}, {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock)
+        }
+    }
+}
+
+#[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
+pub struct AltIds {
+    #[serde(rename = "BGS")]
+    pub bgs: i64,
+    pub feed_code: Option<i64>,
+}
+
+#[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
+pub struct LatestScore {
+    pub home: String,
+    pub visitor: String,
+}
+
+impl fmt::Display for LatestScore {
+    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
+        write!(f, "{:?}, {:?}", self.visitor, self.home)
+    }
+}
+
+#[derive(Serialize, Deserialize, Debug)]
+#[serde(rename_all = "camelCase")]
+pub struct Clock {
+    pub period: String,
+    pub period_number: i64,
+    pub game_time: String,
[…]

### 2020-03-30 rust/sipoxide/src/main.rs
add json_file_to_csv() in main.rs

@@ -26,7 +26,9 @@ fn json_file_to_csv(read_fn: String, write_fn: String) -> Result<(), Box<dyn Err
                 elt.sport.to_string(),
                 elt.game_status.to_string(),
                 elt.last_updated.to_string(),
-                elt.clock.to_string(),
+                elt.clock.period_number.to_string(),
+                elt.clock.relative_game_time_in_secs.to_string(),
+                elt.clock.is_ticking.to_string(),
                 ls.visitor.to_string(),
                 ls.home.to_string(),
             ];
@@ -38,7 +40,9 @@ fn json_file_to_csv(read_fn: String, write_fn: String) -> Result<(), Box<dyn Err
                 elt.sport.to_string(),
                 elt.game_status.to_string(),
                 elt.last_updated.to_string(),
-                elt.clock.to_string(),
+                elt.clock.period_number.to_string(),
+                elt.clock.relative_game_time_in_secs.to_string(),
+                elt.clock.is_ticking.to_string(),
                 "".to_string(),
                 "".to_string(),
             ];

### 2020-03-30 rust/sipoxide/src/scores.rs

@@ -25,9 +25,9 @@ pub struct Root {
 impl fmt::Display for Root {
     fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
         if let Some(cur_score) = &self.latest_score {
-            write!(f, "{}, {}, {}, {}, {} {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock, cur_score)
+            write!(f, "{}, {}, {}, {}, {} {} {} {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock.period_number, self.clock.relative_game_time_in_secs self.clock.is_ticking, cur_score)
         } else {
-            write!(f, "{}, {}, {}, {}, {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock)
+            write!(f, "{}, {}, {}, {}, {} {} {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock.period_number, self.clock.relative_game_time_in_secs self.clock.is_ticking)
         }
     }
 }

### 2020-04-02 random/career_preparation/cover_letters/intel_data.tex
bread.md and paper

--- 2020-03-16 random/career_preparation/cover_letters/intel.tex
@@
 
-In senior year of high school, I was taking AP Computer Science Principles and we had to do two presentations.
-I did my first presentation on convolutional neural networks and my second on quantum computing.
-I didn’t realize until I learned more about complexity theory and big-O notation in college how amazing quantum systems are. 
-This profound and numinous field of study is racing to Landauer's limit and has given me an exponentially greater appreciation for the beauty of nature.
-
-I'm hoping to contribute some meaningful addition to helping us use NISQ devices to improve lives around the world.
-As founder of the UChicago Quantum Society, I am hoping to bring back insights in how to communicate scientific works to general audiences and help grow the community of the quantum-curious.
-
-\closing{Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu}
+\begin{flushright}
+    Sincerely, \\ Anand Jain \\ University of Chicago 2021 \\ anandj@uchicago.edu
+\end{flushright}
 

### 2020-04-02 random/career_preparation/resume/resume2.tex
bread.md and paper

@@
 \section{SKILLS}
-\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL, \LaTeX\\
-\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
+\textbf{Languages:} Python, Go, Rust, Julia, Bash, C/C++, MySQL, \LaTeX\\
+\textbf{Packages:} PyTorch, Gym, TensorFlow, DiffEq.jl, Pandas, Flask \\
 \textbf{Spoken:} Fluent English. Classroom Hindi, Spanish, and Mandarin
@@
 \textbullet{Agent learns to hedge across time and returns a positive net reward on test set}\\
+\textbullet{Currently porting scraper to Rust\\}
 \textbf{tools:} pytorch, gym, spinningup, go\\
-\textbf{src :} github.com/anandijain/sips /sipgo and /gym-sips
+\textbf{src :} github.com/anandijain/sips (/sipgo $=>$ /sipoxide) and /gym-sips
 

### 2020-04-02 random/school/paper.tex
bread.md and paper

@@
     \item A Commodity is a tuple containing: quantity/amount $q$, per-unit constant capital cost $c$, the per-unit variable capital cost $L$, and resulting per-unit surplus value $s$. 
-    \item Let the set of all commodities be an infinite ordered-set denoted $\boldsymbol{C}$ with cardinality $m = |\boldsymbol{C}|$. \textbf{quote}.
+	\item Let the set of all commodities (past and present) be an infinite ordered-set denoted $\boldsymbol{C}$ with cardinality $m = |\boldsymbol{C}|$. \textbf{quote}.
 
-    \item A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities (called assets) $A_{it} = ((q, c, L, s)_{1}, (q, c, L, s)_{2},...,(q, c, L, s)_{m})$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade $\hat{e_{ijt}}$, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
+    \item A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities (called a Portfolio) $A_{it} = ((q, c, L, s)_{1}, (q, c, L, s)_{2},...,(q, c, L, s)_{m})$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade $\hat{e_{ijt}}$, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
+	\item (does this also mean that from the set of all decisions forall possible trades exists a bijection to the persons bitstring) probably? 
     \item A Trade at time $t$ is an instantaneous bidirected edge between the two Persons and N-Person trades are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed.
@@
 	\item We can only say what the behavior is of $\lim_{t \to \infty}$, but not when it will happen.
-
 \end{itemize}
 
-Marx, in assuming that
+% thoughts/misc
+\begin{itemize}
+	\item It seems like a big problem is addressing market efficiency, because largely as old technologies/commodities with depreciated value, may be more valueable as different technology comes about.
+Difference in market price and value
+	\item In order to support a multi-currency model, it makes no difference that exchanging money is represented by a Trade, since any money can be expressed as the commodities of equivalent exchange value (really market price at current time).
+	\item In Marx's model, we see that the distinction in constant and variable capital can be represented as the component parts of the total capital employed by a Person on the means of production and labor respectively.
+To fit the model to this, we can express capital-labor exchanges (commodity production) #####?
+	\item It arises from a violation of Cauchy-Schwarz.
+Marx assumes that it is never the case that the labor of the worker is for goods that he actually consumes for subsistence.
+Dually, this violates that the worker would ever overwork themselves out of joy of the labor.
+If they are free laboreres, however, exploited to the limits of subsistence, can in improve the production process.
+	\item How do we explain hourly wage, contracts, etc as commodity exchange. A contract's value is largely in the character of the judicial system.
+	\item Need something on cooperation
+	\item money
+	\item to say that a capitalist never becomes a wage laborer or vice versa is wrong.
+marx freq writes that the capitalists aim is capital augmentation, not necesarily commodity production.
+however, where does he address that herein lies the labor of capitalists-asset allocation.
+	\item the inner product of two uncountable vectors is still \in \mathbb{R}. but the degree of error for approximation this use-value is the challenge.
+	\item it is clear that the distribution of portfolios will largely consist of subsistence commodities to be used for use-value, and that this sparsity prevents the exchange of commodities between traders when neither want the other's commodity for it's use value.
+this brings about the money form of commodities.
+it is this shift that makes distinct a capitalist mode of production.
+	\item you can expend labor and capital to gain information about the characteristics of a commodity that give a better approximation of its value, and subsequently market price. 
+	\item to assume that a unified/collective revolution will take place is logistically impossible. it is much more likely that given the inherent flaws in commodity prices, the worst 
+	\item   $can_create_ai()$?  $revolution=true$ : $revolution=false$ this is because the worker would have no barganing power, and theres no job that an ai couldn't do.
+	\item alienation can be described by labor Trades in this model.
+where alienation is a vertex with a loop and an edge to another vertex.
+as this demonstrates the resulting commodity not being owned by the worker.
+	\item @430 selling labor power is a basis but not the only.  
+	\item @430 2 if self-expansion of capital $~$ to $#$ of ppl displaced by it. does this imply that the expansion of capital is $~$ expansion of human knowledge?  
+	\item the soln is knxwledge itself
+	\item if the worker finds themselves dissatisfied with their life, but willing to give up a portion of their wages to remedy the problem, then there exists a market to deliver this want. 
+	thots
+	\item social commodities (experiences/mutual culture) are in a similar position to currency, in that they don't exhibit any use-value and are akin to a service to Smith.
+This has the analogy of prices stabilizing as more of a given commodity is translated into various other commodities, likewise the exchange of culture is exhibited by human connectivity.
+\end{itemize}
 
+% quotes 
 \begin{enumerate}
-    \item Smith 20: "Every man thus lives by exchanging, or becomes in some measure a merchant, and the society itself grows to be what is properly a commercial society,"
-    \item Marx 41: "an immense accumulation of commodities,"* its unit being a single commodity. (demonstrates $\in \mathbb{N}$, capitalist basis of value is commodities)
-    \item Marx 42: When treating of use-value, we always assume to be dealing with definite quantities, such as dozens of watches, yards of linen, or tons of iron.
+    \item Smith 20: Every man thus lives by exchanging, or becomes in some measure a merchant, and the society itself grows to be what is properly a commercial society,
+    \item Marx 35: an immense accumulation of commodities,* its unit being a single commodity. (demonstrates $\in \mathbb{N}$, capitalist basis of value is commodities)
+    \item Marx 35: A commodity is, in the first place, an object outside us, a thing that by its properties satisfies human wants of some sort or another.
+	\item 35: To discover the various uses of things is the work of history.
+    \item Marx 36: When treating of use-value, we always assume to be dealing with definite quantities, such as dozens of watches, yards of linen, or tons of iron.
+	\item 38: but as exchange-values they are merely different quantities, and
+		consequently do not contain an atom of use-value. note - quantities of exchange is separate
+    \item Marx 39: The labour, however, that forms the substance of value,
+is homogeneous human labour, expenditure of one uniform la-
+bour-power. The total labour-power of society, which is embodied
+in the sum total of the values of all commodities produced by that
+society, counts here as one homogeneous mass of human labour-
+power, composed though it be of innumerable individual units.
+Each of these units is the same as any other, so far as it has the
+character of the average labour-power of society, and takes effect as
+such; that is, so far as it requires for producing a commodity, no
+more time than is needed on an average, no more than is socially
+necessary. The labour-time socially necessary is that required to
+produce an article under the normal conditions of production, and
+with the average degree of skill and intensity prevalent at the time.
+	\item 40: The value of a commodity, there-
+fore, varies directly as the quantity, and inversely as the produc
+tiveness, of the labour incorporated in it. 
+	\item 40: A thing can be a use-value, without having value. This is
+the case whenever its utility to man is not due to labour. Such
+are air, virgin soil, uatural meadows, c. A thing can be useful,
+and the product of human labour, without being a commodity.
+Whoever directly satisfies his wants with the produce of his own
+labour, creates, indeed, use-values, but not commodities. 
+In order to produce the latter, he must not only produce use-values, but
+use-values for others, social use-values. 
+    \item Marx 40: The value of a commodity would therefore remain constant,
+if the labour-time required for its production also remained
+constant. But the latter changes with every variation in the
+productiveness of labour. 
+    \item Marx 46: The same change in productive power, which
+	increases the fruitfulness of labour, and, in consequence, the
+	quantity of use-values produced by that labour, will diminish
+	the total value of this increased quantity of use-values, provided
+	such change shorten the total labour-time necessary for their
+	production; and vice versa.
+	\item 88: In the course of time, therefore, some
+portion at least of the products of labour must be produced with
+a special view to exchange. From that moment the distinction
+becomes firmly established between the utility of an object for
+the purposes of consumption, and its utility for the purposes of ex-
+change. Its use-value becomes distinguished from its exchange-
+value. 
+	\item 88: In the direct barter of products, each commodity is directly
+a means of exchange to its owner, and to all other persons an
+equivalent, but that only in so far as it has use-value for them.
+At this stage, therefore, the articles exchanged do not acquire
+a value-form independent of their own use-value, or of the individ-
+ual needs of the exchangers. The necessity for a value-form grows
+with the increasing number and variety of the commodities ex-
+changed. The problem and the means of solution arise simultane-
+ously. 
+	\item 89: Since all commodities are merely particular equivalents of
+money, the latter being their universal equivalent, they, with
+regard to the latter as the universal commodity, play the parts
+of particular commodities. 
+    \item Marx 210: The value of a commodity, it is true, is determined by the quan-
+tity of labour contained in it, but this quantity is itself limited
+by social conditions. If the time socially necessary for the pro-
+duction of any commodity alters— and a given weight of cotton
+represents, after a bad harvest, more labour than after a good
+one — all previously existing commodities of the same class are
+affected, because they are, as it were, only individuals of the
+species, * and their value at any given time is measured by the
+labour socially necessary, i.e., by the labour necessary for their
+production under the then existing social conditions.
+    \item Marx 216: Now since his
+work forms part of a system, based on the social division of
+labour, he does not directly produce the actual necessaries which
+he himself consumes; he produces instead a particular commod-
+ity, yarn for example, whose value is equal to the value of those
+necessaries or of the money with which they can be bought. The
+portion of his day's labour devoted to this purpose, will be
+greater or less, in proportion to the value of the necessaries that he
+daily requires on an average, or, what amounts to the same thing,
+in proportion to the labour-time required on an average to produce
+them.
+    \item Marx 218: the values of the variable capital
+and of the labour-power purchased by that capital are equal,
+and the value of this labour-power determines the necessary
+portion of the working-day; and since, on the other hand, the
+surplus-value is determined by the surplus portion of the work-
+ing-day, it follows that surplus-value bears the same ratio to
+variable capital, that surplus-labour does to necessary labour.
+    \item Marx 244: in any given economic formation of so-
+ciety, where not the exchange-value but the use-value of the prod-
+uct predominates, surplus-labour will be limited by a given set
+of wants which may be greater or less
+    \item 321:  The object of all development of the pro-
+ductiveness of labour, within the limits of capitalist production,
+is to shorten that part of the working-day, during which the work-
+man must labour for his own benefit, and by that very shortening,
+to lengthen the other part of the day, during which he is at liberty
+to work gratis for the capitalist. 
+	\item 323 The labour realised in value, is labour of an average social quality;
+		is consequently the expenditure of average labour-power.
+	\item 376 The union of all these simple instruments, set in motion by a single
+motor, constitutes a machine. Babbage
+	\item 406 Machinery produces relative surplus-value; not only by di-
+rectly depreciating the value of labour-power, and by indirectly
+cheapening the same through cheapening the commodities that
+enter into its reproduction, but also, when it is first introduced
+sporadically into an industry, by converting the labour employed
+by the owner of that machinery, into labour of a higher degree and
+greater efficacy, by raising the social value of the article produced
+above its individual value, and thus enabling the capitalist to
+replace the value of a day's labour-power by a smaller portion of
+the value of a day's product.
+	\item 429 It took both time and experience be-
+fore the workpeople learnt to distinguish between machinery and
+its employment by capital, and to direct their attacks, not against
+the material instruments of production, but against the mode
+in which they are used.
+	\item 430 The whole system of capitalist production is based
+on the fact that the workman sells his labour-power as a commodity.
+	\item 430 The self-expansion of capital by means of machinery is
+thenceforward directly proportional to the number of the work-
+people, whose means of livelihood have been destroyed by that
+machinery.
+
+	\item 440 
+	\item 461 analysing the process of production into its constituent phases,
+and of solving the problems thus proposed by the application of
+mechanics, of chemistry, and of the whole range of the natural
+sciences, becomes the determining principle everywhere. 
+	\item 530 Only by suppressing the
+capitalist form of production could the length of the working-day
+be reduced to the necessary labour-time. But, even in that case,
+the latter would extend its limits. On the one hand, because the
+notion of "means of subsistence" would considerably expand, and
+the labourer would lay claim to an altogether different standard of
+life. On the other hand, because a part of what is now surplus-
+labour, would then count as necessary labour; I mean the labour
+of forming a fund for reserve and accumulation.
+	\item 530 2 The capitalist mode of production, while on the
+one hand, enforcing economy in each individual business, on the oth-
+er hand, begets, by its anarchical system of competition, the most
+outrageous squandering of labour-power and of the social means of
+production, not to mention the creation of a vast number of employ-
+ments, at present indispensable, but in themselves superfluous.
+	\item 530 3 The intensity and productiveness of labour being given, the
+time which society is bound to devote to material production is shorter, and as a consequence, the time at its disposal for the
+free development, intellectual and social, of the individual is
+greater, in proportion as the work is more and more evenly divid-
+ed among all the able-bodied members of society, and as a par-
+ticular class is more and more deprived of the power to shift the
+natural burden of labour from its own shoulders to those of an-
+other layer of society. In this direction, the shortening of the work-
+ing-day finds at last a limit in the generalisation of labour. In
+capitalist society spare time is acquired for one class by converting
+the whole life-time of the masses into labour-time.
+
+	\item  
+	\item 554 society can no more cease to produce
+than it can cease to consume. When viewed, therefore, as a con-
+nected whole, and as flowing on with incessant renewal, every
+social process of production is, at the same time, a process of re-
+production.
+	\item 569: Variable capital is therefore only a particular historical form
+		of appearance of the fund for providing the necessaries of life, or
+		the labour-fund which the labourer requires for the maintenance of
+		himself and family, and which, whatever be the system of social
+		production, he must himself produce and reproduce.
+	\item Marx 612: The composition of capital is to be understood in a twofold sense.
+On the side of value, it is determined by the proportion in which it is divided into constant capital or value of the means of production, and variable capital or value of labour-power, the sum total of wages.
+On the side of material, as it functions in the process of production, ll capital is divided into means of production and living labour-power
+    \item Marx 622: the degree of productivity of labour, in a given society, is expressed in the relative extent of the means of production that one labourer, during a given time 
+    \item Marx 622: the growing extent of the means of production, as compared with the labour-power in corporated with them, is an expression of the growing produc tiveness of labour.
+    \item Marx 622: This change in the technical composition of capital, this
+growth in the mass of means of production, as compared with
+the mass of the labour-power that vivifies them, is reflected again
+in its value-composition, by the increase of the constant consti-
+tuent of capital at the expense of its variable constituent. 
+    \item Marx 624: Every individual capital is a larger or smaller concentration of means of production, with a corresponding command over a larger or smaller labour-army. 
+	\item 627: In any given branch of industry cen-
+tralisation would reach its extreme limit if all the individual
+capitals invested in it were fused into a single capital. 1 In a
+given society the limit would be reached only when the entire
+social capital was united in the hands of either a single capitalist
+or a single capitalist company.
+
+    \item 
 \end{enumerate}
@@
     \item \href{https://en.wikipedia.org/wiki/Graph_(abstract_data_type)}{Graphs}
-
+    \item \href{https://archive.org/details/HannahArendt/page/n1/mode/2up}
 \end{itemize}

### 2020-04-02 rust/sipoxide/src/bov.rs

@@ -1,174 +1,0 @@
-extern crate serde;
-use std::fmt;
-
-#[derive(Debug, Deserialize)]
-#[serde(rename_all = "camelCase")]
-struct Record {
-    id: String,
-    sport: String,
-    event_desc: String,
-    dg_desc: String,
-    mkt_desc: String,
-    oc_desc: String,
-    price: String,
-    hc: Option<String>,
-}
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct Root {
-    pub path: Vec<Path>,
-    pub events: Vec<Event>,
-}
-
-impl fmt::Display for Root {
-    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
-        write!(f, "{:#?}", self.events)
-    }
-}
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct Path {
-    pub id: String,
-    pub link: Option<String>,
-    pub description: String,
-    #[serde(rename = "type")]
-    pub type_field: String,
-    pub sport_code: Option<String>,
-    pub order: i128,
-    pub leaf: bool,
-    pub current: bool,
-}
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct Event {
-    pub id: String,
-    pub description: String,
-    #[serde(rename = "type")]
-    pub type_field: String,
-    pub link: String,
-    pub status: String,
-    pub sport: String,
-    pub start_time: Option<i128>,
-    pub live: bool,
-    pub away_team_first: Option<bool>,
-    pub deny_same_game: Option<String>,
-    pub teaser_allowed: Option<bool>,
-    pub competition_id: Option<String>,
-    pub notes: String,
-    pub num_markets: Option<u64>,
-    pub last_modified: Option<i128>,
-    pub competitors: Vec<Competitor>,
-    // pub display_groups: Option<Vec<DisplayGroup>>,
-    pub display_groups: Vec<DisplayGroup>,
-}
-
-impl fmt::Display for Event {
-    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
-        write!(f, "{:#?}", self.display_groups)
-    }
-}
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct Competitor {
-    pub id: String,
-    pub name: String,
[…]

### 2020-04-02 rust/sipoxide/src/main.rs

@@ -1,131 +1,0 @@
-#[macro_use]
-extern crate serde_derive;
-extern crate csv;
-extern crate serde;
-use std::error::Error;
-use std::fs;
-
-mod bov;
-mod scores;
-
-fn test_json_to_csv() {
-    json_file_to_csv("./data/scores.json".to_string(), "./data/scores.csv".to_string());
-}
-
-fn json_file_to_csv(read_fn: String, write_fn: String) -> Result<(), Box<dyn Error>> {
-    let json_data = fs::read_to_string(read_fn)
-        .expect("Something went wrong reading the file")
-        .to_string();
-    let mut wtr = csv::Writer::from_path(write_fn)?;
-
-    let ds: Vec<scores::Root> = serde_json::from_str(&json_data).unwrap();
-    for elt in ds.iter() {
-        if let Some(ls) = &elt.latest_score {
-            let rec = &[
-                elt.event_id.to_string(),
-                elt.sport.to_string(),
-                elt.game_status.to_string(),
-                elt.last_updated.to_string(),
-                elt.clock.period_number.to_string(),
-                elt.clock.relative_game_time_in_secs.to_string(),
-                elt.clock.is_ticking.to_string(),
-                ls.visitor.to_string(),
-                ls.home.to_string(),
-            ];
-            println!("{:#?}", rec);
-            wtr.write_record(rec)?;
-        } else {
-            let rec = &[
-                elt.event_id.to_string(),
-                elt.sport.to_string(),
-                elt.game_status.to_string(),
-                elt.last_updated.to_string(),
-                elt.clock.period_number.to_string(),
-                elt.clock.relative_game_time_in_secs.to_string(),
-                elt.clock.is_ticking.to_string(),
-                "".to_string(),
-                "".to_string(),
-            ];
-            println!("{:#?}", rec);
-            wtr.write_record(rec)?;
-        }
-    }
-    wtr.flush()?;
-    Ok(())
-}
-
-fn parse_and_write(json_data: String) -> Result<(), Box<dyn Error>> {
-    let write_fn = "./data/root.csv";
-
-    let mut wtr = csv::Writer::from_path(write_fn)?;
-
-    wtr.write_record(&[
-        "id",
-        "sport",
-        "event_desc",
-        "dg_desc",
-        "mkt_desc",
-        "oc_desc",
-        "price",
-        "hc",
-    ])?;
-    let ds: Vec<bov::Root> = serde_json::from_str(&json_data).unwrap();
-
[…]

### 2020-04-02 rust/sipoxide/src/scores.rs

@@ -1,233 +1,0 @@
-extern crate serde;
-use std::fmt;
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct Root {
-    pub event_id: i64,
-    pub event_source: String,
-    pub alt_ids: AltIds,
-    pub scoreboard_available: bool,
-    pub sport: String,
-    pub latest_score: Option<LatestScore>,
-    pub clock: Clock,
-    pub sport_details: Option<SportDetails>,
-    pub game_status: String,
-    pub last_updated: String,
-    pub display_visitor_team_first: bool,
-    #[serde(default)]
-    pub previous_periods_score: Vec<PreviousPeriodsScore>,
-    pub current_period_score: Option<CurrentPeriodScore>,
-    pub last_significant_key_event: Option<LastSignificantKeyEvent>,
-    pub last_significant_key_event_index: Option<i64>,
-}
-
-impl fmt::Display for Root {
-    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
-        if let Some(cur_score) = &self.latest_score {
-            write!(f, "{}, {}, {}, {}, {} {} {} {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock.period_number, self.clock.relative_game_time_in_secs self.clock.is_ticking, cur_score)
-        } else {
-            write!(f, "{}, {}, {}, {}, {} {} {}", self.event_id, self.sport, self.game_status, self.last_updated, self.clock.period_number, self.clock.relative_game_time_in_secs self.clock.is_ticking)
-        }
-    }
-}
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct AltIds {
-    #[serde(rename = "BGS")]
-    pub bgs: i64,
-    pub feed_code: Option<i64>,
-}
-
-#[derive(Serialize, Deserialize, Debug)]
-#[serde(rename_all = "camelCase")]
-pub struct LatestScore {
-    pub home: String,
-    pub visitor: String,
-}
-
-impl fmt::Display for LatestScore {
-    fn fmt(&self, f: &mut fmt::Formatter<'_>) -> fmt::Result {
-        write!(f, "{:?}, {:?}", self.visitor, self.home)
-    }
-}
-
[…]

### 2020-04-04 random/school/paper.tex
paper outline, adding quotes to paper

--- 2020-03-30 random/school/paper.tex
@@
 \end{center}
-\begin{itemize} 
-    \item In Capital, Marx asks how a capitalist can purchase something with a certain value and sell it at a higher value. 
-    \item Marx concludes that the defining characteristic of a capitalistic society is the ruling class' ability to valorize their capital, defined by the equation MCM'. 
-    \item Captialist ownership of surplus value, the increasing proportion of constant capital to variable capital, and the declining rate of profit provide as the basis for Marx's claim that the capitalist mode of production will necessarily be replaced.
-
-    \item I will define the model that Smith presents, contrast with Marx, and show that the structural contradictions in capitalism that Marx presents as necessitating a post-capitalist economy follow from the calculation of $\lim_{t \to \infty}$, but fails to provide bounds on the timing of this eventuality.
-    \item Instead of viewing the declining rate of profit as a indicator of capitalisms inevitable demise, I demonstrate the tendency of the rate of profit to fall is the enabling factor that allows for surplus value to be redistributed, in the form of lower cost technology, enabling wage-laborers to enter the hussle.
-    \item A key feature of Smith's model claims maximal individual liberty is ideal for economic and technological growth because the function optimal\_action(someone\_else) is incomputable. 
-    \item Smith defines growth based off of the total value of commodities, claiming that services rarely have value after the service is complete. \textbf{quote}
-    \item Smith describes a commodity by it's exchange value/worth, $W$, derived by the sum of the constant capital, variable capital, and surplus value, given by $c + L + s = W$. \textbf{quote}
-    \item Ignoring economies of scale for this paper, I assume linearity with commodity quantity $q$ to arrive at $\forall q \in \mathbb{N}, \forall{cLs} \in \mathbb{R^{+}}, q(c + L + s) = qW = qc + qL + qs $.
+In Capital, Marx asks how a capitalist can purchase something with a certain value and sell it at a higher value. 
+Marx claims that the defining characteristic of a capitalistic society is the ruling class' ability to valorize their capital, defined by the equation MCM'. 
+Captialist ownership of surplus value, the increasing proportion of constant capital to variable capital, and the declining rate of profit provide as the basis for Marx's claim that the capitalist mode of production will necessarily be replaced.
+I will define the model that Smith presents, contrast with Marx, and show that the structural contradictions in capitalism that Marx presents as necessitating a post-capitalist economy correctly follow from the calculation of $\lim_{t \to \infty}$, but fails to provide bounds on the timing of this eventuality.
+Instead of viewing the declining rate of profit as a indicator of capitalisms inevitable demise, I demonstrate the tendency of the rate of profit to fall is the enabling factor that allows for surplus value to be redistributed, in the form of lower cost technology, enabling wage-laborers to enter the hussle.
+\par
+Definitions of value are the basis for economic theory and an essential distinction to both Smith and Marx is the distinction between the value of commodities and the price of commodities \textbf{distinction between price/value}.
+Smith demonstrates this by explaining supply and demand, showing that commodity value to the owner, when not used for consumption, but for exchange \textbf{`is equal to the quantity of labour which it enables him to purchase or command', whereas to the buyer, the price `is the toil and trouble of acquiring it' (Smith 30).}
+A key feature of Smith's model claims maximal individual liberty is ideal for economic and technological growth because the function $optimal\_action(someone\_else)$ is incomputable.
+\textbf{By pursuing his own interest he frequently promotes that of the society more effectually than when he really intends to promote it (Smith 423).}
+Smith claims that services rarely have value after the service is complete and that it is exhcangable commodities that are valuable.
+\textbf{services which perish generally in the very instant of their performance, and does not fix or realise itself in any vendible commodity (Smith 39).}
+Smith describes a commodity by it's exchange value/worth, $W$, derived by the sum of the constant capital, variable capital, and surplus value, given by $c + L + s = W$. \textbf{quote}
+Ignoring economies of scale for this paper, I assume linearity with commodity quantity $q$ to arrive at $\forall q \in \mathbb{N}, \forall{cLs} \in \mathbb{R^{+}}, q(c + L + s) = qW = qc + qL + qs $.
+The nation's economy will be defined as a graph on a function $f(t) = G_t(V_t, E_t)$. 
+Defining this graph on a function allows for any vertex in set of vertices $V$, and for any edge in the set of edges $E$ to change continuously.
+Now to define what each vertex and edge is (person and instantaneous time trade respectively): We will assume, following Smith's claim that there are uncountably many complexities regarding human action that necesitate individual liberty.
 \textbf{quote}
-    \item The nation's economy will be defined as a graph on a function $f(t) = G_t(V_t, E_t)$. 
-    \item Defining this graph on a function allows for any vertex in set of vertices $V$, and for any edge in the set of edges $E$ to change continuously.
-    \item Now to define what each vertex and edge is (person and instantaneous time trade respectively): We will assume, following Smith's claim that there are uncountably many complexities regarding human action that necesitate individual liberty.
+We can define three important types that generate this model, commodities, people, and trades.
+A Commodity is a tuple containing: quantity/amount $q$, per-unit constant capital cost $c$, the per-unit variable capital cost $L$, and resulting per-unit surplus value $s$. 
+Let the set of all commodities (past and present) be an infinite ordered-set denoted $\boldsymbol{C}$ with cardinality $m = |\boldsymbol{C}|$.
+A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities, called a Portfolio, $A_{it} = {{q, c, L, s}_{1}, {q, c, L, s}_{2},\ldots,{q, c, L, s}_{m}}$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade $\hat{e_{ijt}}$, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
+A Trade at time $t$ is an instantaneous bidirected edge between the two Persons and N-Person trades are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed. 
+Exercising a use-value can be represented as a vertex with an edge to itself, called a loop, in which a trade with one's own commodites consumes their existence.
+Notationally: $q_{ijt_{a}} = V_{it_{a}}.A_{jq} =$ the quantity $q$ of commodity $j$ that person $i$ owns at time $a$, similarly for the constant capital, variable capital, and surplus value.
+An example of labor in this model: $P_i$ Trades with $P_j$ for assets $A$ and Trades, typically money, with $P_k$.
+$P_k$ expends their own assets through work/labour by a series of Trades with $P_i$ in which $A$ is augmented into a new commodity with surplus value, owned by $P_i$.  
+Note, Money::Commodity, but acts as a commodity that serves as a primary mode of conversion for commodities associated with a consumable use-value, as the use-value of money is to employ it and generate a surplus value, given by MCM', \textbf{all commodities are merely particular equivalents of money, the latter being their universal equivalent, they, with regard to the latter as the universal commodity, play the parts of particular commodities (Marx 89.)}
+This quote is a based off of the mean-value theorem (MVT); we can convert all commodities into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc.
+This is a common theme for both Smith and Marx: the directional regression to a
+If we let $\boldsymbol{V} :=\bigcup\limits_{t \leq t_a} V_t \in G_t$ and $\boldsymbol{E} :=\bigcup\limits_{t \leq t_a} E_t \in G_t$ maximal set of all people and trades, then we can define the wealth of a nation at time $t_a$ as $\sum\limits_i^n$ $\sum\limits_j^m$ $q_{ijt_{a}} * (c_{ijt_{a}} + L_{ijt_{a}} + s_{ijt_{a}})$.
+The reason that it is not a sum over all $t < t_a$ is that the surplus value accumulated through production is stored in the costant capital of the current commodities owned by people. \textbf{quote}
+This framework makes easy to interpret the valorization of capital.
+For example, if a Person $i$ at time $t$ with commodities/assets $A$ can employ their capital in a succession of Trades and conclude with more Commodities than starting, then they have valorized their capital via arbitrage.
+ Profitting off of the discrepancies in prices is not a zero sum game, as the arbitrageur is forcing price stability by taking profits from commodity producers, who subsequently need to employ more constant capital to reduce the per-unit variable capital cost.
+We now want to extend this model to account for the class dynamics of MCM' that Marx presents as necessitating a post-capitalist mode of production and show that the discretization of individuals into homogeneous classes violates Smith's key assertion that it is impossible to calculate the optimal action for any given individual.
+\textbf{quote on MCM' and classes}
+\textbf{something about supply demand and normal distributions}
+Marx claims that the worker is completely reduced to selling their labor for wages that are spent entirely on the means of subsistence and reproduction. \textbf{quote}
+Let $\alpha$ be a set of assets defining the means of subsistence, and therefore a death condition given by: $\{A_i - x < 0| x \in \alpha \}$  
+We want to extend this model to explain labor/class relations, the labor theory of value, and the relative dimunition of the variable part of capital to constant capital.
+We can extend the type Person, with an attribute characterizing their class, where a Person is a wage-laborer $\beta$ or a capitalist $\gamma$, $P_i::\beta$ and $P_i::\gamma$ respectively.
+\textbf{Quote on use value being equivalent to exchange value}
+Marx identifies the apparent nonlinear behavior of the proportion of constant capital to variable capital as technology advances.
  \textbf{quote}
-    \item We can define three important types (commodities, people, and trades) that generate this model. 
-    \item A Commodity is a tuple containing: quantity/amount $q$, per-unit constant capital cost $c$, the per-unit variable capital cost $L$, and resulting per-unit surplus value $s$. 
-    \item Let the set of all commodities be an infinite ordered-set denoted $\boldsymbol{C}$ with cardinality $m = |\boldsymbol{C}|$. \textbf{quote}.
-
-    \item A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities (called assets) $A_{it} = ((q, c, L, s)_{1}, (q, c, L, s)_{2},...,(q, c, L, s)_{m})$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade $\hat{e_{ijt}}$, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
-    \item A Trade at time $t$ is an instantaneous bidirected edge between the two Persons and N-Person trades are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed.
-    \item Exercising a use-value can be represented as a vertex with an edge to itself, called a loop, in which a trade with one's own commodites consumes their existence.
-    \item Notationally: $q_{ijt_{a}} = V_{it_{a}}.A_{jq} =$ the quantity $q$ of commodity $j$ that person $i$ owns at time $a$, similarly for the constant capital, variable capital, and surplus value.
-    \item An example of labor in this model: $P_i$ Trades with $P_j$ for assets $A$ and Trades, typically money, with $P_k$.
-    \item $P_k$ expends their own assets through work/labour by a series of Trades with $P_i$ in which $A$ is augmented into a new commodity with surplus value, owned by $P_i$.  
-    \item Note, Money::Commodity, but acts as a commodity that serves as a primary mode of conversion for commodities associated with a consumable use-value, as the use-value of money is to employ it and generate a surplus value, given by MCM'.
-    \item \textbf{quote on monetary value}
-    \item This quote is a based off of the mean-value theorem (MVT); we can convert all commodities into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc.
-    \item If we let $\boldsymbol{V} :=\bigcup\limits_{t \leq t_a} V_t \in G_t$ and $\boldsymbol{E} :=\bigcup\limits_{t \leq t_a} E_t \in G_t$ maximal set of all people and trades, then we can define the wealth of a nation at time $t_a$ as $\sum\limits_i^n$ $\sum\limits_j^m$ $q_{ijt_{a}} * (c_{ijt_{a}} + L_{ijt_{a}} + s_{ijt_{a}})$.
-    \item The reason that it is not a sum over all $t < t_a$ is that the surplus value accumulated through production is stored in the costant capital of the current commodities owned by people.
-\textbf{quote}
-    \item This framework makes easy to interpret the valorization of capital.
-    \item For example, if a Person $i$ at time $t$ with commodities/assets $A$ can employ their capital in a succession of Trades and conclude with more Commodities than starting, then they have valorized their capital via arbitrage.
-    \item  Profitting off of the discrepancies in prices is not a zero sum game, as the arbitrageur is forcing price stability by taking profits from commodity producers, who subsequently need to employ more constant capital to reduce the per-unit variable capital cost.
-    \item We now want to extend this model to account for the class dynamics of MCM' that Marx presents as necessitating a post-capitalist mode of production and show that the discretization of individuals into homogeneous classes violates Smith's key assertion that it is impossible to calculate the optimal action for any given individual.
-    \item \textbf{quote on MCM' and classes}
-    \item \textbf{something about supply demand and normal distributions}
-    \item Marx claims that the worker is completely reduced to selling their labor for wages that are spent entirely on the means of subsistence and reproduction. \textbf{quote}
-    \item Let $\alpha$ be a set of assets defining the means of subsistence, and therefore a death condition given by: $\{A_i - x < 0| x \in \alpha \}$  
-    \item We want to extend this model to explain labor/class relations, the labor theory of value, and the relative dimunition of the variable part of capital to constant capital.
-    \item We can extend the type Person, with an attribute characterizing their class, where a Person is a wage-laborer $\beta$ or a capitalist $\gamma$, $P_i::\beta$ and $P_i::\gamma$ respectively.
-    \item \textbf{Quote on use value being equivalent to exchange value}
-    \item Marx identifies the apparent nonlinear behavior of the proportion of constant capital to variable capital as technology advances.
-    \item  \textbf{quote}
-    \item However, it is not clear that this eventuality is one that will necessarily be witnessed.
-    \item Zeno's paradox is a simple analogy for the amount of time it will take for the proportion of constant capital to entirely encompass that of variable capital, which is the real precondition for a post-capitalist mode of production.
-    \item We can only say what the behavior is of $\lim_{t \to \infty}$, but not when it will happen.
-
-\end{itemize}
-
-Marx, in assuming that
-
-\begin{enumerate}
-    \item Smith 20: "Every man thus lives by exchanging, or becomes in some measure a merchant, and the society itself grows to be what is properly a commercial society,"
-    \item Marx 41: "an immense accumulation of commodities,"* its unit being a single commodity. (demonstrates $\in \mathbb{N}$, capitalist basis of value is commodities)
-    \item Marx 42: When treating of use-value, we always assume to be dealing with definite quantities, such as dozens of watches, yards of linen, or tons of iron.
-\end{enumerate}
+However, it is not clear that this eventuality is one that will necessarily be witnessed.
+Zeno's paradox is a simple analogy for the amount of time it will take for the proportion of constant capital to entirely encompass that of variable capital, which is the real precondition for a post-capitalist mode of production.
+	We can only say what the behavior is of $\lim_{t \to \infty}$, but not when it will happen.
+% \end{itemize}
 
@@
     \item \href{https://en.wikipedia.org/wiki/Graph_(abstract_data_type)}{Graphs}
-
+	\item \href{https://archive.org/details/HannahArendt/page/n1/mode/2up}{arendt fbi doc}
 \end{itemize}
 
-% and are consequent from discretizing the populous into homogeneous classes and that collective ownership
-
-% let $n := |\boldsymbol{V}|$ being the total number of people to have existed in this society.
-% $\forall v, e \in (\boldsymbol{V}, \boldsymbol{E}), v::$Person$, e::$Trade, where Person at time T $:= (A_{t}, B_{t}, u_{t}, e_{t})$ where $u$ is a function that takes in 
+% \textbf{"though the market price of every particular commodity is in this manner continually gravitating, if one may say so, towards the natural price, yet sometimes particular accidents, sometimes natural causes, and sometimes particular regulations of police, may, in many commodities, keep up the market price, for a long time together, a good deal above the natural price (Smith 59).}
 \end{document}

### 2020-04-04 random/school/paper.tex
essay and creative proposal  done, 50% arendt canvas

@@
 Ali Feser \\
-3/27/20 \\
+4/4/20 \\
 Power, Identity, and Resistance-2 
 \begin{center}
-    MCM' and the Tendency of the Rate of Profit
+	Prompt 5: Limits   
 \end{center}
@@
 Captialist ownership of surplus value, the increasing proportion of constant capital to variable capital, and the declining rate of profit provide as the basis for Marx's claim that the capitalist mode of production will necessarily be replaced.
-I will define the model that Smith presents, contrast with Marx, and show that the structural contradictions in capitalism that Marx presents as necessitating a post-capitalist economy correctly follow from the calculation of $\lim_{t \to \infty}$, but fails to provide bounds on the timing of this eventuality.
-Instead of viewing the declining rate of profit as a indicator of capitalisms inevitable demise, I demonstrate the tendency of the rate of profit to fall is the enabling factor that allows for surplus value to be redistributed, in the form of lower cost technology, enabling wage-laborers to enter the hussle.
+I will define the model that Smith presents, contrast with Marx, and show that the structural contradictions in capitalism that Marx presents as necessitating a post-capitalist economy correctly follow from the calculation of $\lim_{t \to \infty}$, but the timing of this eventuality is unbounded.
+Instead of viewing the declining rate of profit as a indicator of capitalisms inevitable demise, I demonstrate the tendency of the rate of profit to fall is the enabling factor that allows for surplus value to be redistributed, in the form of lower cost technology, enabling wage-laborers to enter the hussle and prolonging the capitalist mode of production.
 \par
-Definitions of value are the basis for economic theory and an essential distinction to both Smith and Marx is the distinction between the value of commodities and the price of commodities \textbf{distinction between price/value}.
-Smith demonstrates this by explaining supply and demand, showing that commodity value to the owner, when not used for consumption, but for exchange \textbf{`is equal to the quantity of labour which it enables him to purchase or command', whereas to the buyer, the price `is the toil and trouble of acquiring it' (Smith 30).}
+Definitions of value are the basis for economic theory and an essential distinction to both Smith and Marx is the distinction between the value of commodities and the price of commodities `value, \ldots, has two different meanings, and sometimes expresses the utility of some particular object, and sometimes the power of purchasing other goods' (Smith 28).
+Marx states that this distinction is a fundemental precondition of the capitalist mode of production, `from that moment the distinction becomes firmly established between the utility of an object for the purposes of consumption, and its utility for the purposes of exchange.
+Its use-value becomes distinguished from its exchange-value' (Marx 88).
+Marx also writes that a commodity's use-value is `to all other persons an equivalent, but that only in so far as it has use-value for them' (Marx 88).
+Smith demonstrates this by explaining supply and demand, showing that commodity value to the owner, when not used for consumption, but for exchange `is equal to the quantity of labour which it enables him to purchase or command', whereas to the buyer, the price `is the toil and trouble of acquiring it' (Smith 30).
 A key feature of Smith's model claims maximal individual liberty is ideal for economic and technological growth because the function $optimal\_action(someone\_else)$ is incomputable.
-\textbf{By pursuing his own interest he frequently promotes that of the society more effectually than when he really intends to promote it (Smith 423).}
-Smith claims that services rarely have value after the service is complete and that it is exhcangable commodities that are valuable.
-\textbf{services which perish generally in the very instant of their performance, and does not fix or realise itself in any vendible commodity (Smith 39).}
-Smith describes a commodity by it's exchange value/worth, $W$, derived by the sum of the constant capital, variable capital, and surplus value, given by $c + L + s = W$. \textbf{quote}
-Ignoring economies of scale for this paper, I assume linearity with commodity quantity $q$ to arrive at $\forall q \in \mathbb{N}, \forall{cLs} \in \mathbb{R^{+}}, q(c + L + s) = qW = qc + qL + qs $.
+`By pursuing his own interest he frequently promotes that of the society more effectually than when he really intends to promote it' (Smith 423).
+Smith claims that services rarely have value after the service is complete and that it is exhcangable commodities that are valuable, `services which perish generally in the very instant of their performance, and does not fix or realise itself in any vendible commodity' (Smith 39).
+\par
+
 The nation's economy will be defined as a graph on a function $f(t) = G_t(V_t, E_t)$. 
@@
 Now to define what each vertex and edge is (person and instantaneous time trade respectively): We will assume, following Smith's claim that there are uncountably many complexities regarding human action that necesitate individual liberty.
-\textbf{quote}
 We can define three important types that generate this model, commodities, people, and trades.
@@
 Let the set of all commodities (past and present) be an infinite ordered-set denoted $\boldsymbol{C}$ with cardinality $m = |\boldsymbol{C}|$.
+Smith describes a commodity's exchange value/worth, $W$, derived by the sum of the constant capital, variable capital, and surplus value, given by $c + L + s = W$. 
+Marx however, makes distinct the inherent exchange ratios in commodities, based on the socially necessary labor time to produce, with fluctuating market prices, `the values of the variable capital and of the labour-power purchased by that capital are equal' (Marx 218).
+Despite the origin of value, to Marx, being solely in the variable capital of society, defining a commodity as component parts $c$, $L$, and $s$ allows for explaining the relation between productivity and constant and variable capital.
+Ignoring economies of scale for this paper, I assume linearity with commodity quantity $q$ to arrive at $\forall q \in \mathbb{N}, \forall{cLs} \in \mathbb{R^{+}}, q(c + L + s) = qW = qc + qL + qs $.
 A Person $i$ at a given time $t$ is denoted $P_{it}$ defined by: a list of values for all commodities, called a Portfolio, $A_{it} = {{q, c, L, s}_{1}, {q, c, L, s}_{2},\ldots,{q, c, L, s}_{m}}$, an arbitrary uncountable bitstring (0s and 1s) $B_{it}$ that cannot be computed a priori by someone else and is assumed to be random, and a function, where given one's own bitstring, and a proposed trade $\hat{e_{ijt}}$, a binary decision is computed instantaneously, $g_{it} : (B_{it}, \hat{e_{ijt}}) \mapsto \{x | x \in  \{0, 1\}\}$.
-A Trade at time $t$ is an instantaneous bidirected edge between the two Persons and N-Person trades are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed. 
-Exercising a use-value can be represented as a vertex with an edge to itself, called a loop, in which a trade with one's own commodites consumes their existence.
-Notationally: $q_{ijt_{a}} = V_{it_{a}}.A_{jq} =$ the quantity $q$ of commodity $j$ that person $i$ owns at time $a$, similarly for the constant capital, variable capital, and surplus value.
+A Trade at time $t$ is an instantaneous bidirected edge, defined by a transaction portfolio, between the two Persons.
+N-Person trades are reduced to atomic instantaneous 2 Person Trades and no overdraws in Trades are allowed. 
+Exercising a use-value can be represented as a vertex with an edge to itself, called a loop, in which a trade with one's own commodites fully or partially consumes the goods' existence. 
+Loops can also demonstrate commodity production and labor, where commodities and time are consumed to generate new commodities. 
+Notationally: $q_{ijt_{a}} =$ the quantity $q$ of commodity $j$ that person $i$ owns at time $a$, similarly for the constant capital, variable capital, and surplus value. \par
+
+This model is agnostic of currency, however, money is a fundemental invention for capitalist production, according to Marx, enabling the capitalist to valorize capital through employing labor and exchanging goods for more capital, all commodities are merely particular equivalents of money, the latter being their universal equivalent, they, with regard to the latter as the universal commodity, play the parts of particular commodities (Marx 89.)
+Note, Money::Commodity, but acts as a commodity that serves as a primary mode of conversion for commodities associated with a consumable use-value, as the use-value of money is to employ it and generate a surplus value, given by MCM'.
+We can see alienation as a consequence of labor in this model, in which the commodities produced from paid labor, are owned by the employer, the worker `does not directly produce the actual necessaries which he himself consumes' (Marx 216).
 An example of labor in this model: $P_i$ Trades with $P_j$ for assets $A$ and Trades, typically money, with $P_k$.
 $P_k$ expends their own assets through work/labour by a series of Trades with $P_i$ in which $A$ is augmented into a new commodity with surplus value, owned by $P_i$.  
-Note, Money::Commodity, but acts as a commodity that serves as a primary mode of conversion for commodities associated with a consumable use-value, as the use-value of money is to employ it and generate a surplus value, given by MCM', \textbf{all commodities are merely particular equivalents of money, the latter being their universal equivalent, they, with regard to the latter as the universal commodity, play the parts of particular commodities (Marx 89.)}
-This quote is a based off of the mean-value theorem (MVT); we can convert all commodities into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc.
-This is a common theme for both Smith and Marx: the directional regression to a
-If we let $\boldsymbol{V} :=\bigcup\limits_{t \leq t_a} V_t \in G_t$ and $\boldsymbol{E} :=\bigcup\limits_{t \leq t_a} E_t \in G_t$ maximal set of all people and trades, then we can define the wealth of a nation at time $t_a$ as $\sum\limits_i^n$ $\sum\limits_j^m$ $q_{ijt_{a}} * (c_{ijt_{a}} + L_{ijt_{a}} + s_{ijt_{a}})$.
-The reason that it is not a sum over all $t < t_a$ is that the surplus value accumulated through production is stored in the costant capital of the current commodities owned by people. \textbf{quote}
+Money's basis as being the approximation of equivalent values and in conjunction, average labor-power, is based off of the mean-value theorem (MVT),
+Each commodity can thus be converted into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc.
+This is a common theme for both Smith and Marx, however Marx would disregard the constant capital and surplus value, denoting solely labor as the basis of value, `labour realised in value, is labour of an average social quality; is consequently the expenditure of average labour-power' (Marx 323).
+We can define the wealth of a nation at time $t_a$ as $\sum\limits_i^n$ $\sum\limits_j^m$ $q_{ijt_{a}} * (c_{ijt_{a}} + L_{ijt_{a}} + s_{ijt_{a}})$. 
+The reason that it is not a sum over all $t < t_a$ is that the surplus value accumulated through production is stored in the costant capital (previous stored labor) of the current commodities owned by people.
+`The total labour-power of society, which is embodied in the sum total of the values of all commodities produced by that society' (Marx 39).
 This framework makes easy to interpret the valorization of capital.
@@
 Profitting off of the discrepancies in prices is not a zero sum game, as the arbitrageur is forcing price stability by taking profits from commodity producers, who subsequently need to employ more constant capital to reduce the per-unit variable capital cost.
+\par
 We now want to extend this model to account for the class dynamics of MCM' that Marx presents as necessitating a post-capitalist mode of production and show that the discretization of individuals into homogeneous classes violates Smith's key assertion that it is impossible to calculate the optimal action for any given individual.
-\textbf{quote on MCM' and classes}
-\textbf{something about supply demand and normal distributions}
-Marx claims that the worker is completely reduced to selling their labor for wages that are spent entirely on the means of subsistence and reproduction. \textbf{quote}
+Marx claims that the worker is completely reduced to selling their labor for wages that are spent entirely on the means of subsistence and reproduction. 
 Let $\alpha$ be a set of assets defining the means of subsistence, and therefore a death condition given by: $\{A_i - x < 0| x \in \alpha \}$  
-We want to extend this model to explain labor/class relations, the labor theory of value, and the relative dimunition of the variable part of capital to constant capital.
+If it were the case that every worker was selling their labor at subsistence, then a post-capitalist economy would take hold, however, at no point can this be proven. 
 We can extend the type Person, with an attribute characterizing their class, where a Person is a wage-laborer $\beta$ or a capitalist $\gamma$, $P_i::\beta$ and $P_i::\gamma$ respectively.
-\textbf{Quote on use value being equivalent to exchange value}
+It is clear that if $\forall P::\gamma \in V_t$, $P$ satisfies the death/subsistence condition, then it is clear no opportunities for competition exist. 
+This would satisfy the condition that the optimal action for every worker would be to stop working.
+However, this ignores the distribution of wages/profit in both workers and capitalists, $\forall P \in V_t, \exists \Pr(class\_change) > 0$.
+This can be seen in capitalists overpaying workers relative to the natural price, as other capitalists advance technology, increasing labor-power and enabling a worker to begin their exploitation of others.
+Marx correctly demonstrates the increasing relative difficulty in a capitalist becoming working class, or vice versa, through his idea of capital centralization, where mechanization increases the supply of labor, by increasing the productivity of labor-power, and decreases per-unit cost of production, `demand for labour is not identical with increase of capital, nor supply of labour with increase of the working-class' (Marx 640).
 Marx identifies the apparent nonlinear behavior of the proportion of constant capital to variable capital as technology advances.
- \textbf{quote}
 However, it is not clear that this eventuality is one that will necessarily be witnessed.
-Zeno's paradox is a simple analogy for the amount of time it will take for the proportion of constant capital to entirely encompass that of variable capital, which is the real precondition for a post-capitalist mode of production.
+Zeno's paradox is a simple analogy for the amount of time it will take for the proportion of constant capital to entirely encompass that of variable capital, which is the precondition for a post-capitalist mode of production, `in a given society the limit would be reached only when the entire social capital was united in the hands of either a single capitalist or a single capitalist company' (Marx 627).
 We can only say what the behavior is of $\lim_{t \to \infty}$, but not when it will happen.
-% \end{itemize}
 
+Link Sources: 
 \begin{itemize}
     \item \href{https://en.wikipedia.org/wiki/Graph_(abstract_data_type)}{Graphs}
-	\item \href{https://archive.org/details/HannahArendt/page/n1/mode/2up}{arendt fbi doc}
+	\item \href{https://archive.org/details/in.ernet.dli.2015.207956/page/n21/mode/2up}{Wealth of Nations}
+	\item \href{http://www.archive.org/details/capitalcritiqueoOOmarx}{Capital}
 \end{itemize}
-
-% \textbf{"though the market price of every particular commodity is in this manner continually gravitating, if one may say so, towards the natural price, yet sometimes particular accidents, sometimes natural causes, and sometimes particular regulations of police, may, in many commodities, keep up the market price, for a long time together, a good deal above the natural price (Smith 59).}
 \end{document}

### 2020-04-04 random/school/paper.tex
last touches on essay

@@
 Despite the origin of value, to Marx, being solely in the variable capital of society, defining a commodity as component parts $c$, $L$, and $s$ allows for explaining the relation between productivity and constant and variable capital.
+\par
 Ignoring economies of scale for this paper, I assume linearity with commodity quantity $q$ to arrive at $\forall q \in \mathbb{N}, \forall{cLs} \in \mathbb{R^{+}}, q(c + L + s) = qW = qc + qL + qs $.
@@
 $P_k$ expends their own assets through work/labour by a series of Trades with $P_i$ in which $A$ is augmented into a new commodity with surplus value, owned by $P_i$.  
-Money's basis as being the approximation of equivalent values and in conjunction, average labor-power, is based off of the mean-value theorem (MVT),
-Each commodity can thus be converted into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc.
+Money's basis as being the approximation of equivalent values and in conjunction, average labor-power, is based off of the mean-value theorem (MVT).
+Each commodity can thus be converted into a single value for monetary wealth by summing up $q(c+L+s)$ for all commodities, for a given set of people, trades, etc. \par
+
 This is a common theme for both Smith and Marx, however Marx would disregard the constant capital and surplus value, denoting solely labor as the basis of value, `labour realised in value, is labour of an average social quality; is consequently the expenditure of average labour-power' (Marx 323).
@@
 \par
+
 We now want to extend this model to account for the class dynamics of MCM' that Marx presents as necessitating a post-capitalist mode of production and show that the discretization of individuals into homogeneous classes violates Smith's key assertion that it is impossible to calculate the optimal action for any given individual.
 Marx claims that the worker is completely reduced to selling their labor for wages that are spent entirely on the means of subsistence and reproduction. 
-Let $\alpha$ be a set of assets defining the means of subsistence, and therefore a death condition given by: $\{A_i - x < 0| x \in \alpha \}$  
+Let $\alpha$ be a set of assets defining the means of subsistence, and therefore a death condition given by: $\{A_i - x < 0| x \in \alpha \}$.
 If it were the case that every worker was selling their labor at subsistence, then a post-capitalist economy would take hold, however, at no point can this be proven. 
@@
 This can be seen in capitalists overpaying workers relative to the natural price, as other capitalists advance technology, increasing labor-power and enabling a worker to begin their exploitation of others.
+\par
+
 Marx correctly demonstrates the increasing relative difficulty in a capitalist becoming working class, or vice versa, through his idea of capital centralization, where mechanization increases the supply of labor, by increasing the productivity of labor-power, and decreases per-unit cost of production, `demand for labour is not identical with increase of capital, nor supply of labour with increase of the working-class' (Marx 640).
@@
 Link Sources:
-\begin{itemize}
-    \item \href{https://en.wikipedia.org/wiki/Graph_(abstract_data_type)}{Graphs}
-	\item \href{https://archive.org/details/in.ernet.dli.2015.207956/page/n21/mode/2up}{Wealth of Nations}
-	\item \href{http://www.archive.org/details/capitalcritiqueoOOmarx}{Capital}
-\end{itemize}
+\begin{verbatim}
+Graphs
+
+https://en.wikipedia.org/wiki/Graph_(abstract_data_type)
+
+Wealth of Nations
+
+https://archive.org/details/in.ernet.dli.2015.207956/page/n21/mode/2up
+
+Capital
+
+https://archive.org/details/capitalcritiqueo00marx/page/n6/mode/2up 
+\end{verbatim}
 \end{document}

### 2024-06-28 random/career_preparation/2024_resume/RESUME_2024_Anand.tex
new resume

\documentclass[10pt]{extarticle}
\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}
\marginparwidth 0pt \oddsidemargin 0pt \evensidemargin 0pt
\marginparsep0pt \topmargin 0pt \textwidth 7.5in \textheight 9in
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}	
\setlength{\parskip}{\baselineskip}
\usepackage{enumitem}
\usepackage{hyperref}

\addtolength{\topmargin}{-1.075in}
\addtolength{\textheight}{1.75in}
\parindent=0pt
\def\ccfont{\sf}
\begin{document}

\hspace{0.145in} {\huge\bf ANAND I. JAIN} \hspace{0.4cm} 610 Jackson St., Santa Clara CA 95050 \hspace{0.1cm} 408-597-4214 \hfill anandash2@gmail.com

\begin{list}{}{\setlength{\leftmargin}{1.4in}\setlength{\labelsep}{0.1cm}\setlength{\labelwidth}{1.18in}}
\item[{\bf EDUCATION}\hfill]
{\bf University of Chicago}\hfill {\bf 2017-2020}\\
Computer Science

{\bf Courses:}
•Abstract Linear Algebra (MATH 20250) •Theory of Algorithms (CMSC 27200) •Computer Systems (CMSC 15400) •Discrete Mathematics (CMSC 27100)
•Electronics (PHYS 22600) •Inventing Interactive Devices (CMSC 23220) •Mathematical Logic (CMSC27700) •Quantum Computation (MENG 23700)

\item[\bf EXPERIENCE\hfill]

{\bf Research Programmer, JuliaHub Inc.}\hfill {\bf Apr 2021 - July 2023}
  \setlist{nolistsep}
  \begin{itemize}[noitemsep]
    \item Implemented parsers for the CellML (CellMLToolkit.jl), Systems Biology Markup Language (SBML) (SBMLToolkit.jl), and MathML (MathML.jl) specifications in the Julia programming language. 
    %\item Experienced in high performance differential equation simulation for large state systems (>1000 ODEs).
    \item Automated simulation of \textasciitilde2000 ODE models on the BioModels.org database for performance tracking and specification compliance (\url{github.com/anandijain/BioModelsAnalysis.jl})
    \item Worked with pharma clients to translate MATLAB models to Julia for improved performance.
  \end{itemize}

{\bf Large Synoptic Survey Telescope Machine Learning Intern, Fermilab} \hfill {\bf June - Aug 2019}
  \setlist{nolistsep}
  \begin{itemize}[noitemsep]
    \item Researched the applications of neural differential equations in astronomy for the LSST.
    \item Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate
    the differential equation of different astronomical objects’ light curves (brightness over time)
    \item Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona
    \item Source code:  \url{github.com/deepskies/cosmoNODE} - Private
  \end{itemize}

\item[\bf PROJECTS\hfill]

{\bf cas3.rs - Implementing Mathematica in the Rust Language}\hfill {\bf 200 Hours Sept-Oct 2023}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
	\item Wrote the core pattern matcher, parser, and evaluator of Mathematica in Rust.
	\item Cas3 can reduce S-K combinator system expressions, simulate cellular automata, and calculate symbolic derivatives.
	\item Source code: \url{github.com/anandijain/cas3.rs} Video development: \url{https://youtube.com/playlist?list=PL79kqjVnD2EOBvsTiCQqX0ZAwx9AKiA_w&si=emnOHZQEnS98zd4m}
\end{itemize}

{\bf Building a modular synthesizer from scratch}\hfill {\bf 300 Hours Dec 2023-Feb 2024}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
	\item Used kicad to implement a square and sine-wave voltage controlled oscillator, dual power supply (+- 9V), a transistor amplifier, envelope generator, and voltage controlled low-pass filter.
	\item Used the toner-transfer method to fabricate double sided through-hole PCBs of above modules.
	\item Source code:  \url{github.com/anandijain/synth.kicad} Video development: \url{https://youtube.com/playlist?list=PL79kqjVnD2ENdJDDSTUD3ZMdZPhVVu8yw&si=TNAEGmvNShpb-L0L}
\end{itemize}

{\bf Free2Pee - Free bathroom locator website in Rust and Leptos}\hfill {\bf 75 Hours Feb-Sept 2023}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
	\item Website hosted on GitHub Pages that uses the OpenStreetMap database to find nearby bathrooms, then uses an open-source API to determine distance to the user, returning a table of all nearby bathrooms, metadata, and distance.
	\item Compiling to WebAssembly makes the website hostable statically and serverless.
	\item Source code: \url{https://github.com/free2pee/free2pee}
	\item Website: \url{https://free2pee.github.io/free2pee/}
\end{itemize}

{\bf AILeetcode - Evaluating GPT-3.5 on every LeetCode coding question}\hfill {\bf 75 Hours Jun-Aug 2023}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
	\item Created a dataset of \textasciitilde40000 OpenAI GPT completions (\textasciitilde2000 questions x 20 languages) to study the quality of code generation of LLMs across languages
	\item Submitted answers generated by GPT to LeetCode by reverse engineering LeetCode's REST API - got into top 3000 rank in LeetCode
	\item Source code: \url{https://github.com/anandijain/leetcode_evals}
\end{itemize}

{\bf Music generation with Variational-Autoencoders (VAE) in Pytorch} \hfill {\bf30 Hours Jan-Feb 2020}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
	\item Trained a VAE to find a low dimensional representation of sound segments 1-3 seconds in length
	\item Source code: \url{https://github.com/anandijain/sippyart}. 
	\item Music Outputs: \url{https://anonstandardunitofmeasurement.bandcamp.com/album/vae}
\end{itemize}

\item[\bf PUBLICATIONS\hfill]

Lang, P. F., Jain, A., \& Rackauckas, C. (2024). SBMLToolkit.jl: A Julia package for importing SBML into the SciML ecosystem. \textit{Journal of Integrative Bioinformatics}. \href{https://www.degruyter.com/document/doi/10.1515/jib-2024-0003/html}{doi:10.1515/jib-2024-0003}

Rackauckas, C., Anantharaman, R., Edelman, A., Gowda, S., Gwozdz, M., Jain, A., Laughman, C., Ma, Y., Martinuzzi, F., Pal, A., Rajput, U., Saba, E., \& Shah, V. B. (2021). Composing Modeling and Simulation with Machine Learning in Julia. \textit{arXiv:2105.05946}. Retrieved from \href{https://arxiv.org/abs/2105.05946}{arXiv:2105.05946}

%Iravanian, S., Martensen, C. J., Cheli, A., Gowda, S., Jain, A., Ma, Y., \& Rackauckas, C. (2022). Symbolic-Numeric Integration of Univariate Expressions based on Sparse Regression. \textit{CoRR}, \textit{abs/2201.12468}. Retrieved from \href{https://arxiv.org/abs/2201.12468}{arXiv:2201.12468}

\item[\bf SKILLS\hfill] Rust, Python, Julia, C, Kicad, Git, Continuous Integration, High-performance modeling and simulation of differential equations, Deep learning, MATLAB, Autodesk Fusion, Ableton Live

\end{list}

\end{document}
